---
title: "ClearanceRate_calculate rates foodxOA_experiment"
author: "Samuel Gurr"
date: "10/12/2021"
output: pdf_document
---

```{r setup, include=FALSE}
# Purpose: Bay Scallop Project - Feeding Rates
# analysis of respiration rate data

# Written by: Sam J Gurr (last edit 4/2/2023 - added back he high chrolophyll (simply TET and Chaet without separation)


# Review Riisgard 2001 defining the clearance rate of bivalves 
# NOTE: clearance rate is defined as the volume of water cleared of suspended particles per unit time, and only equals filtration rate when 
# 100% of suspended particles are efficiently retained

# LOAD PACKAGES :::::::::::::::::::::::::::::::::::::::::::::::::::::::

library(dplyr)
library(ggplot2)
library(forcats)
library(lme4)
library(lmerTest)
library(see)
library(performance)
library(car)
library(reshape2)
library(lubridate)
library(SciViews)
library(reshape2)
library(SciViews)
library(kableExtra)
library(latex2exp)
library(pander)
library(performance)
library(ggpubr)
library(Rmisc)

# SET WORKING DIRECTORY :::::::::::::::::::::::::::::::::::::::::::::::

# setwd("C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis") # Work computer
setwd("C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis") # personal computer

# LOAD DATA :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# Master_data       <- read.csv(file="Data/Clearance_rates/ClearanceRates_MasterData.csv", header=T) # master data file
Master_data           <- read.csv(file="Data/Clearance_rates/ClearanceRates_MasterData.csv", header=T, fileEncoding = "latin1") %>%  # master data file
                                   dplyr::mutate(Total_cell.ml = as.numeric(Chaet_cell.ml) + as.numeric(PLY_cell.ml)) 
  


clearance.rate_914    <- Master_data  %>% 
  dplyr::filter(Date %in% 20210914)  %>% 
  dplyr::mutate(Chamber_tank = paste(pH, Replicate, sep='_'))

clearance.rate_930    <- Master_data  %>% 
  dplyr::filter(Date %in% 20210930)  %>% 
  dplyr::mutate(Chamber_tank = paste(pH, Replicate, sep='_'))

clearance.rate_1026    <- Master_data  %>% 
  dplyr::filter(Date %in% 20211026)  %>% 
  dplyr::mutate(Chamber_tank = paste(pH, Replicate, sep='_'))



length.resp.feed <- read.csv(file="Data/Respiration/Lengths_Condition_resp_clearance.csv", header=T) %>% 
  dplyr::mutate(Date = paste("20",(format(as.Date(Date, "%m/%d/%Y"), "%y%m%d")), sep ='')) %>%
  dplyr::rename(Fed_Unfed = Food) 

length.resp.feed <- length.resp.feed[!is.na(length.resp.feed$Length_um),] %>%  
  dplyr::select(c('Date', 
                  'Run', 
                  'Plate',
                  'pH', 
                  'Fed_Unfed', 
                  'Replicate',
                  'Chamber_tank', 
                  'Number', 
                  'Length_um',
                  'whole_Dry_weight'))

```



```{r, calc ratio ChatB : PLY429 for CR trials}

Av_Chaet_Tet_initial <- Master_data %>% 
  dplyr::filter(!quality %in% '*') %>% # poor quality data marked with * due to pseudofeces in occasional measurements 
  dplyr::filter(time %in% 0) %>%       # call the initial time point 
 # dplyr::group_by(Date) %>% 
  dplyr::summarise(
    
    meanChaetB = mean(Chaet_cell.ml),
    sdChaetB   = sd(Chaet_cell.ml), 
    
    meanPLY429 = mean(PLY_cell.ml), 
    sdPLY429   = sd(PLY_cell.ml), 
    
    n = n(),
    
    seChaetB   = (sdChaetB / (sqrt(n))),
    sePLY429   = (sdPLY429 / (sqrt(n))),
    
    mean.Total_cellsmL = mean(Chaet_cell.ml + PLY_cell.ml),
    sdTotal    = sd(Chaet_cell.ml + PLY_cell.ml), 
    seTotal    = (sdTotal / (sqrt(n))),

    meanRatio_Ply429.ChaetB = mean(Chaet_cell.ml/PLY_cell.ml)
  )
Av_Chaet_Tet_initial

```

## Merge to master file 'ClearanceRate_Master'

Date from: 
- 20210914
- 20210930 

```{r merge master file, echo = TRUE}

# 20210914 DATA :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# formatting for merge
# call the 20210914 data and remove blanks
clearance.rate_914_Scallops <- merge( # note - merging with th elengths removed the blanks from the clearance rate data (no lengths for them! )
  (clearance.rate_914),
  (length.resp.feed %>% 
     dplyr::filter(Date %in% 20210914) %>% dplyr::mutate(Fed_Unfed = 'fed')) ) # note that the unfed are not present yet in the experiment!

# 20210930 DATA :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# formatting for merge
# call the 20210930 data and remove blanks
clearance.rate_930_Scallops <- merge( # note - merging with th elengths removed the blanks from the clearance rate data (no lengths for them! )
  (clearance.rate_930),
  (length.resp.feed %>% 
     dplyr::filter(Date %in% 20210930)) ) 

# 20210930 DATA :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# formatting for merge
# call the 20210930 data and remove blanks
clearance.rate_1026_Scallops <- merge( # note - merging with th elengths removed the blanks from the clearance rate data (no lengths for them! )
  (clearance.rate_1026),
  (length.resp.feed %>% 
     dplyr::filter(Date %in% 20211026)) ) 


ClearanceRate_Master             <- as.data.frame(rbind(clearance.rate_914_Scallops, 
                                          clearance.rate_930_Scallops, 
                                          clearance.rate_1026_Scallops))

# ClearanceRate_Master$tet.ply     <- (as.numeric(gsub(",", "", ClearanceRate_Master$tet.ply )))*(1000/33)
# ClearanceRate_Master$chaet       <- (as.numeric(gsub(",", "", ClearanceRate_Master$chaet )))*(1000/33)
# ClearanceRate_Master$total_algae <- (as.numeric(gsub(",", "", ClearanceRate_Master$total_algae )))*(1000/33)
# ClearanceRate_Master$seston      <- (as.numeric(gsub(",", "", ClearanceRate_Master$seston )))*(1000/33)

print(head(ClearanceRate_Master))
```



``` {r loops and  for statements - visualization of slope and calculation of CR, echo = TRUE}
# Day 0 0914 
ClearanceRate_Master.914 <- ClearanceRate_Master %>% 
  dplyr::filter(Date %in% 20210914) %>% 
  dplyr::mutate(uniq_Identifier = paste(pH, "Run", Run, "Rep",Replicate, "Num", Number, sep='_'))

loop_914 <- as.data.frame(unique(ClearanceRate_Master.914$uniq_Identifier)) %>% 
  dplyr::rename(ID = "unique(ClearanceRate_Master.914$uniq_Identifier)")

# 64 DPF 0930 
ClearanceRate_Master.930       <- ClearanceRate_Master %>% 
  dplyr::filter(Date %in% 20210930) %>% 
  dplyr::mutate(uniq_Identifier = paste(pH, Fed_Unfed, "Run", Run, "Rep",Replicate, "Num", Number, sep='_'))

loop_930 <- as.data.frame(unique(ClearanceRate_Master.930$uniq_Identifier)) %>% 
  dplyr::rename(ID = "unique(ClearanceRate_Master.930$uniq_Identifier)")

# 92 DPF 1026
ClearanceRate_Master.1026       <- ClearanceRate_Master %>% 
  dplyr::filter(Date %in% 20211026) %>% 
  dplyr::mutate(Run = case_when(Run == "1_B" ~ "1B", Run == "1" ~ "1", Run =='2' ~ '2', Run == '3' ~ '3')) %>% 
  dplyr::mutate(uniq_Identifier = paste(pH, Fed_Unfed, "Run", Run, "Rep",Replicate, "Num", Number, sep='_'))
loop_1026 <- as.data.frame(unique(ClearanceRate_Master.1026$uniq_Identifier)) %>% 
  dplyr::rename(ID = "unique(ClearanceRate_Master.1026$uniq_Identifier)")

```



# Visualize raw data & simple slopes/algae loss time-1
## Plot the raw Flow cytometry output

- note: some data points were omitted in the worksheet, review the 'raw' vs 'worksheet_R' data files

``` {r raw data plots, echo = TRUE}

# :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# 20210914 DATA :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::


SlopePlots_914_Total_ChaetPly <- ClearanceRate_Master[!is.na(ClearanceRate_Master$Total_cell.ml),] %>% 
  dplyr::filter(!Replicate %in% 'blank') %>%
  dplyr::filter(Date %in% "20210914") %>% 
  dplyr::mutate(Time._min = as.numeric(as.character(time))) %>% 
  ggplot(aes(Time._min, Total_cell.ml, color=Replicate)) + 
  geom_point(shape=1, color = "black")+ 
  ggtitle("RAW DATA - Total cells: F1s Feeding Rate 20210914")+
  labs(y = expression(Live~algae~cells~"("~cells~mL^{-1}~")"), 
       x = expression(Time~"("~minutes~")")) + 
  theme(plot.title= element_text(size =16, face ="bold", 
                                 lineheight = 8, vjust=1), aspect.ratio=1)+
  stat_smooth(method="lm", se = F) + 
  theme_bw() +
  scale_shape_identity() + 
  facet_wrap( ~ pH, scales = "free_x" )
SlopePlots_914_Total_ChaetPly

# SlopePlots_914 <- ClearanceRate_Master[!is.na(ClearanceRate_Master$total_algae),] %>% 
SlopePlots_914_chaet <- ClearanceRate_Master[!is.na(ClearanceRate_Master$Chaet_cell.ml),] %>% 
  dplyr::filter(!Replicate %in% 'blank') %>%
  dplyr::filter(Date %in% "20210914") %>% 
  dplyr::mutate(Time._min = as.numeric(as.character(time))) %>% 
  ggplot(aes(Time._min, Chaet_cell.ml, color=Replicate)) + 
  geom_point(shape=1, color = "black")+ 
  ggtitle("RAW DATA - Chaetoceros: F1s Feeding Rate 20210914")+
  labs(y = expression(Live~algae~cells~"("~cells~mL^{-1}~")"), 
       x = expression(Time~"("~minutes~")")) + 
  theme(plot.title= element_text(size =16, face ="bold", 
                                 lineheight = 8, vjust=1), aspect.ratio=1)+
  stat_smooth(method="lm", se = F) + 
  theme_bw() +
  scale_shape_identity() + 
  facet_wrap( ~ pH, scales = "free_x" )
SlopePlots_914_chaet


SlopePlots_914_ply <- ClearanceRate_Master[!is.na(ClearanceRate_Master$PLY_cell.ml),] %>% 
  dplyr::filter(!Replicate %in% 'blank') %>%
  dplyr::filter(Date %in% "20210914") %>% 
  dplyr::mutate(Time._min = as.numeric(as.character(time))) %>% 
  ggplot(aes(time, PLY_cell.ml, color=Replicate)) + 
  geom_point(shape=1, color = "black")+ 
  ggtitle("RAW DATA - PLY: F1s Feeding Rate 20210914")+
  labs(y = expression(Live~algae~cells~"("~cells~mL^{-1}~")"), 
       x = expression(Time~"("~minutes~")")) + 
  theme(plot.title= element_text(size =16, face ="bold", 
                                 lineheight = 8, vjust=1), aspect.ratio=1)+
  stat_smooth(method="lm", se = F) + 
  theme_bw() +
  scale_shape_identity() + 
  facet_wrap( ~ pH, scales = "free_x" )
SlopePlots_914_ply


SlopePlots_914_lowchla <- ClearanceRate_Master[!is.na(ClearanceRate_Master$Low_chlorophyll_cell.ml),] %>% 
  dplyr::filter(!Replicate %in% 'blank') %>%
  dplyr::filter(Date %in% "20210914") %>% 
  dplyr::mutate(Time._min = as.numeric(as.character(time))) %>% 
  ggplot(aes(time, Low_chlorophyll_cell.ml, color=Replicate)) + 
  geom_point(shape=1, color = "black")+ 
  ggtitle("RAW DATA - Low chl a (seston): F1s Feeding Rate 20210914")+
  labs(y = expression(Live~algae~cells~"("~cells~mL^{-1}~")"), 
       x = expression(Time~"("~minutes~")")) + 
  theme(plot.title= element_text(size =16, face ="bold", 
                                 lineheight = 8, vjust=1), aspect.ratio=1)+
  stat_smooth(method="lm", se = F) + 
  theme_bw() +
  scale_shape_identity() + 
  facet_wrap( ~ pH, scales = "free_x" )
SlopePlots_914_lowchla

ggarrange(SlopePlots_914_Total_ChaetPly, SlopePlots_914_chaet, SlopePlots_914_ply, SlopePlots_914_lowchla)





# Table of slope data

SlopeTable_914 <- data.frame() # run this before the loop
for(i in 1:nrow(loop_914)){
  dat <- ClearanceRate_Master.914 %>%  filter(uniq_Identifier %in% loop_914[i,])
    slope<- summary(lm((dat$Chaet_cell.ml) ~ as.numeric(dat$time)))$coef[2,"Estimate"]
    SLOPE  <- summary(lm((dat$Chaet_cell.ml) ~ as.numeric(dat$time)))$r.squared
    pval <- summary(lm((dat$Chaet_cell.ml) ~ as.numeric(dat$time)))$coef[2,"Pr(>|t|)"]
    mod  <- lm(as.numeric(dat$time) ~ dat$Chaet_cell.ml)
    norm_assum <- shapiro.test(resid(mod))
    shapiro_pval <- norm_assum$p.value
    # assign the data table 
    SLOPE.loop <- data.frame(matrix(nrow = 1, ncol = 5)) # create a new data table
    colnames(SLOPE.loop) <- c('pH', 'Replicate', 'slope', 'SLOPE', 'pval') # assign headers
    SLOPE.loop$pH        <- gsub("_.*", "\\1", loop_914[i,])
    SLOPE.loop$Replicate <- gsub("^(?:[^_]+_){4}([^_]+).*", "\\1", loop_914[i,])
    SLOPE.loop$slope     <- slope * 60  # cells per mL per hour  
    SLOPE.loop$Number    <- gsub("^(?:[^_]+_){6}([^_]+).*", "\\1", loop_914[i,])
    SLOPE.loop$SLOPE       <- SLOPE
    SLOPE.loop$pval      <- pval
    SLOPE.loop$shapiro_pval <- shapiro_pval
    # loop additions 
    df <- data.frame(SLOPE.loop) # name dataframe for this single row
    SlopeTable_914 <- rbind(SlopeTable_914,df) # bind to a cumulative list dataframe
   # print(SlopeTable_914) # show loop progress in the console
}# outside loo

SLOPE_mod_914 <- aov(lm(slope ~ pH, data= SlopeTable_914))
DF   <- paste( (summary(SLOPE_mod_914)[[1]][["Df"]])[1], (summary(SLOPE_mod_914)[[1]][["Df"]])[2], sep = '/')
Fval <- (summary(SLOPE_mod_914)[[1]][["F value"]])[1]
pval <- (summary(SLOPE_mod_914)[[1]][["Pr(>F)"]])[1]

SlopeFig914_geombox <- ggplot(SlopeTable_914, aes(pH , abs(slope) , fill = pH)) +
  theme(panel.grid=element_blank()) +
  geom_boxplot(size=0.2, alpha=0.1, aes(fill=pH)) +
  scale_fill_manual(values=c("grey50","white")) +
  geom_point(shape = 21, size = 2, position = position_jitterdodge(jitter.width = 0.1)) +
  theme_classic() +
  scale_x_discrete(labels= c('Elevated (H)', 'Ambient (L)')) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold")) +
  labs(title = "F1 Scallops: Slope algae cells/time - feeding rate trials 20210914", 
       y = expression(Slope~"="~absolute~value~"("~Live~algae~cells~mL^{-1}~hour^{-1}~")"), 
       x = expression(italic(p)*CO[2]~Treatment~"("~mu*atm~")")) + 
  annotate("text", x=2, y= 25000, size = 4, label = "aov(slope~pH Treatment)") +
  annotate("text", x=2, y= 24300, size = 4, label= paste('DF =',DF,'F =', signif(Fval, digits=3), 'p value =', signif(pval, digits=3), sep=" ")) 

SlopeFig914_geombox # 0.0531





# :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# 20210930 DATA :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

SlopePlots_930_Total_ChaetPly <- ClearanceRate_Master[!is.na(ClearanceRate_Master$Total_cell.ml),] %>% 
  dplyr::filter(!Replicate %in% 'blank') %>%
  dplyr::filter(Date %in% "20210930") %>% 
  dplyr::mutate(pH_food = paste(pH, Fed_Unfed, sep = '_')) %>% 
  dplyr::mutate(Time._min = as.numeric(as.character(time))) %>% 
  ggplot(aes(Time._min, Total_cell.ml, color=Replicate)) + 
  geom_point(shape=1, color = "black")+ 
  ggtitle("RAW DATA - Total high chl a: F1s Feeding Rate 20210930")+
  labs(y = expression(Live~algae~cells~"("~cells~mL^{-1}~")"), 
       x = expression(Time~"("~minutes~")")) + 
  theme(plot.title= element_text(size =16, face ="bold", 
                                 lineheight = 8, vjust=1), aspect.ratio=1)+
  stat_smooth(method="lm", se = F) + 
  theme_bw() +
  scale_shape_identity() + 
  facet_wrap( ~ pH_food, scales = "free_x" )
SlopePlots_930_Total_ChaetPly

SlopePlots_930_chaet <- ClearanceRate_Master[!is.na(ClearanceRate_Master$Chaet_cell.ml),] %>% 
  dplyr::filter(!Replicate %in% 'blank') %>%
  dplyr::filter(Date %in% "20210930") %>% 
  dplyr::mutate(pH_food = paste(pH, Fed_Unfed, sep = '_')) %>% 
  dplyr::mutate(Time._min = as.numeric(as.character(time))) %>% 
  ggplot(aes(Time._min, Chaet_cell.ml, color=Replicate)) + 
  geom_point(shape=1, color = "black")+ 
  ggtitle("RAW DATA - Chaetoceros: F1s Feeding Rate 20210930")+
  labs(y = expression(Live~algae~cells~"("~cells~mL^{-1}~")"), 
       x = expression(Time~"("~minutes~")")) + 
  theme(plot.title= element_text(size =16, face ="bold", 
                                 lineheight = 8, vjust=1), aspect.ratio=1)+
  stat_smooth(method="lm", se = F) + 
  theme_bw() +
  scale_shape_identity() + 
  facet_wrap( ~ pH_food, scales = "free_x" )
SlopePlots_930_chaet


SlopePlots_930_ply <- ClearanceRate_Master[!is.na(ClearanceRate_Master$PLY_cell.ml),] %>% 
  dplyr::filter(!Replicate %in% 'blank') %>%
  dplyr::filter(Date %in% "20210930") %>% 
  dplyr::mutate(pH_food = paste(pH, Fed_Unfed, sep = '_')) %>% 
  dplyr::mutate(Time._min = as.numeric(as.character(time))) %>% 
  ggplot(aes(time, PLY_cell.ml, color=Replicate)) + 
  geom_point(shape=1, color = "black")+ 
  ggtitle("RAW DATA - PLY: F1s Feeding Rate 20210930")+
  labs(y = expression(Live~algae~cells~"("~cells~mL^{-1}~")"), 
       x = expression(Time~"("~minutes~")")) + 
  theme(plot.title= element_text(size =16, face ="bold", 
                                 lineheight = 8, vjust=1), aspect.ratio=1)+
  stat_smooth(method="lm", se = F) + 
  theme_bw() +
  scale_shape_identity() + 
  facet_wrap( ~ pH_food, scales = "free_x" )
SlopePlots_930_ply


SlopePlots_930_lowchla <- ClearanceRate_Master[!is.na(ClearanceRate_Master$Low_chlorophyll_cell.ml),] %>% 
  dplyr::filter(!Replicate %in% 'blank') %>%
  dplyr::filter(Date %in% "20210930") %>% 
  dplyr::mutate(pH_food = paste(pH, Fed_Unfed, sep = '_')) %>% 
  dplyr::mutate(Time._min = as.numeric(as.character(time))) %>% 
  ggplot(aes(time, Low_chlorophyll_cell.ml, color=Replicate)) + 
  geom_point(shape=1, color = "black")+ 
  ggtitle("RAW DATA - Low chl a (seston): F1s Feeding Rate 20210930")+
  labs(y = expression(Live~algae~cells~"("~cells~mL^{-1}~")"), 
       x = expression(Time~"("~minutes~")")) + 
  theme(plot.title= element_text(size =16, face ="bold", 
                                 lineheight = 8, vjust=1), aspect.ratio=1)+
  stat_smooth(method="lm", se = F) + 
  theme_bw() +
  scale_shape_identity() + 
  facet_wrap( ~ pH_food, scales = "free_x" )
SlopePlots_930_lowchla

ggarrange(SlopePlots_930_Total_ChaetPly, SlopePlots_930_chaet, SlopePlots_930_ply, SlopePlots_930_lowchla)






# :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# 20211026 DATA :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::



SlopePlots_1026_Total_ChaetPly <- ClearanceRate_Master[!is.na(ClearanceRate_Master$Total_cell.ml),] %>% 
  dplyr::filter(!Replicate %in% 'blank') %>%
  dplyr::filter(Date %in% "20211026") %>% 
  dplyr::mutate(pH_food = paste(pH, Fed_Unfed, sep = '_')) %>% 
  dplyr::mutate(Time._min = as.numeric(as.character(time))) %>% 
  ggplot(aes(Time._min, Total_cell.ml, color=Replicate)) + 
  geom_point(shape=1, color = "black")+ 
  ggtitle("RAW DATA - Total high chl a: F1s Feeding Rate 20211026")+
  labs(y = expression(Live~algae~cells~"("~cells~mL^{-1}~")"), 
       x = expression(Time~"("~minutes~")")) + 
  theme(plot.title= element_text(size =16, face ="bold", 
                                 lineheight = 8, vjust=1), aspect.ratio=1)+
  stat_smooth(method="lm", se = F) + 
  theme_bw() +
  scale_shape_identity() + 
  facet_wrap( ~ pH_food, scales = "free_x" )
SlopePlots_1026_Total_ChaetPly

SlopePlots_1026_chaet <- ClearanceRate_Master[!is.na(ClearanceRate_Master$Chaet_cell.ml),] %>% 
  dplyr::filter(!Replicate %in% 'blank') %>%
  dplyr::filter(Date %in% "20211026") %>% 
  dplyr::mutate(pH_food = paste(pH, Fed_Unfed, sep = '_')) %>% 
  dplyr::mutate(Time._min = as.numeric(as.character(time))) %>% 
  ggplot(aes(Time._min, Chaet_cell.ml, color=Replicate)) + 
  geom_point(shape=1, color = "black")+ 
  ggtitle("RAW DATA - Chaetoceros: F1s Feeding Rate 20211026")+
  labs(y = expression(Live~algae~cells~"("~cells~mL^{-1}~")"), 
       x = expression(Time~"("~minutes~")")) + 
  theme(plot.title= element_text(size =16, face ="bold", 
                                 lineheight = 8, vjust=1), aspect.ratio=1)+
  stat_smooth(method="lm", se = F) + 
  theme_bw() +
  scale_shape_identity() + 
  facet_wrap( ~ pH_food, scales = "free_x" )
SlopePlots_1026_chaet


SlopePlots_1026_ply <- ClearanceRate_Master[!is.na(ClearanceRate_Master$PLY_cell.ml),] %>% 
  dplyr::filter(!Replicate %in% 'blank') %>%
  dplyr::filter(Date %in% "20211026") %>% 
  dplyr::mutate(pH_food = paste(pH, Fed_Unfed, sep = '_')) %>% 
  dplyr::mutate(Time._min = as.numeric(as.character(time))) %>% 
  ggplot(aes(time, PLY_cell.ml, color=Replicate)) + 
  geom_point(shape=1, color = "black")+ 
  ggtitle("RAW DATA - PLY: F1s Feeding Rate 20211026")+
  labs(y = expression(Live~algae~cells~"("~cells~mL^{-1}~")"), 
       x = expression(Time~"("~minutes~")")) + 
  theme(plot.title= element_text(size =16, face ="bold", 
                                 lineheight = 8, vjust=1), aspect.ratio=1)+
  stat_smooth(method="lm", se = F) + 
  theme_bw() +
  scale_shape_identity() + 
  facet_wrap( ~ pH_food, scales = "free_x" )
SlopePlots_1026_ply


SlopePlots_1026_lowchla <- ClearanceRate_Master[!is.na(ClearanceRate_Master$Low_chlorophyll_cell.ml),] %>% 
  dplyr::filter(!Replicate %in% 'blank') %>%
  dplyr::filter(Date %in% "20211026") %>% 
  dplyr::mutate(pH_food = paste(pH, Fed_Unfed, sep = '_')) %>% 
  dplyr::mutate(Time._min = as.numeric(as.character(time))) %>% 
  ggplot(aes(time, Low_chlorophyll_cell.ml, color=Replicate)) + 
  geom_point(shape=1, color = "black")+ 
  ggtitle("RAW DATA - Low chl a (seston): F1s Feeding Rate 20211026")+
  labs(y = expression(Live~algae~cells~"("~cells~mL^{-1}~")"), 
       x = expression(Time~"("~minutes~")")) + 
  theme(plot.title= element_text(size =16, face ="bold", 
                                 lineheight = 8, vjust=1), aspect.ratio=1)+
  stat_smooth(method="lm", se = F) + 
  theme_bw() +
  scale_shape_identity() + 
  facet_wrap( ~ pH_food, scales = "free_x" )
SlopePlots_1026_lowchla

ggarrange(SlopePlots_1026_Total_ChaetPly,SlopePlots_1026_chaet, SlopePlots_1026_ply, SlopePlots_1026_lowchla, ncol = 1, nrow = 3)






# Save plots :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

pdf(paste0("C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/ClearanceRates/20210914_figs_tables/20210914_FlowCytometry_rawdata.pdf"), height =10)
ggarrange(SlopePlots_914_Total_ChaetPly,SlopePlots_914_chaet, SlopePlots_914_ply, SlopePlots_914_lowchla, ncol = 1, nrow = 4)
dev.off()

pdf(paste0("C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/ClearanceRates/20210930_figs_tables/20210930_FlowCytometry_rawdata.pdf"), height = 16)
ggarrange(SlopePlots_930_Total_ChaetPly,SlopePlots_930_chaet, SlopePlots_930_ply, SlopePlots_930_lowchla, ncol = 1, nrow = 4)
dev.off()

pdf(paste0("C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/ClearanceRates/20211026_figs_tables/20211026_FlowCytometry_rawdata.pdf"), height = 16)
ggarrange(SlopePlots_1026_Total_ChaetPly,SlopePlots_1026_chaet, SlopePlots_1026_ply, SlopePlots_1026_lowchla, ncol = 1, nrow = 4)
dev.off()
```



## Calculate the blank Clearance rate values for each trial

### CLEARANCE RATE EQUATION

**CR =  CR = V * (ln(C0/Ct)/t - A)**

- **V** == the volume of the vessel
- **t** == time of the trial interval (i.e. 60 minutes or 1 hour)
- **ln(C_0/C_t)** == ratio of the live algae concentration (cells ml-1) at time 0 (C0) and at the elapsed time interval(s) (Ct) - take the natural log of this ratio
- **A** == V * (ln(Blank_0/Blank_t)/t) for the 'blank' values in each treatment, accounts for the sink or stuck algae cells 
- **L** == normalization factor between individuals - here we will use the shell length in mm




```{r Calculate BLANKS and write csv, echo = FALSE}

# **A** == V * (ln(Blank_0/Blank_t)/t) for the 'blank' values in each treatment, accounts for the sink or stuck algae cells 

Blanks.Master <- Master_data[is.na(Master_data$Replicate),] %>% 
                                dplyr::mutate(unique_identifier =
                                                paste(Date, pH, "Run", Run, raw_ID_sample_number, sep ='_'))

loop_BLANKS       <- as.data.frame(unique(Blanks.Master$unique_identifier)) %>%
                            dplyr::rename(ID = "unique(Blanks.Master$unique_identifier)") # call unique identifier tfor the for loop calc of blanks 

meanBLANKS.Master       <- data.frame() 
for (i in 1:nrow(loop_BLANKS)) { # for each unique identifier....
  
  # data loop
  dat <- Blanks.Master %>% 
          dplyr::filter(unique_identifier == loop_BLANKS[i,]) %>% # subset the data out for that ID
          dplyr::arrange(time) # arrange from time 0 to the last recorded time )this is important for the next part of this loop!
    
    # note that in some cases t_init and t_end are not the max and minimum values, respectively - this can alse call bad values due to error or pseudofeces!
    
    #  C0 = concentration at T initial
    #  t_init below (C0), I call a conditional statement based on the first two values 
    #  if the max value of timepoints 0 and 1 is  < than 1.25 * the minimum values ( > than assumed as exaggerated by pseudofeces) - call the MAX - else call the MIN
    
    # parameters
    t_end      <- nrow(dat)
    t_end_min <- nrow(dat) - 3

    
    
    
    # total cells
    C0_Total         <- if ( (max(c(dat[1,]$Total_cell.ml, dat[2,]$Total_cell.ml))) < (1.25*  (min(c(dat[1,]$Total_cell.ml, dat[2,]$Total_cell.ml)))) )  { 
                           C0_Total <-  (max(c(dat[1,]$Total_cell.ml, dat[2,]$Total_cell.ml))) 
                           } else (C0_Total <-  (min(c(dat[1,]$Total_cell.ml, dat[2,]$Total_cell.ml)))) # C0 for the ply 
    
    t0_Total         <- min(dat$time[dat$Total_cell.ml==C0_Total])
    
    
    if (  min(dat$Total_cell.ml[c(t_end_min:t_end)])  <   C0_Total) { # if the minmum value of the last three timepoints is less than the concentration at time 0....
                          Cend_Total <- min(dat$Total_cell.ml[c(t_end_min:t_end)])  # call this value 
                          } else (Cend_Total <- min(dat$Total_cell.ml[t_end])) # ...else just call the last value - it will result in a negative ln() and be ommitted after the loop (below)
    
    
    tot.time_Total   <- max(dat$time[dat$Total_cell.ml==Cend_Total]) - t0_Total
    
    
    
    
    # ply
    C0_Ply         <- if ( (max(c(dat[1,]$PLY_cell.ml, dat[2,]$PLY_cell.ml))) < (1.25*  (min(c(dat[1,]$PLY_cell.ml, dat[2,]$PLY_cell.ml)))) )  { 
                           C0_Ply <-  (max(c(dat[1,]$PLY_cell.ml, dat[2,]$PLY_cell.ml))) 
                           } else (C0_Ply <-  (min(c(dat[1,]$PLY_cell.ml, dat[2,]$PLY_cell.ml)))) # C0 for the ply 
    
    t0_Ply         <- min(dat$time[dat$PLY_cell.ml==C0_Ply])
    
    
    if (  min(dat$PLY_cell.ml[c(t_end_min:t_end)])  <   C0_Ply) { # if the minmum value of the last three timepoints is less than the concentration at time 0....
                          Cend_Ply <- min(dat$PLY_cell.ml[c(t_end_min:t_end)])  # call this value 
                          } else (Cend_Ply <- min(dat$PLY_cell.ml[t_end])) # ...else just call the last value - it will result in a negative ln() and be ommitted after the loop (below)
    
    
    tot.time_Ply   <- max(dat$time[dat$PLY_cell.ml==Cend_Ply]) - t0_Ply

    
    # chaet
    C0_Chaet        <- if ( (max(c(dat[1,]$Chaet_cell.ml, dat[2,]$Chaet_cell.ml))) < (1.25*  (min(c(dat[1,]$Chaet_cell.ml, dat[2,]$Chaet_cell.ml)))) )  { 
                           C0_Chaet <-  (max(c(dat[1,]$Chaet_cell.ml, dat[2,]$Chaet_cell.ml))) 
                           } else (C0_Chaet <-  (min(c(dat[1,]$Chaet_cell.ml, dat[2,]$Chaet_cell.ml)))) 
    
    t0_Chaet        <- min(dat$time[dat$Chaet_cell.ml==C0_Chaet])
    
    if (  min(dat$Chaet_cell.ml[c(t_end_min:t_end)])  <   C0_Ply) { # if the minmum value of the last three timepoints is less than the concentration at time 0....
                          Cend_Chaet <- min(dat$Chaet_cell.ml[c(t_end_min:t_end)])  # call this value 
                          } else (Cend_Chaet <- min(dat$Chaet_cell.ml[t_end])) # ...else just call the last value - it will result in a negative ln() and be ommitted after the loop (below)
    
    tot.time_Chaet  <- max(dat$time[dat$Chaet_cell.ml==Cend_Chaet]) - t0_Chaet
    
    
    # low chl a (seston)
    C0_seston <- if ( (max(c(dat[1,]$Low_chlorophyll_cell.ml, dat[2,]$Low_chlorophyll_cell.ml))) < (1.25*  (min(c(dat[1,]$Low_chlorophyll_cell.ml, dat[2,]$Low_chlorophyll_cell.ml)))) )  { 
                     C0_seston <-  (max(c(dat[1,]$Low_chlorophyll_cell.ml, dat[2,]$Low_chlorophyll_cell.ml))) 
                     } else (C0_seston <-  (min(c(dat[1,]$Low_chlorophyll_cell.ml, dat[2,]$Low_chlorophyll_cell.ml))))  
    t0_seston       <- min(dat$time[dat$Low_chlorophyll_cell.ml==C0_seston])
    
    if (  min(dat$Low_chlorophyll_cell.ml[c(t_end_min:t_end)])  <   C0_Ply) { # if the minmum value of the last three timepoints is less than the concentration at time 0....
                          Cend_seston <- min(dat$Low_chlorophyll_cell.ml[c(t_end_min:t_end)])  # call this value 
                          } else (Cend_seston <- min(dat$Low_chlorophyll_cell.ml[t_end])) # ...else just call the last value - it will result in a negative ln() and be ommitted after the loop (below)
    
    tot.time_seston <- max(dat$time[dat$Low_chlorophyll_cell.ml==Cend_seston]) - t0_seston
    
    # natural log (ln) of the start and end ratio
    Blank_dat <- dat[1,] %>%  
        dplyr::select(c('Date','pH','Fed_Unfed','Run')) %>% 
        dplyr::mutate(CR.Blank_Total  = (ln(C0_Total / Cend_Total) / (tot.time_Total/60) ) ) %>%  # calc the ration of algae lost to the time 0 number 
        dplyr::mutate(CR.Blank_Chaet  = (ln(C0_Chaet / Cend_Chaet) / (tot.time_Chaet/60) ) ) %>%  # calc the ration of algae lost to the time 0 number 
        dplyr::mutate(CR.Blank_Ply    = (ln(C0_Ply / Cend_Ply) / (tot.time_Ply/60) ) ) %>%  # calc the ration of algae lost to the time 0 number 
        dplyr::mutate(CR.Blank_Seston = (ln(C0_seston / Cend_seston)/ (tot.time_seston/60) ) ) # calc the ration of algae lost to the time 0 number 
   
    df                <- data.frame(Blank_dat) # name dataframe for this single row
    meanBLANKS.Master <- rbind(meanBLANKS.Master,df) #bind to a cumulative list dataframe
 } 






#  LETS LOOK AT ALL THE DATA AND ASSESS THE BLANKS FOR OUTLIERS 



# total chlorophyll - view figure of all 
ggplot(aes(x=as.factor(pH), y=CR.Blank_Total, group=as.factor(pH)), data=meanBLANKS.Master) +
  geom_boxplot() +
  theme_bw()+
  geom_point() +
  facet_wrap(~Date)
# - some negatives - make these zero 
# - abnormal high values above 0.7 - omit
meanBLANKS.Master %>% 
  dplyr::mutate(CR.Blank_Total = if_else(CR.Blank_Total < 0, 0, CR.Blank_Total)) %>% # make all negative values 0 
  dplyr::filter(!(CR.Blank_Total > 0.7)) %>%  # omits 3 values greater than 0.7
  ggplot(aes(x=as.factor(pH), y=CR.Blank_Total, group=as.factor(pH))) + # now lets see the fig mang!
  geom_boxplot() +
  theme_bw()+
  geom_point() +
  facet_wrap(~Date)




# chaetoceros
ggplot(aes(x=as.factor(pH), y=CR.Blank_Chaet, group=as.factor(pH)), data=meanBLANKS.Master) +
  geom_boxplot() +
  geom_point() +
  theme_bw()+
  facet_wrap(~Date)
# - make negative values zero 
# - no other changes 
meanBLANKS.Master %>% 
  dplyr::mutate(CR.Blank_Chaet = if_else(CR.Blank_Chaet < 0, 0, CR.Blank_Chaet)) %>% # make all negative values 0 
  ggplot(aes(x=as.factor(pH), y=CR.Blank_Chaet, group=as.factor(pH))) + # now lets see the fig mang!
  geom_boxplot() +
  theme_bw()+
  geom_point() +
  facet_wrap(~Date)





# ply 
ggplot(aes(x=as.factor(pH), y=CR.Blank_Ply, group=as.factor(pH)), data=meanBLANKS.Master) +
  geom_boxplot() +
  theme_bw()+
  geom_point() +
  facet_wrap(~Date)
# - make negative values zero 
# - omit outliers higher than 2.35 (N = 3)
meanBLANKS.Master %>% 
  dplyr::mutate(CR.Blank_Ply = if_else(CR.Blank_Ply < 0, 0, CR.Blank_Ply)) %>% # make all negative values 0 
  dplyr::filter(!(CR.Blank_Ply > 2)) %>%  # omits 3 values greater than 2
  ggplot(aes(x=as.factor(pH), y=CR.Blank_Ply, group=as.factor(pH))) + # now lets see the fig mang!
  geom_boxplot() +
  theme_bw()+
  geom_point() +
  facet_wrap(~Date)







# seston
ggplot(aes(x=as.factor(pH), y=CR.Blank_Seston, group=as.factor(pH)), data=meanBLANKS.Master) +
  geom_boxplot() +
  theme_bw()+
  geom_point() +
  facet_wrap(~Date)
# - make negative values zero 
meanBLANKS.Master %>% 
  dplyr::mutate(CR.Blank_Seston = if_else(CR.Blank_Seston < 0, 0, CR.Blank_Seston)) %>% # make all negative values 0 
 # dplyr::filter(!(CR.Blank_Seston > 2)) %>%  # omits 3 values greater than 2
  ggplot(aes(x=as.factor(pH), y=CR.Blank_Seston, group=as.factor(pH))) + # now lets see the fig mang!
  geom_boxplot() +
  theme_bw()+
  geom_point() +
  facet_wrap(~Date)





meanBLANKS.Total <- data.frame(meanBLANKS.Master) %>% 
                      dplyr::group_by(Date, pH) %>% 
                      mutate(CR.Blank_Total = if_else(CR.Blank_Total < 0, 0, CR.Blank_Total)) %>% # make all negative values 0 
                      dplyr::filter(!(CR.Blank_Total > 0.7)) %>%  # omits 3 values greater than 0.7
                      dplyr::summarise(
                       meanBlank  = mean(CR.Blank_Total),
                       sdBlank    = sd(CR.Blank_Total),
                       n = n()) %>% 
                       dplyr::mutate(Type = 'Total') %>% 
                       dplyr::mutate(Date_pH = paste(Date, pH, sep = '_'))


meanBLANKS.Chaet <- data.frame(meanBLANKS.Master) %>% 
                      dplyr::group_by(Date, pH) %>% 
                      mutate(CR.Blank_Chaet = if_else(CR.Blank_Chaet < 0, 0, CR.Blank_Chaet)) %>% # make all negative values 0 
                      dplyr::summarise(
                       meanBlank  = mean(CR.Blank_Chaet),
                       sdBlank    = sd(CR.Blank_Chaet),
                       n = n()) %>% 
                       dplyr::mutate(Type = 'Chaet') %>% 
                       dplyr::mutate(Date_pH = paste(Date, pH, sep = '_'))

meanBLANKS.Ply   <- data.frame(meanBLANKS.Master) %>% 
                          dplyr::group_by(Date, pH) %>% 
                          mutate(CR.Blank_Ply = if_else(CR.Blank_Ply < 0, 0, CR.Blank_Ply)) %>% # make all negative values 0 ]
                          dplyr::filter(!(CR.Blank_Ply > 2)) %>%  # omits 3 values greater than 2
                          dplyr::summarise(
                           meanBlank  = mean(CR.Blank_Ply),
                           sdBlank    = sd(CR.Blank_Ply),
                           n= n()) %>% 
                          dplyr::mutate(Type = 'Ply') %>% 
                          dplyr::mutate(Date_pH = paste(Date, pH, sep = '_'))
                                      
meanBLANKS.Seson <- data.frame(meanBLANKS.Master) %>% 
                        dplyr::group_by(Date, pH) %>% 
                        mutate(CR.Blank_Seston = if_else(CR.Blank_Seston < 0, 0, CR.Blank_Seston)) %>% # make all negative values 0 
                        dplyr::summarise(
                         meanBlank  = mean(CR.Blank_Seston),
                         sdBlank    = sd(CR.Blank_Seston),
                         n= n()) %>% 
                        dplyr::mutate(Type = 'Seston') %>% 
                        dplyr::mutate(Date_pH = paste(Date, pH, sep = '_'))

meanBLANKS.Summary <- rbind(meanBLANKS.Total,meanBLANKS.Chaet, meanBLANKS.Ply, meanBLANKS.Seson)


write.csv(meanBLANKS.Summary, "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/ClearanceRates/Blanks_Master.csv")

```

# Calculate Clearance Rate 

### Note: the following clusters calculate CR for the start/end Algae counts (i.e. 20210914 time 0 and time 90 minutes; 20210930 time 0 and time 60 minutes)


### CLEARANCE RATE EQUATION

**CR =  CR = V * (ln(C0/Ct)/t - A)**

- **V** == the volume of the vessel
- **t** == time of the trial interval (i.e. 60 minutes or 1 hour)
- **ln(C_0/C_t)** == ratio of the live algae concentration (cells ml-1) at time 0 (C0) and at the elapsed time interval(s) (Ct) - take the natural log of this ratio
- **A** == V * (ln(Blank_0/Blank_t)/t) for the 'blank' values in each treatment, accounts for the sink or stuck algae cells 
- **L** == normalization factor between individuals - here we will use the shell length in mm



## 20210914 Clearance Rate data 

```{r 20210914 CR calc, echo = T}

# ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# Clearance Rate for loop     ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

meanLength_um_914 <- mean(ClearanceRate_Master.914$Length_um) # 2459.597
# Bayne Biology of oyster page 254: "Cranford et al. (2011) reviewed published allometric relationships between
# clearance rate and body size for 21 bivalve species. Average exponents were below expectation: b1⁄41.780.34 for shell length"
bfactor_Length    <- 1.78 

V = 25 # V == Volume of the vessel (in mL as 25 ml)
df_total.914<- data.frame() # start dataframe 
for (i in 1:nrow(loop_914)) {
  dat <- ClearanceRate_Master.914 %>% 
    dplyr::filter(uniq_Identifier == loop_914[i,]) %>% 
    dplyr::mutate(Date_pH = paste(Date, pH, sep = '_')) %>% 
    dplyr::arrange(time)
  
  t_end      <- nrow(dat)
  t_end_min1 <- nrow(dat) - 1
  
  blanks <- meanBLANKS.Summary %>% dplyr::filter(Date_pH %in% dat$Date_pH[1])
  
  
  
    # Total
    A.Total               <- blanks$meanBlank[blanks$Type == 'Total']
   
    C0_Total              <- if ( (max(c(dat[1,]$Total_cell.ml, dat[2,]$Total_cell.ml))) < (1.25*  (min(c(dat[1,]$Total_cell.ml, dat[2,]$Total_cell.ml)))) )  { 
                               C0_Total <-  (max(c(dat[1,]$Total_cell.ml, dat[2,]$Total_cell.ml))) 
                               } else (C0_Total <-  (min(c(dat[1,]$Total_cell.ml, dat[2,]$Total_cell.ml)))) # C0 for the Total 
    
    Cend_Total            <- (min(c(dat[t_end_min1,]$Total_cell.ml, dat[t_end,]$Total_cell.ml)))
    
    t0_Total              <- dat$time[dat$Total_cell.ml==C0_Total]
    
    t_Total               <- max((dat$time[dat$Total_cell.ml==Cend_Total]) - t0_Total) # call max becasue (although unlikely) there can be a case of the same count - calling multiple values
    
    # no corrected
    ClearanceRate.Total           <- (V * ((ln( C0_Total / Cend_Total )/(t_Total/60)) - A.Total)) # Tetraselmis cells mL-1  hr-1 mm 
    # shell length corrected
    ClearanceRate.Total.length    <- (V * ((ln( C0_Total / Cend_Total )/(t_Total/60)) - A.Total)) / (dat$Length_um[1] / 1000) # Tetraselmis cells mL-1  hr-1 mm shell length-1
    # b factor normalized - Bayne value 1.78
    ClearanceRate.Total.bfactor   <- (V * ((ln( C0_Total / Cend_Total )/(t_Total/60)) - A.Total)) *
                                    ((meanLength_um_914 / dat$Length_um[1])^bfactor_Length) # b factor correction 
    
    
  
  
  
  
  # ply
  A.ply               <- blanks$meanBlank[blanks$Type == 'Ply']
 
  C0_Ply              <- if ( (max(c(dat[1,]$PLY_cell.ml, dat[2,]$PLY_cell.ml))) < (1.25*  (min(c(dat[1,]$PLY_cell.ml, dat[2,]$PLY_cell.ml)))) )  { 
                             C0_Ply <-  (max(c(dat[1,]$PLY_cell.ml, dat[2,]$PLY_cell.ml))) 
                             } else (C0_Ply <-  (min(c(dat[1,]$PLY_cell.ml, dat[2,]$PLY_cell.ml)))) # C0 for the ply 
  
  Cend_Ply            <- (min(c(dat[t_end_min1,]$PLY_cell.ml, dat[t_end,]$PLY_cell.ml)))
  
  t0_Ply              <- dat$time[dat$PLY_cell.ml==C0_Ply]
  
  t_Ply               <- max((dat$time[dat$PLY_cell.ml==Cend_Ply]) - t0_Ply) # call max becasue (although unlikely) there can be a case of the same count - calling multiple values
  
  # no corrected
  ClearanceRate.Ply           <- (V * ((ln( C0_Ply / Cend_Ply )/(t_Ply/60)) - A.ply)) # Tetraselmis cells mL-1  hr-1 mm 
  # shell length corrected
  ClearanceRate.Ply.length    <- (V * ((ln( C0_Ply / Cend_Ply )/(t_Ply/60)) - A.ply)) / (dat$Length_um[1] / 1000) # Tetraselmis cells mL-1  hr-1 mm shell length-1
  # b factor normalized - Bayne value 1.78
  ClearanceRate.Ply.bfactor   <- (V * ((ln( C0_Ply / Cend_Ply )/(t_Ply/60)) - A.ply)) *
                                  ((meanLength_um_914 / dat$Length_um[1])^bfactor_Length) # b factor correction 
 
  
  
  
  # chaet
  A.chaet             <- blanks$meanBlank[blanks$Type == 'Chaet']
 
  C0_Chaet            <- if ( (max(c(dat[1,]$Chaet_cell.ml, dat[2,]$Chaet_cell.ml))) < (1.25*  (min(c(dat[1,]$Chaet_cell.ml, dat[2,]$Chaet_cell.ml)))) )  { 
                             C0_Chaet <-  (max(c(dat[1,]$Chaet_cell.ml, dat[2,]$Chaet_cell.ml))) 
                             } else (C0_Chaet <-  (min(c(dat[1,]$Chaet_cell.ml, dat[2,]$Chaet_cell.ml)))) # C0 for the ply 
  
  Cend_Chaet          <- (min(c(dat[t_end_min1,]$Chaet_cell.ml, dat[t_end,]$Chaet_cell.ml)))
  
  t0_Chaet            <- dat$time[dat$Chaet_cell.ml==C0_Chaet]
  
  t_Chaet             <- max((dat$time[dat$Chaet_cell.ml==Cend_Chaet]) - t0_Chaet) # call max becasue (although unlikely) there can be a case of the same count - calling multiple values
  
  
  # no corrected
  ClearanceRate.Chaet          <- (V * ((ln( C0_Chaet / Cend_Chaet )/(t_Chaet/60)) - A.chaet))  
  # shell length corrected
  ClearanceRate.Chaet.length   <- (V * ((ln( C0_Chaet / Cend_Chaet )/(t_Chaet/60)) - A.chaet)) / (dat$Length_um[1] / 1000) # Chaetoceros cells mL-1  hr-1 mm shell length-1
  # b factor normalized - Bayne value 1.78
  ClearanceRate.Chaet.bfactor  <- (V * ((ln( C0_Chaet / Cend_Chaet )/(t_Chaet/60)) - A.chaet)) *
                                  ((meanLength_um_914 / dat$Length_um[1])^bfactor_Length) # b factor correction 
    
  
  
  
  # low chl a (seston)
  A.Seston             <- blanks$meanBlank[blanks$Type == 'Seston']
 
  C0_Seston            <- if ( (max(c(dat[1,]$Low_chlorophyll_cell.ml, dat[2,]$Low_chlorophyll_cell.ml))) < (1.25*  (min(c(dat[1,]$Low_chlorophyll_cell.ml, dat[2,]$Low_chlorophyll_cell.ml)))) )  { 
                             C0_Seston <-  (max(c(dat[1,]$Low_chlorophyll_cell.ml, dat[2,]$Low_chlorophyll_cell.ml))) 
                             } else (C0_Seston <-  (min(c(dat[1,]$Low_chlorophyll_cell.ml, dat[2,]$Low_chlorophyll_cell.ml)))) # C0 for the ply 
  
  Cend_Seston          <- (min(c(dat[t_end_min1,]$Low_chlorophyll_cell.ml, dat[t_end,]$Low_chlorophyll_cell.ml)))
  
  t0_Seston            <- dat$time[dat$Low_chlorophyll_cell.ml==C0_Seston]
  
  t_Seston             <- max((dat$time[dat$Low_chlorophyll_cell.ml==Cend_Seston]) - t0_Seston) # call max becasue (although unlikely) there can be a case of the same count - calling multiple values
  
  # no corrected
  ClearanceRate.Seston         <- (V * ((ln( C0_Seston / Cend_Seston )/(t_Seston/60)) - A.Seston))   
  # shell length corrected
  ClearanceRate.Seston.length  <- (V * ((ln( C0_Seston / Cend_Seston )/(t_Seston/60)) - A.Seston)) / (dat$Length_um[1] / 1000) # seston cells mL-1  hr-1 mm shell length-1
  # b factor normalized - Bayne value 1.78
  ClearanceRate.Seston.bfactor <- (V * ((ln( C0_Seston / Cend_Seston )/(t_Seston/60)) - A.Seston)) *
                                  ((meanLength_um_914 / dat$Length_um[1])^bfactor_Length) # b factor correction 
  
  
  dat2 <- dat[1,] %>%
    dplyr::select(c('Date','pH', 'Replicate', 'Fed_Unfed','Run', 'Plate', 'Number', 'Length_um')) %>% 
    
    
    mutate(Total_mL.hr            = ClearanceRate.Total) %>% 
    mutate(Total_mL.hr.mmlength   = ClearanceRate.Total.length) %>% 
    mutate(Total_mL.hr.bfactor    = ClearanceRate.Total.bfactor) %>% 
    
    mutate(Ply_mL.hr            = ClearanceRate.Ply) %>% 
    mutate(Ply_mL.hr.mmlength   = ClearanceRate.Ply.length) %>% 
    mutate(Ply_mL.hr.bfactor    = ClearanceRate.Ply.bfactor) %>% 
    
    mutate(Chaet_mL.hr          = ClearanceRate.Chaet) %>% 
    mutate(Chaet_mL.hr.mmlength = ClearanceRate.Chaet.length) %>% 
    mutate(Chaet_mL.hr.bfactor  = ClearanceRate.Chaet.bfactor) %>% 
    
    mutate(Seston_mL.hr          = ClearanceRate.Seston) %>% 
    mutate(Seston_mL.hr.mmlength = ClearanceRate.Seston.length) %>% 
    mutate(Seston_mL.hr.bfactor  = ClearanceRate.Seston.bfactor) 

    
  if (nrow(dat2) > 0) {
    CR.table           <- data.frame(matrix(nrow = nrow(dat2), ncol = 21)) # create dataframe to save cumunalitively during for loop
    colnames(CR.table) <- c('Date', 'ID', 'pH', 'Replicate', 'Fed_Unfed','Run', 'Plate', 'Number', 'Length_um', 
                                  'Total_mL.hr','Total_mL.hr.mmlength', 'Total_mL.hr.bfactor', 
                                  'Chaet_mL.hr','Chaet_mL.hr.mmlength', 'Chaet_mL.hr.bfactor', 
                                  'Ply_mL.hr', 'Ply_mL.hr.mmlength', 'Ply_mL.hr.bfactor',
                                   'Seston_mL.hr','Seston_mL.hr.mmlength','Seston_mL.hr.bfactor') 
    CR.table$Date                       <- dat2$Date
    CR.table$ID                         <- loop_914[i,]
    CR.table$pH                         <- gsub("_.*", "\\1", CR.table$ID)
    CR.table$Replicate                  <- gsub("^(?:[^_]+_){4}([^_]+).*", "\\1", CR.table$ID)
    CR.table$Fed_Unfed                  <- dat2$Fed_Unfed
    CR.table$Run                        <- gsub("^(?:[^_]+_){2}([^_]+).*", "\\1", CR.table$ID)
    CR.table$Plate                      <- dat2$Plate
    CR.table$Number                     <- gsub("^(?:[^_]+_){6}([^_]+).*", "\\1", CR.table$ID)
    CR.table$Length_um                  <- dat2$Length_um
    
    CR.table$Total_mL.hr                <- dat2$Total_mL.hr
    CR.table$Total_mL.hr.mmlength       <- dat2$Total_mL.hr.mmlength
    CR.table$Total_mL.hr.bfactor        <- dat2$Total_mL.hr.bfactor
    
    CR.table$Ply_mL.hr                  <- dat2$Ply_mL.hr
    CR.table$Ply_mL.hr.mmlength         <- dat2$Ply_mL.hr.mmlength
    CR.table$Ply_mL.hr.bfactor          <- dat2$Ply_mL.hr.bfactor
    
    CR.table$Chaet_mL.hr                <- dat2$Chaet_mL.hr
    CR.table$Chaet_mL.hr.mmlength       <- dat2$Chaet_mL.hr.mmlength
    CR.table$Chaet_mL.hr.bfactor        <- dat2$Chaet_mL.hr.bfactor
    
    CR.table$Seston_mL.hr               <- dat2$Seston_mL.hr
    CR.table$Seston_mL.hr.mmlength      <- dat2$Seston_mL.hr.mmlength
    CR.table$Seston_mL.hr.bfactor       <- dat2$Seston_mL.hr.bfactor
    
    df       <- data.frame(CR.table) # name dataframe for this single row
    df_total.914 <- rbind(df_total.914,df) #bind to a cumulative list dataframe
    #print(df_total.914) # print to monitor progress
  } else {}
}


# ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# clean & view means...       ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

df_total.914 <- df_total.914  %>% 
  dplyr::mutate(pCO2 = case_when(pH == 8.0 ~ "500 μatm", pH == 7.5 ~ "800 μatm")) %>% 
  dplyr::mutate(random_fact = as.factor(paste(Replicate, pH, sep = '_')))


Total_CR_914_Means <- df_total.914 %>% 
  dplyr::group_by(pCO2) %>% 
  dplyr::filter(Total_mL.hr.mmlength > 0) %>% # ommit negative values
  dplyr::summarise(
    Total_meanCR = mean(Total_mL.hr.mmlength),
    Total_sdCR   = sd(Total_mL.hr.mmlength), 
    Total_seCR   = sd(Total_mL.hr.mmlength) / sqrt(length(Total_mL.hr.mmlength)), 
    n = n())
print(Total_CR_914_Means)


Ply_CR_914_Means <- df_total.914 %>% 
  dplyr::group_by(pCO2) %>% 
  dplyr::filter(Ply_mL.hr.mmlength > 0) %>% # ommit negative values
  dplyr::summarise(
    Ply_meanCR = mean(Ply_mL.hr.mmlength),
    Ply_sdCR   = sd(Ply_mL.hr.mmlength), 
    Ply_seCR   = sd(Ply_mL.hr.mmlength) / sqrt(length(Ply_mL.hr.mmlength)), 
    n = n())
print(Ply_CR_914_Means)

Chaet_CR_914_Means <- df_total.914 %>% 
  dplyr::group_by(pCO2) %>% 
  dplyr::filter(Chaet_mL.hr.bfactor > 0) %>% # ommit negative values
  dplyr::summarise(
    Chaet_meanCR = mean(Chaet_mL.hr.bfactor),
    Chaet_sdCR   = sd(Chaet_mL.hr.bfactor), 
    Chaet_seCR   = sd(Chaet_mL.hr.bfactor) / sqrt(length(Chaet_mL.hr.bfactor)), 
    n = n())
print(Chaet_CR_914_Means)


Seston_CR_914_Means <- df_total.914 %>% 
  dplyr::group_by(pCO2) %>% 
  dplyr::filter(Seston_mL.hr.bfactor > 0) %>% # ommit negative values
  dplyr::summarise(
    Seston_meanCR = mean(Seston_mL.hr.bfactor),
    Seston_sdCR   = sd(Seston_mL.hr.bfactor), 
    Seston_seCR   = sd(Seston_mL.hr.bfactor) / sqrt(length(Seston_mL.hr.bfactor)), 
    n = n())
print(Seston_CR_914_Means)

```





## 20210930 Clearance Rate data 

```{r 20210930 CR, echo = T}

# ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# Clearance Rate for loop     ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

meanLength_um_930 <- mean(ClearanceRate_Master.930$Length_um) # 3352.054
# Bayne Biology of oyster page 254: "Cranford et al. (2011) reviewed published allometric relationships between
# clearance rate and body size for 21 bivalve species. Average exponents were below expectation: b1⁄41.780.34 for shell length"
bfactor_Length    <- 1.78 

V = 25 # V == Volume of the vessel (in mL as 25 ml)
df_total.930<- data.frame() # start dataframe 
for (i in 1:nrow(loop_930)) {
  dat <- ClearanceRate_Master.930 %>% 
    dplyr::filter(uniq_Identifier == loop_930[i,]) %>% 
    dplyr::mutate(Date_pH = paste(Date, pH, sep = '_')) %>% 
    dplyr::arrange(time)
  
  t_end      <- nrow(dat)
  t_end_min1 <- nrow(dat) - 1
  
  blanks <- meanBLANKS.Summary %>% dplyr::filter(Date_pH %in% dat$Date_pH[1])
  
  
  
  
    # Total
    A.Total               <- blanks$meanBlank[blanks$Type == 'Total']
   
    C0_Total              <- if ( (max(c(dat[1,]$Total_cell.ml, dat[2,]$Total_cell.ml))) < (1.25*  (min(c(dat[1,]$Total_cell.ml, dat[2,]$Total_cell.ml)))) )  { 
                               C0_Total <-  (max(c(dat[1,]$Total_cell.ml, dat[2,]$Total_cell.ml))) 
                               } else (C0_Total <-  (min(c(dat[1,]$Total_cell.ml, dat[2,]$Total_cell.ml)))) # C0 for the Total 
    
    Cend_Total            <- (min(c(dat[t_end_min1,]$Total_cell.ml, dat[t_end,]$Total_cell.ml)))
    
    t0_Total              <- dat$time[dat$Total_cell.ml==C0_Total]
    
    t_Total               <- max((dat$time[dat$Total_cell.ml==Cend_Total]) - t0_Total) # call max becasue (although unlikely) there can be a case of the same count - calling multiple values
    
    # no corrected
    ClearanceRate.Total           <- (V * ((ln( C0_Total / Cend_Total )/(t_Total/60)) - A.Total)) # Tetraselmis cells mL-1  hr-1 mm 
    # shell length corrected
    ClearanceRate.Total.length    <- (V * ((ln( C0_Total / Cend_Total )/(t_Total/60)) - A.Total)) / (dat$Length_um[1] / 1000) # Tetraselmis cells mL-1  hr-1 mm shell length-1
    # b factor normalized - Bayne value 1.78
    ClearanceRate.Total.bfactor   <- (V * ((ln( C0_Total / Cend_Total )/(t_Total/60)) - A.Total)) *
                                    ((meanLength_um_930 / dat$Length_um[1])^bfactor_Length) # b factor correction 
    
    
    
  # ply
  A.ply               <- blanks$meanBlank[blanks$Type == 'Ply']
 
  C0_Ply              <- if ( (max(c(dat[1,]$PLY_cell.ml, dat[2,]$PLY_cell.ml))) < (1.25*  (min(c(dat[1,]$PLY_cell.ml, dat[2,]$PLY_cell.ml)))) )  { 
                             C0_Ply <-  (max(c(dat[1,]$PLY_cell.ml, dat[2,]$PLY_cell.ml))) 
                             } else (C0_Ply <-  (min(c(dat[1,]$PLY_cell.ml, dat[2,]$PLY_cell.ml)))) # C0 for the ply 
  
  Cend_Ply            <- (min(c(dat[t_end_min1,]$PLY_cell.ml, dat[t_end,]$PLY_cell.ml)))
  
  t0_Ply              <- dat$time[dat$PLY_cell.ml==C0_Ply]
  
  t_Ply               <- max((dat$time[dat$PLY_cell.ml==Cend_Ply]) - t0_Ply) # call max becasue (although unlikely) there can be a case of the same count - calling multiple values
  
  
  # no corrected
  ClearanceRate.Ply           <- (V * ((ln( C0_Ply / Cend_Ply )/(t_Ply/60)) - A.ply)) # Tetraselmis cells mL-1  hr-1 mm 
  # shell length corrected
  ClearanceRate.Ply.length    <- (V * ((ln( C0_Ply / Cend_Ply )/(t_Ply/60)) - A.ply)) / (dat$Length_um[1] / 1000) # Tetraselmis cells mL-1  hr-1 mm shell length-1
  # b factor normalized - Bayne value 1.78
  ClearanceRate.Ply.bfactor   <- (V * ((ln( C0_Ply / Cend_Ply )/(t_Ply/60)) - A.ply)) *
                                  ((meanLength_um_930 / dat$Length_um[1])^bfactor_Length) # b factor correction 

  # chaet
  A.chaet             <- blanks$meanBlank[blanks$Type == 'Chaet']
 
  C0_Chaet            <- if ( (max(c(dat[1,]$Chaet_cell.ml, dat[2,]$Chaet_cell.ml))) < (1.25*  (min(c(dat[1,]$Chaet_cell.ml, dat[2,]$Chaet_cell.ml)))) )  { 
                             C0_Chaet <-  (max(c(dat[1,]$Chaet_cell.ml, dat[2,]$Chaet_cell.ml))) 
                             } else (C0_Chaet <-  (min(c(dat[1,]$Chaet_cell.ml, dat[2,]$Chaet_cell.ml)))) # C0 for the ply 
  
  Cend_Chaet          <- (min(c(dat[t_end_min1,]$Chaet_cell.ml, dat[t_end,]$Chaet_cell.ml)))
  
  t0_Chaet            <- dat$time[dat$Chaet_cell.ml==C0_Chaet]
  
  t_Chaet             <- max((dat$time[dat$Chaet_cell.ml==Cend_Chaet]) - t0_Chaet) # call max becasue (although unlikely) there can be a case of the same count - calling multiple values
  
  
  # no corrected
  ClearanceRate.Chaet          <- (V * ((ln( C0_Chaet / Cend_Chaet )/(t_Chaet/60)) - A.chaet))  
  # shell length corrected
  ClearanceRate.Chaet.length   <- (V * ((ln( C0_Chaet / Cend_Chaet )/(t_Chaet/60)) - A.chaet)) / (dat$Length_um[1] / 1000) # Chaetoceros cells mL-1  hr-1 mm shell length-1
  # b factor normalized - Bayne value 1.78
  ClearanceRate.Chaet.bfactor  <- (V * ((ln( C0_Chaet / Cend_Chaet )/(t_Chaet/60)) - A.chaet)) *
                                  ((meanLength_um_930 / dat$Length_um[1])^bfactor_Length) # b factor correction 

    
  # low chl a (seston)
  A.Seston             <- blanks$meanBlank[blanks$Type == 'Seston']
 
  C0_Seston            <- if ( (max(c(dat[1,]$Low_chlorophyll_cell.ml, dat[2,]$Low_chlorophyll_cell.ml))) < (1.25*  (min(c(dat[1,]$Low_chlorophyll_cell.ml, dat[2,]$Low_chlorophyll_cell.ml)))) )  { 
                             C0_Seston <-  (max(c(dat[1,]$Low_chlorophyll_cell.ml, dat[2,]$Low_chlorophyll_cell.ml))) 
                             } else (C0_Seston <-  (min(c(dat[1,]$Low_chlorophyll_cell.ml, dat[2,]$Low_chlorophyll_cell.ml)))) # C0 for the ply 
  
  Cend_Seston          <- (min(c(dat[t_end_min1,]$Low_chlorophyll_cell.ml, dat[t_end,]$Low_chlorophyll_cell.ml)))
  
  t0_Seston            <- dat$time[dat$Low_chlorophyll_cell.ml==C0_Seston]
  
  t_Seston             <- max((dat$time[dat$Low_chlorophyll_cell.ml==Cend_Seston]) - t0_Seston) # call max becasue (although unlikely) there can be a case of the same count - calling multiple values
  
  
  
  # no corrected
  ClearanceRate.Seston         <- (V * ((ln( C0_Seston / Cend_Seston )/(t_Seston/60)) - A.Seston))   
  # shell length corrected
  ClearanceRate.Seston.length  <- (V * ((ln( C0_Seston / Cend_Seston )/(t_Seston/60)) - A.Seston)) / (dat$Length_um[1] / 1000) # seston cells mL-1  hr-1 mm shell length-1
  # b factor normalized - Bayne value 1.78
  ClearanceRate.Seston.bfactor <- (V * ((ln( C0_Seston / Cend_Seston )/(t_Seston/60)) - A.Seston)) *
                                  ((meanLength_um_930 / dat$Length_um[1])^bfactor_Length) # b factor correction 

  
  dat2 <- dat[1,] %>%
    dplyr::select(c('Date','pH', 'Replicate', 'Fed_Unfed','Run', 'Plate', 'Number', 'Length_um')) %>% 
    
    mutate(Total_mL.hr            = ClearanceRate.Total) %>% 
    mutate(Total_mL.hr.mmlength   = ClearanceRate.Total.length) %>% 
    mutate(Total_mL.hr.bfactor    = ClearanceRate.Total.bfactor) %>% 
    
    mutate(Ply_mL.hr            = ClearanceRate.Ply) %>% 
    mutate(Ply_mL.hr.mmlength   = ClearanceRate.Ply.length) %>% 
    mutate(Ply_mL.hr.bfactor    = ClearanceRate.Ply.bfactor) %>% 
    
    mutate(Chaet_mL.hr          = ClearanceRate.Chaet) %>% 
    mutate(Chaet_mL.hr.mmlength = ClearanceRate.Chaet.length) %>% 
    mutate(Chaet_mL.hr.bfactor  = ClearanceRate.Chaet.bfactor) %>% 
    
    mutate(Seston_mL.hr          = ClearanceRate.Seston) %>% 
    mutate(Seston_mL.hr.mmlength = ClearanceRate.Seston.length) %>% 
    mutate(Seston_mL.hr.bfactor  = ClearanceRate.Seston.bfactor) 
    
  if (nrow(dat2) > 0) {
    CR.table           <- data.frame(matrix(nrow = nrow(dat2), ncol = 21)) # create dataframe to save cumunalitively during for loop
    colnames(CR.table) <- c('Date', 'ID', 'pH', 'Replicate', 'Fed_Unfed','Run', 'Plate', 'Number', 'Length_um', 
                                  'Total_mL.hr','Total_mL.hr.mmlength', 'Total_mL.hr.bfactor', 
                                  'Chaet_mL.hr','Chaet_mL.hr.mmlength', 'Chaet_mL.hr.bfactor', 
                                  'Ply_mL.hr', 'Ply_mL.hr.mmlength', 'Ply_mL.hr.bfactor',
                                   'Seston_mL.hr','Seston_mL.hr.mmlength','Seston_mL.hr.bfactor') 
    CR.table$Date                       <- dat2$Date
    CR.table$ID                         <- loop_930[i,]
    CR.table$pH                         <- gsub("_.*", "\\1", CR.table$ID)
    CR.table$Replicate                  <- gsub("^(?:[^_]+_){4}([^_]+).*", "\\1", CR.table$ID)
    CR.table$Fed_Unfed                  <- dat2$Fed_Unfed
    CR.table$Run                        <- gsub("^(?:[^_]+_){2}([^_]+).*", "\\1", CR.table$ID)
    CR.table$Plate                      <- dat2$Plate
    CR.table$Number                     <- gsub("^(?:[^_]+_){6}([^_]+).*", "\\1", CR.table$ID)
    CR.table$Length_um                  <- dat2$Length_um
    
    CR.table$Total_mL.hr                <- dat2$Total_mL.hr
    CR.table$Total_mL.hr.mmlength       <- dat2$Total_mL.hr.mmlength
    CR.table$Total_mL.hr.bfactor        <- dat2$Total_mL.hr.bfactor
    
    CR.table$Ply_mL.hr                  <- dat2$Ply_mL.hr
    CR.table$Ply_mL.hr.mmlength         <- dat2$Ply_mL.hr.mmlength
    CR.table$Ply_mL.hr.bfactor          <- dat2$Ply_mL.hr.bfactor
    
    CR.table$Chaet_mL.hr                <- dat2$Chaet_mL.hr
    CR.table$Chaet_mL.hr.mmlength       <- dat2$Chaet_mL.hr.mmlength
    CR.table$Chaet_mL.hr.bfactor        <- dat2$Chaet_mL.hr.bfactor
    
    CR.table$Seston_mL.hr               <- dat2$Seston_mL.hr
    CR.table$Seston_mL.hr.mmlength      <- dat2$Seston_mL.hr.mmlength
    CR.table$Seston_mL.hr.bfactor       <- dat2$Seston_mL.hr.bfactor
    
    df       <- data.frame(CR.table) # name dataframe for this single row
    df_total.930 <- rbind(df_total.930,df) #bind to a cumulative list dataframe
    #print(df_total.930) # print to monitor progress
  } else {}
}


# ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# clean & view means...       ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

df_total.930 <- df_total.930  %>% 
  dplyr::mutate(pCO2 = case_when(pH == 8.0 ~ "500 μatm", pH == 7.5 ~ "800 μatm")) %>% 
  dplyr::mutate(random_fact = as.factor(paste(Replicate, pH, Fed_Unfed, sep = '_')))

Total_CR_930_Means <- df_total.930 %>% 
  dplyr::group_by(pCO2,Fed_Unfed) %>% 
  dplyr::filter(Total_mL.hr.mmlength > 0) %>% # ommit negative values
  dplyr::summarise(
    Total_meanCR = mean(Total_mL.hr.mmlength),
    Total_sdCR   = sd(Total_mL.hr.mmlength), 
    Total_seCR   = sd(Total_mL.hr.mmlength) / sqrt(length(Total_mL.hr.mmlength)), 
    n = n())
print(Total_CR_930_Means)


Ply_CR_930_Means <- df_total.930 %>% 
  dplyr::group_by(pCO2, Fed_Unfed) %>% 
  dplyr::filter(Ply_mL.hr.bfactor > 0) %>% # ommit negative values
  dplyr::summarise(
    Ply_meanCR = mean(Ply_mL.hr.bfactor),
    Ply_sdCR   = sd(Ply_mL.hr.bfactor), 
    Ply_seCR   = sd(Ply_mL.hr.bfactor) / sqrt(length(Ply_mL.hr.bfactor)), 
    n = n())
print(Ply_CR_930_Means)

Chaet_CR_930_Means <- df_total.930 %>% 
  dplyr::group_by(pCO2, Fed_Unfed) %>% 
  dplyr::filter(Chaet_mL.hr.bfactor > 0) %>% # ommit negative values
  dplyr::summarise(
    Chaet_meanCR = mean(Chaet_mL.hr.bfactor),
    Chaet_sdCR   = sd(Chaet_mL.hr.bfactor), 
    Chaet_seCR   = sd(Chaet_mL.hr.bfactor) / sqrt(length(Chaet_mL.hr.bfactor)), 
    n = n())
print(Chaet_CR_930_Means)


Seston_CR_930_Means <- df_total.930 %>% 
  dplyr::group_by(pCO2, Fed_Unfed) %>% 
  dplyr::filter(Seston_mL.hr.bfactor > 0) %>% # ommit negative values
  dplyr::summarise(
    Seston_meanCR = mean(Seston_mL.hr.bfactor),
    Seston_sdCR   = sd(Seston_mL.hr.bfactor), 
    Seston_seCR   = sd(Seston_mL.hr.bfactor) / sqrt(length(Seston_mL.hr.bfactor)), 
    n = n())
print(Seston_CR_930_Means)


```





## 20211026 Clearance Rate data 

NOTE: the calculation here changes from the other tiepoints due to **complete clearance of algae in larger/older individuals!** 
if the 0 value is kept it will become 'Inf' due to negative denominator in the natural log... in ln(C_init / C_end)
thus I wrote a conditional statement (if else) for these negative values - making them equal to 0.0001 for this ratio
the alternative can be to call the nearest non-zero value in line


```{r 20211026 CR, echo = T}



# ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# Clearance Rate for loop     ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

meanLength_um_1026 <- mean(ClearanceRate_Master.1026$Length_um) # 7130.816
# Bayne Biology of oyster page 254: "Cranford et al. (2011) reviewed published allometric relationships between
# clearance rate and body size for 21 bivalve species. Average exponents were below expectation: b1⁄41.780.34 for shell length"
bfactor_Length     <- 1.78 

V = 25 # V == Volume of the vessel (in mL as 25 ml)
df_total.1026<- data.frame() # start dataframe 
for (i in 1:nrow(loop_1026)) {
  dat <- ClearanceRate_Master.1026 %>% 
    dplyr::filter(uniq_Identifier == loop_1026[i,]) %>% 
    dplyr::mutate(Date_pH = paste(Date, pH, sep = '_')) %>% 
    dplyr::arrange(time)
  
  t_end      <- nrow(dat)
  t_end_min1 <- nrow(dat) - 2
  
  blanks <- meanBLANKS.Summary %>% dplyr::filter(Date_pH %in% dat$Date_pH[1])
  
  
  
  
    # Total
  A.Total               <- blanks$meanBlank[blanks$Type == 'Total']
 
  C0_Total              <- max(dat$Total_cell.ml[c(1:2)])
  
  Cend_Total            <- min(dat$Total_cell.ml[c(t_end_min1:t_end)])
  
  t0_Total              <- dat$time[dat$Total_cell.ml==C0_Total]
  
  t_Total               <- max(  (min(dat$time[dat$Total_cell.ml==Cend_Total])) - t0_Total) # call max becasue (although unlikely) there can be a case of the same count - calling multiple values
  
  # no correction
  if (Cend_Total == 0) { 
        ClearanceRate.Total <- (V * ((ln( C0_Total / 0.0001 )/(t_Total/60)) - A.Total)) # Chaetoceros cells mL-1  hr-1 mm shell length-1
         } else ( ClearanceRate.Total <- (V * ((ln( C0_Total / Cend_Total )/(t_Total/60)) - A.Total)))
  # shell length corrected
  if (Cend_Total == 0) { 
        ClearanceRate.Total.length <- (V * ((ln( C0_Total / 0.0001 )/(t_Total/60)) - A.Total)) / (dat$Length_um[1] / 1000) # Chaetoceros cells mL-1  hr-1 mm shell length-1
         } else ( ClearanceRate.Total.length <- (V * ((ln( C0_Total / Cend_Total )/(t_Total/60)) - A.Total)) / (dat$Length_um[1] / 1000))
  # b factor normalized - Bayne value 1.78
  if (Cend_Total == 0) { 
        ClearanceRate.Total.bfactor <- (V * ((ln( C0_Total / 0.0001 )/(t_Total/60)) - A.Total)) * ((meanLength_um_1026 / dat$Length_um[1])^bfactor_Length) # b factor correction  # Chaetoceros cells mL-1  hr-1 mm shell length-1
         } else ( ClearanceRate.Total.bfactor <- (V * ((ln( C0_Total / Cend_Total )/(t_Total/60)) - A.Total)) * ((meanLength_um_1026 / dat$Length_um[1])^bfactor_Length) )# b factor correction  # Chaetoceros cells mL-1  hr-1 mm shell length-1
  
  
  
  
  # ply
  A.ply               <- blanks$meanBlank[blanks$Type == 'Ply']
 
  C0_Ply              <- max(dat$PLY_cell.ml[c(1:2)])
  
  Cend_Ply            <- min(dat$PLY_cell.ml[c(t_end_min1:t_end)])
  
  t0_Ply              <- dat$time[dat$PLY_cell.ml==C0_Ply]
  
  t_Ply               <- max(  (min(dat$time[dat$PLY_cell.ml==Cend_Ply])) - t0_Ply) # call max becasue (although unlikely) there can be a case of the same count - calling multiple values
  
  # no correction
  if (Cend_Ply == 0) { 
        ClearanceRate.Ply <- (V * ((ln( C0_Ply / 0.0001 )/(t_Ply/60)) - A.ply)) # Chaetoceros cells mL-1  hr-1 mm shell length-1
         } else ( ClearanceRate.Ply <- (V * ((ln( C0_Ply / Cend_Ply )/(t_Ply/60)) - A.ply)))
  # shell length corrected
  if (Cend_Ply == 0) { 
        ClearanceRate.Ply.length <- (V * ((ln( C0_Ply / 0.0001 )/(t_Ply/60)) - A.ply)) / (dat$Length_um[1] / 1000) # Chaetoceros cells mL-1  hr-1 mm shell length-1
         } else ( ClearanceRate.Ply.length <- (V * ((ln( C0_Ply / Cend_Ply )/(t_Ply/60)) - A.ply)) / (dat$Length_um[1] / 1000))
  # b factor normalized - Bayne value 1.78
  if (Cend_Ply == 0) { 
        ClearanceRate.Ply.bfactor <- (V * ((ln( C0_Ply / 0.0001 )/(t_Ply/60)) - A.ply)) * ((meanLength_um_1026 / dat$Length_um[1])^bfactor_Length) # b factor correction  # Chaetoceros cells mL-1  hr-1 mm shell length-1
         } else ( ClearanceRate.Ply.bfactor <- (V * ((ln( C0_Ply / Cend_Ply )/(t_Ply/60)) - A.ply)) * ((meanLength_um_1026 / dat$Length_um[1])^bfactor_Length) )# b factor correction  # Chaetoceros cells mL-1  hr-1 mm shell length-1
  
  # chaet
  A.chaet             <- blanks$meanBlank[blanks$Type == 'Chaet']
 
  C0_Chaet            <- max(dat$Chaet_cell.ml[c(1:2)])
  
  Cend_Chaet          <- min(dat$Chaet_cell.ml[c(t_end_min1:t_end)])
  
  t0_Chaet            <- dat$time[dat$Chaet_cell.ml==C0_Chaet]
  
  t_Chaet             <- max((dat$time[dat$Chaet_cell.ml==Cend_Chaet]) - t0_Chaet) # call max becasue (although unlikely) there can be a case of the same count - calling multiple values
  
  
  # no correction
  if (Cend_Chaet == 0) {  
    ClearanceRate.Chaet <- (V * ((ln( C0_Chaet / 0.0001 )/(t_Chaet/60)) - A.chaet)) # Chaetoceros cells mL-1  hr-1 mm shell length-1
         } else ( ClearanceRate.Chaet <- (V * ((ln( C0_Chaet / Cend_Chaet )/(t_Chaet/60)) - A.chaet)))
  # shell length corrected
  if (Cend_Chaet == 0) {  
    ClearanceRate.Chaet.length <- (V * ((ln( C0_Chaet / 0.0001 )/(t_Chaet/60)) - A.chaet)) / (dat$Length_um[1] / 1000) # Chaetoceros cells mL-1  hr-1 mm shell length-1
         } else ( ClearanceRate.Chaet.length <- (V * ((ln( C0_Chaet / Cend_Chaet )/(t_Chaet/60)) - A.chaet)) / (dat$Length_um[1] / 1000))
  # b factor normalized - Bayne value 1.78
    if (Cend_Chaet == 0) {  
    ClearanceRate.Chaet.bfactor <- (V * ((ln( C0_Chaet / 0.0001 )/(t_Chaet/60)) - A.chaet)) * ((meanLength_um_1026 / dat$Length_um[1])^bfactor_Length) # b factor correction  # Chaetoceros cells mL-1  hr-1 mm shell length-1
         } else ( ClearanceRate.Chaet.bfactor <- (V * ((ln( C0_Chaet / Cend_Chaet )/(t_Chaet/60)) - A.chaet)) * ((meanLength_um_1026 / dat$Length_um[1])^bfactor_Length) )# b factor correction  # Chaetoceros cells mL-1  hr-1 mm shell length-1
  
  # low chl a (seston)
  A.Seston             <- blanks$meanBlank[blanks$Type == 'Seston']
 
  C0_Seston            <- max(dat$Low_chlorophyll_cell.ml[c(1:2)])
  
  Cend_Seston          <- min(dat$Low_chlorophyll_cell.ml[c(t_end_min1:t_end)])
  
  t0_Seston            <- dat$time[dat$Low_chlorophyll_cell.ml==C0_Seston]
  
  t_Seston             <- max((dat$time[dat$Low_chlorophyll_cell.ml==Cend_Seston]) - t0_Seston) # call max becasue (although unlikely) there can be a case of the same count - calling multiple values
  
  
  
  # no correction
    if (Cend_Seston == 0) {  
    ClearanceRate.Seston <- (V * ((ln( C0_Seston / 0.0001 )/(t_Seston/60)) - A.Seston)) # Chaetoceros cells mL-1  hr-1 mm shell length-1
         } else ( ClearanceRate.Seston <- (V * ((ln( C0_Seston / Cend_Seston )/(t_Seston/60)) - A.Seston)))
  # shell length corrected
    if (Cend_Seston == 0) {  
    ClearanceRate.Seston.length <- (V * ((ln( C0_Seston / 0.0001 )/(t_Seston/60)) - A.Seston)) / (dat$Length_um[1] / 1000) # Chaetoceros cells mL-1  hr-1 mm shell length-1
         } else ( ClearanceRate.Seston.length <- (V * ((ln( C0_Seston / Cend_Seston )/(t_Seston/60)) - A.Seston)) / (dat$Length_um[1] / 1000))
  # b factor normalized - Bayne value 1.78
    if (Cend_Seston == 0) {  
    ClearanceRate.Seston.bfactor <- (V * ((ln( C0_Seston / 0.0001 )/(t_Seston/60)) - A.Seston)) * ((meanLength_um_1026 / dat$Length_um[1])^bfactor_Length) # b factor correction  # Chaetoceros cells mL-1  hr-1 mm shell length-1
         } else ( ClearanceRate.Seston.bfactor <- (V * ((ln( C0_Seston / Cend_Seston )/(t_Seston/60)) - A.Seston)) * ((meanLength_um_1026 / dat$Length_um[1])^bfactor_Length) )# b factor correction  # Chaetoceros cells mL-1  hr-1 mm shell length-1
  
  
  dat2 <- dat[1,] %>%
    dplyr::select(c('Date','pH', 'Replicate', 'Fed_Unfed','Run', 'Plate', 'Number', 'Length_um')) %>% 
    
    
    mutate(Total_mL.hr            = ClearanceRate.Total) %>% 
    mutate(Total_mL.hr.mmlength   = ClearanceRate.Total.length) %>% 
    mutate(Total_mL.hr.bfactor    = ClearanceRate.Total.bfactor) %>% 
    
    mutate(Ply_mL.hr            = ClearanceRate.Ply) %>% 
    mutate(Ply_mL.hr.mmlength   = ClearanceRate.Ply.length) %>% 
    mutate(Ply_mL.hr.bfactor    = ClearanceRate.Ply.bfactor) %>% 
    
    mutate(Chaet_mL.hr          = ClearanceRate.Chaet) %>% 
    mutate(Chaet_mL.hr.mmlength = ClearanceRate.Chaet.length) %>% 
    mutate(Chaet_mL.hr.bfactor  = ClearanceRate.Chaet.bfactor) %>% 
    
    mutate(Seston_mL.hr          = ClearanceRate.Seston) %>% 
    mutate(Seston_mL.hr.mmlength = ClearanceRate.Seston.length) %>% 
    mutate(Seston_mL.hr.bfactor  = ClearanceRate.Seston.bfactor) 
    
  if (nrow(dat2) > 0) {
    CR.table           <- data.frame(matrix(nrow = nrow(dat2), ncol = 21)) # create dataframe to save cumunalitively during for loop
    colnames(CR.table) <- c('Date', 'ID', 'pH', 'Replicate', 'Fed_Unfed','Run', 'Plate', 'Number', 'Length_um', 
                                  'Total_mL.hr','Total_mL.hr.mmlength', 'Total_mL.hr.bfactor', 
                                  'Chaet_mL.hr','Chaet_mL.hr.mmlength', 'Chaet_mL.hr.bfactor', 
                                  'Ply_mL.hr', 'Ply_mL.hr.mmlength', 'Ply_mL.hr.bfactor',
                                   'Seston_mL.hr','Seston_mL.hr.mmlength','Seston_mL.hr.bfactor') 
    CR.table$Date                       <- dat2$Date
    CR.table$ID                         <- loop_1026[i,]
    CR.table$pH                         <- gsub("_.*", "\\1", CR.table$ID)
    CR.table$Replicate                  <- gsub("^(?:[^_]+_){4}([^_]+).*", "\\1", CR.table$ID)
    CR.table$Fed_Unfed                  <- dat2$Fed_Unfed
    CR.table$Run                        <- gsub("^(?:[^_]+_){2}([^_]+).*", "\\1", CR.table$ID)
    CR.table$Plate                      <- dat2$Plate
    CR.table$Number                     <- gsub("^(?:[^_]+_){6}([^_]+).*", "\\1", CR.table$ID)
    CR.table$Length_um                  <- dat2$Length_um
    
    CR.table$Total_mL.hr                 <- dat2$Total_mL.hr
    CR.table$Total_mL.hr.mmlength       <- dat2$Total_mL.hr.mmlength
    CR.table$Total_mL.hr.bfactor        <- dat2$Total_mL.hr.bfactor
    
    CR.table$Ply_mL.hr                  <- dat2$Ply_mL.hr
    CR.table$Ply_mL.hr.mmlength         <- dat2$Ply_mL.hr.mmlength
    CR.table$Ply_mL.hr.bfactor          <- dat2$Ply_mL.hr.bfactor
    
    CR.table$Chaet_mL.hr                <- dat2$Chaet_mL.hr
    CR.table$Chaet_mL.hr.mmlength       <- dat2$Chaet_mL.hr.mmlength
    CR.table$Chaet_mL.hr.bfactor        <- dat2$Chaet_mL.hr.bfactor
    
    CR.table$Seston_mL.hr               <- dat2$Seston_mL.hr
    CR.table$Seston_mL.hr.mmlength      <- dat2$Seston_mL.hr.mmlength
    CR.table$Seston_mL.hr.bfactor       <- dat2$Seston_mL.hr.bfactor
    
    df       <- data.frame(CR.table) # name dataframe for this single row
    df_total.1026 <- rbind(df_total.1026,df) #bind to a cumulative list dataframe
    #print(df_total.1026) # print to monitor progress
  } else {}
}


# ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# clean & view means...       ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

df_total.1026 <- df_total.1026  %>% 
  dplyr::mutate(pCO2 = case_when(pH == 8.0 ~ "500 μatm", pH == 7.5 ~ "800 μatm")) %>% 
  dplyr::mutate(random_fact = as.factor(paste(Replicate, pH, Fed_Unfed, sep = '_')))
#  unique(df_total.1026$pH)
# View(df_total.1026)

Total_CR_1026_Means <- df_total.1026 %>% 
  dplyr::group_by(pCO2, Fed_Unfed) %>% 
  dplyr::filter(Total_mL.hr.bfactor > 0) %>% # ommit negative values
  dplyr::summarise(
    Total_meanCR = mean(Total_mL.hr.bfactor),
    Total_sdCR   = sd(Total_mL.hr.bfactor), 
    Total_seCR   = sd(Total_mL.hr.bfactor) / sqrt(length(Total_mL.hr.bfactor)), 
    n = n())
print(Total_CR_1026_Means)


Ply_CR_1026_Means <- df_total.1026 %>% 
  dplyr::group_by(pCO2, Fed_Unfed) %>% 
  dplyr::filter(Ply_mL.hr.bfactor > 0) %>% # ommit negative values
  dplyr::summarise(
    Ply_meanCR = mean(Ply_mL.hr.bfactor),
    Ply_sdCR   = sd(Ply_mL.hr.bfactor), 
    Ply_seCR   = sd(Ply_mL.hr.bfactor) / sqrt(length(Ply_mL.hr.bfactor)), 
    n = n())
print(Ply_CR_1026_Means)

Chaet_CR_1026_Means <- df_total.1026 %>% 
  dplyr::group_by(pCO2, Fed_Unfed) %>% 
  dplyr::filter(Chaet_mL.hr.bfactor > 0) %>% # ommit negative values
  dplyr::summarise(
    Chaet_meanCR = mean(Chaet_mL.hr.bfactor),
    Chaet_sdCR   = sd(Chaet_mL.hr.bfactor), 
    Chaet_seCR   = sd(Chaet_mL.hr.bfactor) / sqrt(length(Chaet_mL.hr.bfactor)), 
    n = n())
print(Chaet_CR_1026_Means)


Seston_CR_1026_Means <- df_total.1026 %>% 
  dplyr::group_by(pCO2, Fed_Unfed) %>% 
  dplyr::filter(Seston_mL.hr.bfactor > 0) %>% # ommit negative values
  dplyr::summarise(
    Seston_meanCR = mean(Seston_mL.hr.bfactor),
    Seston_sdCR   = sd(Seston_mL.hr.bfactor), 
    Seston_seCR   = sd(Seston_mL.hr.bfactor) / sqrt(length(Seston_mL.hr.bfactor)), 
    n = n())
print(Seston_CR_1026_Means)

```


# save data
```{r, master Clearance rate data }

ClearanceRate_Calc <- rbind(df_total.914, df_total.930, df_total.1026)
write.csv(ClearanceRate_Calc, "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/ClearanceRates/ClearanceRate_Calc.csv")

```


# upload data
```{r, master Clearance rate data }

# LOAD DATA :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
setwd("C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis") # personal computer
Master_calculated <- read.csv(file="Output/ClearanceRates/ClearanceRate_Calc.csv", header=T)

```

## b factor

```{r b factor}

nrow(Master_calculated) # 130

CR.Master_bfactor_plotting <- Master_calculated %>% 
  dplyr::mutate(log10_CR_Total      = log10(as.numeric(Master_calculated$Total_mL.hr)) ) %>%  # assign resp value
  dplyr::mutate(log10_CR_Ply       = log10(as.numeric(Master_calculated$Chaet_mL.hr)) ) %>%  # assign resp value
  dplyr::mutate(log10_CR_Chaet     = log10(as.numeric(Master_calculated$Ply_mL.hr)) ) %>%  # assign resp value
  dplyr::mutate(log10_CR_Seston    = log10(as.numeric(Master_calculated$Seston_mL.hr)) ) %>%  # assign resp value
  dplyr::mutate(log10_Length       = log10(as.numeric(Master_calculated$Length_um)) ) %>% # assign length value 
  dplyr::mutate(Food_OA            = paste(Master_calculated$pCO2, Master_calculated$Fed_Unfed, sep = "_")) # two-way factor to facet plots by  

# Resp.Master_bfactor_plottingOM <- Resp.Master_bfactor_plotting %>% 
#   # one outlier value that is omitted for parallet graphical outputsn with the non-omitted data 
#   dplyr::filter(!(log10_Length > 3.8 & log10_VO2 < -2))  # outliers ommited (a ingle data point)


Total_b.factorLENGTH_PLOT        <- CR.Master_bfactor_plotting %>% 
                                     ggplot(aes(x=log10_Length, y=log10_CR_Total)) +
                                        geom_point(size = 2) +
                                        theme(panel.grid.major = element_blank(), 
                                              panel.grid.minor = element_blank())+ 
                                        scale_x_continuous(name ="log10_Length; in mm") +
                                        scale_y_continuous(name ="log10_CR; CR in mL-1 hr-1)") +
                                        theme_classic() +
                                        theme(legend.position="none",
                                              element_line(linewidth = 0.5, 
                                                           color = 'black'),
                                              axis.title.y=element_text(size=12),
                                              axis.text.x=element_text(size=(15)),
                                              axis.text.y=element_text(size=(15))) + # legend.position="none",
                                        ggtitle("CR Scaling exponent: log10_CR_Total = log10_a + 
                                                (b.factor * log10_Length)") +
                                        geom_smooth(method = lm, color = 'black') +
                                        ggpmisc::stat_poly_eq(parse=T, 
                                                              aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
                                                              label.x.npc = "left")
Total_b.factorLENGTH_PLOT_facetted <- CR.Master_bfactor_plotting %>% 
                                     ggplot(aes(x=log10_Length, 
                                                y=log10_CR_Total, 
                                                color = Food_OA,
                                                shape = Food_OA)) +
                                        geom_point(size = 2) +
                                        geom_point() +
                                        #scale_color_manual(values=c("blue","orange")) +
                                        scale_color_manual(values=c("black","black", "grey50", "grey50")) +
                                        scale_shape_manual(values=c(19,1, 19, 1)) +
                                        theme(panel.grid.major = element_blank(), 
                                              panel.grid.minor = element_blank())+ 
                                        scale_x_continuous(name ="log10_Length; in mm") +
                                        scale_y_continuous(name ="log10_CR; CR in mL-1 hr-1)") +
                                        theme_classic() +
                                        theme(legend.position="none",
                                              element_line(linewidth = 0.5, 
                                                           color = 'black'),
                                              axis.title.y=element_text(size=12),
                                              axis.text.x=element_text(size=(15)),
                                              axis.text.y=element_text(size=(15))) + # legend.position="none",
                                        ggtitle("CR Scaling exponent: log10_CR_Total = log10_a + 
                                                (b.factor * log10_Length)") +
                                        geom_smooth(aes(group=Food_OA, linetype=Fed_Unfed),
                                                    method = lm, 
                                                    #color = c("black","black", "grey50", "grey50"), 
                                                    #linetype = c("solid","dashed", "solid", "dashed"),
                                                    se=F) +
                                        scale_linetype_discrete(name="Food x pCO2", 
                                                    breaks=c("500 μatm_fed", 
                                                             "500 μatm_unfed", 
                                                             "800 μatm_fed", 
                                                             "800 μatm_fed"), 
                                                    labels = c("high food x low pCO2", 
                                                               "low food x low pCO2", 
                                                               "high food x high pCO2",
                                                               "high food x high pCO2")) +
                                        ggpmisc::stat_poly_eq(parse=T, 
                                                              aes(label = paste(..eq.label..,
                                                                                ..rr.label.., sep = "~~~")),
                                                              label.x.npc = "left")

pdf(paste0(filename = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/ClearanceRates/scaling_exponent/CRScaling_bFactor_Length_Total.pdf"), width = 10, height = 5)
print(ggarrange(Total_b.factorLENGTH_PLOT, Total_b.factorLENGTH_PLOT_facetted, nrow = 1, ncol = 2)) # print the model diagnostics
dev.off()


Chaet_b.factorLENGTH_PLOT        <- CR.Master_bfactor_plotting %>% 
                                     ggplot(aes(x=log10_Length, y=log10_CR_Chaet)) +
                                        geom_point(size = 2) +
                                        theme(panel.grid.major = element_blank(), 
                                              panel.grid.minor = element_blank())+ 
                                        scale_x_continuous(name ="log10_Length; in mm") +
                                        scale_y_continuous(name ="log10_CR; CR in mL-1 hr-1)") +
                                        theme_classic() +
                                        theme(legend.position="none",
                                              element_line(linewidth = 0.5, 
                                                           color = 'black'),
                                              axis.title.y=element_text(size=12),
                                              axis.text.x=element_text(size=(15)),
                                              axis.text.y=element_text(size=(15))) + # legend.position="none",
                                        ggtitle("CR Scaling exponent: log10_CR_Chaet = log10_a + 
                                                (b.factor * log10_Length)") +
                                        geom_smooth(method = lm, color = 'black') +
                                        ggpmisc::stat_poly_eq(parse=T, 
                                                              aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
                                                              label.x.npc = "left")
Chaet_b.factorLENGTH_PLOT_facetted <- CR.Master_bfactor_plotting %>% 
                                     ggplot(aes(x=log10_Length, 
                                                y=log10_CR_Chaet, 
                                                color = Food_OA,
                                                shape = Food_OA)) +
                                        geom_point(size = 2) +
                                        geom_point() +
                                        #scale_color_manual(values=c("blue","orange")) +
                                        scale_color_manual(values=c("black","black", "grey50", "grey50")) +
                                        scale_shape_manual(values=c(19,1, 19, 1)) +
                                        theme(panel.grid.major = element_blank(), 
                                              panel.grid.minor = element_blank())+ 
                                        scale_x_continuous(name ="log10_Length; in mm") +
                                        scale_y_continuous(name ="log10_CR; CR in mL-1 hr-1)") +
                                        theme_classic() +
                                        theme(legend.position="none",
                                              element_line(linewidth = 0.5, 
                                                           color = 'black'),
                                              axis.title.y=element_text(size=12),
                                              axis.text.x=element_text(size=(15)),
                                              axis.text.y=element_text(size=(15))) + # legend.position="none",
                                        ggtitle("CR Scaling exponent: log10_CR_Chaet = log10_a + 
                                                (b.factor * log10_Length)") +
                                        geom_smooth(aes(group=Food_OA, linetype=Fed_Unfed),
                                                    method = lm, 
                                                    #color = c("black","black", "grey50", "grey50"), 
                                                    #linetype = c("solid","dashed", "solid", "dashed"),
                                                    se=F) +
                                        scale_linetype_discrete(name="Food x pCO2", 
                                                    breaks=c("500 μatm_fed", 
                                                             "500 μatm_unfed", 
                                                             "800 μatm_fed", 
                                                             "800 μatm_fed"), 
                                                    labels = c("high food x low pCO2", 
                                                               "low food x low pCO2", 
                                                               "high food x high pCO2",
                                                               "high food x high pCO2")) +
                                        ggpmisc::stat_poly_eq(parse=T, 
                                                              aes(label = paste(..eq.label..,
                                                                                ..rr.label.., sep = "~~~")),
                                                              label.x.npc = "left")

pdf(paste0(filename = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/ClearanceRates/scaling_exponent/CRScaling_bFactor_Length_Chaet.pdf"), width = 10, height = 5)
print(ggarrange(Chaet_b.factorLENGTH_PLOT, Chaet_b.factorLENGTH_PLOT_facetted, nrow = 1, ncol = 2)) # print the model diagnostics
dev.off()

Ply_b.factorLENGTH_PLOT        <- CR.Master_bfactor_plotting %>% 
                                     ggplot(aes(x=log10_Length, y=log10_CR_Ply)) +
                                        geom_point(size = 2) +
                                        theme(panel.grid.major = element_blank(), 
                                              panel.grid.minor = element_blank())+ 
                                        scale_x_continuous(name ="log10_Length; in mm") +
                                        scale_y_continuous(name ="log10_CR; CR in mL-1 hr-1)") +
                                        theme_classic() +
                                        theme(legend.position="none",
                                              element_line(linewidth = 0.5, 
                                                           color = 'black'),
                                              axis.title.y=element_text(size=12),
                                              axis.text.x=element_text(size=(15)),
                                              axis.text.y=element_text(size=(15))) + # legend.position="none",
                                        ggtitle("CR Scaling exponent: log10_CR_Ply = log10_a + 
                                                (b.factor * log10_Length)") +
                                        geom_smooth(method = lm, color = 'black') +
                                        ggpmisc::stat_poly_eq(parse=T, 
                                                              aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
                                                              label.x.npc = "left")
Ply_b.factorLENGTH_PLOT_facetted <- CR.Master_bfactor_plotting %>% 
                                     ggplot(aes(x=log10_Length, 
                                                y=log10_CR_Ply, 
                                                color = Food_OA,
                                                shape = Food_OA)) +
                                        geom_point(size = 2) +
                                        geom_point() +
                                        #scale_color_manual(values=c("blue","orange")) +
                                        scale_color_manual(values=c("black","black", "grey50", "grey50")) +
                                        scale_shape_manual(values=c(19,1, 19, 1)) +
                                        theme(panel.grid.major = element_blank(), 
                                              panel.grid.minor = element_blank())+ 
                                        scale_x_continuous(name ="log10_Length; in mm") +
                                        scale_y_continuous(name ="log10_CR; CR in mL-1 hr-1)") +
                                        theme_classic() +
                                        theme(legend.position="none",
                                              element_line(linewidth = 0.5, 
                                                           color = 'black'),
                                              axis.title.y=element_text(size=12),
                                              axis.text.x=element_text(size=(15)),
                                              axis.text.y=element_text(size=(15))) + # legend.position="none",
                                        ggtitle("CR Scaling exponent: log10_CR_Ply = log10_a + 
                                                (b.factor * log10_Length)") +
                                        geom_smooth(aes(group=Food_OA, 
                                                        linetype=Fed_Unfed),
                                                    method = lm, 
                                                    #color = c("black","black", "grey50", "grey50"), 
                                                    #linetype = c("solid","dashed", "solid", "dashed"),
                                                    se=F) +
                                        scale_linetype_discrete(name="Food x pCO2", 
                                                    breaks=c("500 μatm_fed", 
                                                             "500 μatm_unfed", 
                                                             "800 μatm_fed", 
                                                             "800 μatm_fed"), 
                                                    labels = c("high food x low pCO2", 
                                                               "low food x low pCO2", 
                                                               "high food x high pCO2",
                                                               "high food x high pCO2")) +
                                        ggpmisc::stat_poly_eq(parse=T, 
                                                              aes(label = paste(..eq.label..,
                                                                                ..rr.label.., sep = "~~~")),
                                                              label.x.npc = "left")

pdf(paste0(filename = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/ClearanceRates/scaling_exponent/CRScaling_bFactor_Length_Ply.pdf"), width = 10, height = 5)
print(ggarrange(Ply_b.factorLENGTH_PLOT, Ply_b.factorLENGTH_PLOT_facetted, nrow = 1, ncol = 2)) # print the model diagnostics
dev.off()

Seston_b.factorLENGTH_PLOT        <- CR.Master_bfactor_plotting %>% 
                                     ggplot(aes(x=log10_Length, y=log10_CR_Seston)) +
                                        geom_point(size = 2) +
                                        theme(panel.grid.major = element_blank(), 
                                              panel.grid.minor = element_blank())+ 
                                        scale_x_continuous(name ="log10_Length; in mm") +
                                        scale_y_continuous(name ="log10_CR; CR in mL-1 hr-1)") +
                                        theme_classic() +
                                        theme(legend.position="none",
                                              element_line(linewidth = 0.5, 
                                                           color = 'black'),
                                              axis.title.y=element_text(size=12),
                                              axis.text.x=element_text(size=(15)),
                                              axis.text.y=element_text(size=(15))) + # legend.position="none",
                                        ggtitle("CR Scaling exponent: log10_CR_Seston = log10_a + 
                                                (b.factor * log10_Length)") +
                                        geom_smooth(method = lm, color = 'black') +
                                        ggpmisc::stat_poly_eq(parse=T, 
                                                              aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
                                                              label.x.npc = "left")
Seston_b.factorLENGTH_PLOT_facetted <- CR.Master_bfactor_plotting %>% 
                                     ggplot(aes(x=log10_Length, 
                                                y=log10_CR_Seston, 
                                                color = Food_OA,
                                                shape = Food_OA)) +
                                        geom_point(size = 2) +
                                        #scale_color_manual(values=c("blue","orange")) +
                                        scale_color_manual(values=c("black","black", "grey50", "grey50")) +
                                        scale_shape_manual(values=c(19,1, 19, 1)) +
                                        theme(panel.grid.major = element_blank(), 
                                              panel.grid.minor = element_blank())+ 
                                        scale_x_continuous(name ="log10_Length; in mm") +
                                        scale_y_continuous(name ="log10_CR; CR in mL-1 hr-1)") +
                                        theme_classic() +
                                        theme(legend.position="none",
                                              element_line(linewidth = 0.5, 
                                                           color = 'black'),
                                              axis.title.y=element_text(size=12),
                                              axis.text.x=element_text(size=(15)),
                                              axis.text.y=element_text(size=(15))) + # legend.position="none",
                                        ggtitle("CR Scaling exponent: log10_CR_Seston = log10_a + 
                                                (b.factor * log10_Length)") +
                                        geom_smooth(aes(group=Food_OA, 
                                                        linetype=Fed_Unfed),
                                                    method = lm, 
                                                    #color = c("black","black", "grey50", "grey50"), 
                                                    #linetype = c("solid","dashed", "solid", "dashed"),
                                                    se=F) +
                                        scale_linetype_discrete(name="Food x pCO2", 
                                                    breaks=c("500 μatm_fed", 
                                                             "500 μatm_unfed", 
                                                             "800 μatm_fed", 
                                                             "800 μatm_fed"), 
                                                    labels = c("high food x low pCO2", 
                                                               "low food x low pCO2", 
                                                               "high food x high pCO2",
                                                               "high food x high pCO2")) +
                                        ggpmisc::stat_poly_eq(parse=T, 
                                                              aes(label = paste(..eq.label..,
                                                                                ..rr.label.., sep = "~~~")),
                                                              label.x.npc = "left")
                                        
                                        
pdf(paste0(filename = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/ClearanceRates/scaling_exponent/CRScaling_bFactor_Length_Seston.pdf"), width = 10, height = 5)
print(ggarrange(Seston_b.factorLENGTH_PLOT, Seston_b.factorLENGTH_PLOT_facetted, nrow = 1, ncol = 2)) # print the model diagnostics
dev.off()


pdf(paste0(filename = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/ClearanceRates/scaling_exponent/CRScaling_bFactor_Length_ALL.pdf"), width = 10, height = 15)
print(ggarrange(Chaet_b.factorLENGTH_PLOT, Chaet_b.factorLENGTH_PLOT_facetted,
                Ply_b.factorLENGTH_PLOT, Ply_b.factorLENGTH_PLOT_facetted,
                Seston_b.factorLENGTH_PLOT, Seston_b.factorLENGTH_PLOT_facetted,
                nrow = 3, ncol = 2)) # print the model diagnostics
dev.off()


```


## Density plots

```{r, 20210930 Density plots }
library(dplyr)
library(tidyr)

Master_930_plotting$pHxfood <- as.factor(Master_930_plotting$pHxfood)
CHAET_plotting  <- Master_930_plotting %>% dplyr::filter(type %in% 'chaet')
PLY_plotting    <- Master_930_plotting %>% dplyr::filter(type %in% 'ply')
SESTON_plotting <- Master_930_plotting %>% dplyr::filter(type %in% 'seston')



# :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# Chaetoceros                  ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

df_mean_CHAET <- CHAET_plotting %>%
  dplyr::group_by(pHxfood) %>% 
  dplyr::summarize(average = mean(CR_mL.hr.mmlength)) %>%
  dplyr::ungroup()
p.box_CHAET <- ggplot(CHAET_plotting, aes(x = pHxfood, y = CR_mL.hr.mmlength)) + geom_boxplot() + geom_point(data= df_mean_CHAET, mapping = aes(x = pHxfood, y = average),
             color="red") 
p.box.data.CHAET <- layer_data(p.box_CHAET) %>%
  select(x, ymin, lower, middle, upper, ymax, outliers, flipped_aes) %>%
  dplyr::rename(mean = flipped_aes) %>% 
  dplyr::mutate(mean  = df_mean_CHAET$average) %>% 
  mutate(pHxfood = factor(x, labels = levels(CHAET_plotting$pHxfood), ordered = TRUE)) %>%
  select(-x)

p.box.data.CHAET %>% unnest(outliers)


density.plot_CR_CHAET_930 <-ggplot(p.box.data.CHAET) +
                                # manually plot flipped boxplot
                                geom_segment(aes(x = ymin, xend = ymax, y = -0.15, yend = -0.15)) +
                                geom_rect(aes(xmin = lower, xmax = upper, ymin = -0.3, ymax = 0,  fill = pHxfood),color = "black") +
                                geom_point(data = . %>% unnest(outliers), aes(x = outliers, y = -0.15), color = "grey60", size = 1) +
                                # vertical lines at Q1 / Q2 / Q3
                                geom_vline(data = . %>% select(pHxfood, lower, mean, upper) %>% gather(key, value, -pHxfood), aes(xintercept = value)) +
                                # density plot
                                geom_density(data = CHAET_plotting, aes(x = CR_mL.hr.mmlength, group=pHxfood, fill=pHxfood, ..scaled..), alpha=.4, adjust=1.5) +
                                #  theme
                                theme_classic() +
                                facet_grid(pHxfood ~ .) +
                                theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.position = "none", plot.title = element_text(size=10))+
                                labs(title = "F1 Scallops: Clearance rates (Chaetoceros) 92 DPF", 
                                     x = expression(Clearance~rate~"("~Chaetoceros~cells~mL^{-1}%.%~mm~shell~length^{-1}%.%hr^{-1}~")"),
                                     y = "Scaled density") +
                                scale_fill_manual(values=c("grey40", "grey40", "grey85", "grey85"))
density.plot_CR_CHAET_930

pdf(paste0(filename = "C:/Users/samuel.gurr/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/ClearanceRates/20210930_figs_tables/20210930_CR_CHAET_density_plot.pdf"), width = 5, height = 5)
density.plot_CR_CHAET_930 # print the model diagnostics 
dev.off()


# :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# Tetraselmis (Ply)                  ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::


df_mean_PLY <- PLY_plotting %>%
  dplyr::group_by(pHxfood) %>% 
  dplyr::summarize(average = mean(CR_mL.hr.mmlength)) %>%
  dplyr::ungroup()
p.box_PLY <- ggplot(PLY_plotting, aes(x = pHxfood, y = CR_mL.hr.mmlength)) + geom_boxplot() + geom_point(data= df_mean_PLY, mapping = aes(x = pHxfood, y = average),
             color="red") 
p.box.data.PLY <- layer_data(p.box_PLY) %>%
  select(x, ymin, lower, middle, upper, ymax, outliers, flipped_aes) %>%
  dplyr::rename(mean = flipped_aes) %>% 
  dplyr::mutate(mean  = df_mean_PLY$average) %>% 
  mutate(pHxfood = factor(x, labels = levels(PLY_plotting$pHxfood), ordered = TRUE)) %>%
  select(-x)

p.box.data.PLY %>% unnest(outliers)


density.plot_CR_PLY_930 <-ggplot(p.box.data.PLY) +
                                # manually plot flipped boxplot
                                geom_segment(aes(x = ymin, xend = ymax, y = -0.15, yend = -0.15)) +
                                geom_rect(aes(xmin = lower, xmax = upper, ymin = -0.3, ymax = 0,  fill = pHxfood),color = "black") +
                                geom_point(data = . %>% unnest(outliers), aes(x = outliers, y = -0.15), color = "grey60", size = 1) +
                                # vertical lines at Q1 / Q2 / Q3
                                geom_vline(data = . %>% select(pHxfood, lower, mean, upper) %>% gather(key, value, -pHxfood), aes(xintercept = value)) +
                                # density plot
                                geom_density(data = PLY_plotting, aes(x = CR_mL.hr.mmlength, group=pHxfood, fill=pHxfood, ..scaled..), alpha=.4, adjust=1.5) +
                                #  theme
                                theme_classic() +
                                facet_grid(pHxfood ~ .) +
                                theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.position = "none", plot.title = element_text(size=10))+
                                labs(title = "F1 Scallops: Clearance rates (Tetraselmis/PLY) 92 DPF", 
                                     x = expression(Clearance~rate~"("~Tetraselmis~cells~mL^{-1}%.%~mm~shell~length^{-1}%.%hr^{-1}~")"),
                                     y = "Scaled density") +
                                scale_fill_manual(values=c("grey40", "grey40", "grey85", "grey85"))
density.plot_CR_PLY_930

pdf(paste0(filename = "C:/Users/samuel.gurr/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/ClearanceRates/20210930_figs_tables/20210930_CR_PLY_density_plot.pdf"), width = 5, height = 5)
density.plot_CR_PLY_930 # print the model diagnostics 
dev.off()

# :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# Seston                             ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::


df_mean_SESTON <- SESTON_plotting %>%
  dplyr::group_by(pHxfood) %>% 
  dplyr::summarize(average = mean(CR_mL.hr.mmlength)) %>%
  dplyr::ungroup()
p.box_SESTON <- ggplot(SESTON_plotting, aes(x = pHxfood, y = CR_mL.hr.mmlength)) + geom_boxplot() + geom_point(data= df_mean_SESTON, mapping = aes(x = pHxfood, y = average),
             color="red") 
p.box.data.SESTON <- layer_data(p.box_SESTON) %>%
  select(x, ymin, lower, middle, upper, ymax, outliers, flipped_aes) %>%
  dplyr::rename(mean = flipped_aes) %>% 
  dplyr::mutate(mean  = df_mean_SESTON$average) %>% 
  mutate(pHxfood = factor(x, labels = levels(SESTON_plotting$pHxfood), ordered = TRUE)) %>%
  select(-x)

p.box.data.SESTON %>% unnest(outliers)


density.plot_CR_SESTON_0930 <-ggplot(p.box.data.SESTON) +
                                # manually plot flipped boxplot
                                geom_segment(aes(x = ymin, xend = ymax, y = -0.15, yend = -0.15)) +
                                geom_rect(aes(xmin = lower, xmax = upper, ymin = -0.3, ymax = 0,  fill = pHxfood),color = "black") +
                                geom_point(data = . %>% unnest(outliers), aes(x = outliers, y = -0.15), color = "grey60", size = 1) +
                                # vertical lines at Q1 / Q2 / Q3
                                geom_vline(data = . %>% select(pHxfood, lower, mean, upper) %>% gather(key, value, -pHxfood), aes(xintercept = value)) +
                                # density plot
                                geom_density(data = SESTON_plotting, aes(x = CR_mL.hr.mmlength, group=pHxfood, fill=pHxfood, ..scaled..), alpha=.4, adjust=1.5) +
                                #  theme
                                theme_classic() +
                                facet_grid(pHxfood ~ .) +
                                theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.position = "none", plot.title = element_text(size=10))+
                                labs(title = "F1 Scallops: Clearance rates (seston) 92 DPF", 
                                     x = expression(Clearance~rate~"("~SESTONoceros~cells~mL^{-1}%.%~mm~shell~length^{-1}%.%hr^{-1}~")"),
                                     y = "Scaled density") +
                                scale_fill_manual(values=c("grey40", "grey40", "grey85", "grey85"))
density.plot_CR_SESTON_0930

pdf(paste0(filename = "C:/Users/samuel.gurr/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/ClearanceRates/20210930_figs_tables/20210930_CR_SESTON_density_plot.pdf"), width = 5, height = 5)
density.plot_CR_SESTON_0930 # print the model diagnostics 
dev.off()

```

```{r, 20211026 Density plots }
library(dplyr)
library(tidyr)

Master_1026_plotting$pHxfood <- as.factor(Master_1026_plotting$pHxfood)
CHAET_plotting <- Master_1026_plotting %>% dplyr::filter(type %in% 'chaet')
PLY_plotting    <- Master_1026_plotting %>% dplyr::filter(type %in% 'ply')
SESTON_plotting <- Master_1026_plotting %>% dplyr::filter(type %in% 'seston')



# :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# Chaetoceros                  ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

df_mean_CHAET <- CHAET_plotting %>%
  dplyr::group_by(pHxfood) %>% 
  dplyr::summarize(average = mean(CR_mL.hr.mmlength)) %>%
  dplyr::ungroup()
p.box_CHAET <- ggplot(CHAET_plotting, aes(x = pHxfood, y = CR_mL.hr.mmlength)) + geom_boxplot() + geom_point(data= df_mean_CHAET, mapping = aes(x = pHxfood, y = average),
             color="red") 
p.box.data.CHAET <- layer_data(p.box_CHAET) %>%
  select(x, ymin, lower, middle, upper, ymax, outliers, flipped_aes) %>%
  dplyr::rename(mean = flipped_aes) %>% 
  dplyr::mutate(mean  = df_mean_CHAET$average) %>% 
  mutate(pHxfood = factor(x, labels = levels(CHAET_plotting$pHxfood), ordered = TRUE)) %>%
  select(-x)

p.box.data.CHAET %>% unnest(outliers)


density.plot_CR_CHAET_1026 <-ggplot(p.box.data.CHAET) +
                                # manually plot flipped boxplot
                                geom_segment(aes(x = ymin, xend = ymax, y = -0.15, yend = -0.15)) +
                                geom_rect(aes(xmin = lower, xmax = upper, ymin = -0.3, ymax = 0,  fill = pHxfood),color = "black") +
                                geom_point(data = . %>% unnest(outliers), aes(x = outliers, y = -0.15), color = "grey60", size = 1) +
                                # vertical lines at Q1 / Q2 / Q3
                                geom_vline(data = . %>% select(pHxfood, lower, mean, upper) %>% gather(key, value, -pHxfood), aes(xintercept = value)) +
                                # density plot
                                geom_density(data = CHAET_plotting, aes(x = CR_mL.hr.mmlength, group=pHxfood, fill=pHxfood, ..scaled..), alpha=.4, adjust=1.5) +
                                #  theme
                                theme_classic() +
                                facet_grid(pHxfood ~ .) +
                                theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.position = "none", plot.title = element_text(size=10))+
                                labs(title = "F1 Scallops: Clearance rates (Chaetoceros) 92 DPF", 
                                     x = expression(Clearance~rate~"("~Chaetoceros~cells~mL^{-1}%.%~mm~shell~length^{-1}%.%hr^{-1}~")"),
                                     y = "Scaled density") +
                                scale_fill_manual(values=c("grey40", "grey40", "grey85", "grey85"))
density.plot_CR_CHAET_1026

pdf(paste0(filename = "C:/Users/samuel.gurr/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/ClearanceRates/20211026_figs_tables/20211026_CR_CHAET_density_plot.pdf"), width = 5, height = 5)
density.plot_CR_CHAET_1026 # print the model diagnostics 
dev.off()


# :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# Tetraselmis (Ply)                  ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::


df_mean_PLY <- PLY_plotting %>%
  dplyr::group_by(pHxfood) %>% 
  dplyr::summarize(average = mean(CR_mL.hr.mmlength)) %>%
  dplyr::ungroup()
p.box_PLY <- ggplot(PLY_plotting, aes(x = pHxfood, y = CR_mL.hr.mmlength)) + geom_boxplot() + geom_point(data= df_mean_PLY, mapping = aes(x = pHxfood, y = average),
             color="red") 
p.box.data.PLY <- layer_data(p.box_PLY) %>%
  select(x, ymin, lower, middle, upper, ymax, outliers, flipped_aes) %>%
  dplyr::rename(mean = flipped_aes) %>% 
  dplyr::mutate(mean  = df_mean_PLY$average) %>% 
  mutate(pHxfood = factor(x, labels = levels(PLY_plotting$pHxfood), ordered = TRUE)) %>%
  select(-x)

p.box.data.PLY %>% unnest(outliers)


density.plot_CR_PLY_1026 <-ggplot(p.box.data.PLY) +
                                # manually plot flipped boxplot
                                geom_segment(aes(x = ymin, xend = ymax, y = -0.15, yend = -0.15)) +
                                geom_rect(aes(xmin = lower, xmax = upper, ymin = -0.3, ymax = 0,  fill = pHxfood),color = "black") +
                                geom_point(data = . %>% unnest(outliers), aes(x = outliers, y = -0.15), color = "grey60", size = 1) +
                                # vertical lines at Q1 / Q2 / Q3
                                geom_vline(data = . %>% select(pHxfood, lower, mean, upper) %>% gather(key, value, -pHxfood), aes(xintercept = value)) +
                                # density plot
                                geom_density(data = PLY_plotting, aes(x = CR_mL.hr.mmlength, group=pHxfood, fill=pHxfood, ..scaled..), alpha=.4, adjust=1.5) +
                                #  theme
                                theme_classic() +
                                facet_grid(pHxfood ~ .) +
                                theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.position = "none", plot.title = element_text(size=10))+
                                labs(title = "F1 Scallops: Clearance rates (Tetraselmis/PLY) 92 DPF", 
                                     x = expression(Clearance~rate~"("~Tetraselmis~cells~mL^{-1}%.%~mm~shell~length^{-1}%.%hr^{-1}~")"),
                                     y = "Scaled density") +
                                scale_fill_manual(values=c("grey40", "grey40", "grey85", "grey85"))
density.plot_CR_PLY_1026

pdf(paste0(filename = "C:/Users/samuel.gurr/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/ClearanceRates/20211026_figs_tables/20211026_CR_PLY_density_plot.pdf"), width = 5, height = 5)
density.plot_CR_PLY_1026 # print the model diagnostics 
dev.off()

# :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# Seston                             ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::


df_mean_SESTON <- SESTON_plotting %>%
  dplyr::group_by(pHxfood) %>% 
  dplyr::summarize(average = mean(CR_mL.hr.mmlength)) %>%
  dplyr::ungroup()
p.box_SESTON <- ggplot(SESTON_plotting, aes(x = pHxfood, y = CR_mL.hr.mmlength)) + geom_boxplot() + geom_point(data= df_mean_SESTON, mapping = aes(x = pHxfood, y = average),
             color="red") 
p.box.data.SESTON <- layer_data(p.box_SESTON) %>%
  select(x, ymin, lower, middle, upper, ymax, outliers, flipped_aes) %>%
  dplyr::rename(mean = flipped_aes) %>% 
  dplyr::mutate(mean  = df_mean_SESTON$average) %>% 
  mutate(pHxfood = factor(x, labels = levels(SESTON_plotting$pHxfood), ordered = TRUE)) %>%
  select(-x)

p.box.data.SESTON %>% unnest(outliers)


density.plot_CR_SESTON_1026 <-ggplot(p.box.data.SESTON) +
                                # manually plot flipped boxplot
                                geom_segment(aes(x = ymin, xend = ymax, y = -0.15, yend = -0.15)) +
                                geom_rect(aes(xmin = lower, xmax = upper, ymin = -0.3, ymax = 0,  fill = pHxfood),color = "black") +
                                geom_point(data = . %>% unnest(outliers), aes(x = outliers, y = -0.15), color = "grey60", size = 1) +
                                # vertical lines at Q1 / Q2 / Q3
                                geom_vline(data = . %>% select(pHxfood, lower, mean, upper) %>% gather(key, value, -pHxfood), aes(xintercept = value)) +
                                # density plot
                                geom_density(data = SESTON_plotting, aes(x = CR_mL.hr.mmlength, group=pHxfood, fill=pHxfood, ..scaled..), alpha=.4, adjust=1.5) +
                                #  theme
                                theme_classic() +
                                facet_grid(pHxfood ~ .) +
                                theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.position = "none", plot.title = element_text(size=10))+
                                labs(title = "F1 Scallops: Clearance rates (seston) 92 DPF", 
                                     x = expression(Clearance~rate~"("~SESTONoceros~cells~mL^{-1}%.%~mm~shell~length^{-1}%.%hr^{-1}~")"),
                                     y = "Scaled density") +
                                scale_fill_manual(values=c("grey40", "grey40", "grey85", "grey85"))
density.plot_CR_SESTON_1026

pdf(paste0(filename = "C:/Users/samuel.gurr/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/ClearanceRates/20211026_figs_tables/20211026_CR_SESTON_density_plot.pdf"), width = 5, height = 5)
density.plot_CR_SESTON_1026 # print the model diagnostics 
dev.off()

```