---
title: "Respiration Analysis F1 Scallops 2021"
author: "Samuel Gurr"
date: "10/6/2021"
output:
  pdf_document:
    latex_engine: xelatex
---


```{r setup, include=FALSE}

# LOAD PACKAGES :::::::::::::::::::::::::::::::::::::::::::::::::::::::

library(dplyr)
library(ggplot2)
library(forcats)
library(lme4)
library(lmerTest)
library(see)
library(performance)
library(car)
library(kableExtra)
library(pander)
library(data.table)
library(stringr)
library(latex2exp)
library(Rmisc)

# SET WORKING DIRECTORY :::::::::::::::::::::::::::::::::::::::::::::::

#setwd("C:/Users/samjg/Documents/Github_repositories/Airradians_OA/RAnalysis") # personal computer
#setwd("C:/Users/samuel.gurr/Documents/Github_repositories/Airradians_OA/RAnalysis") # Work computer
setwd("C:/Users/samjg/Documents/Github_repositories/Airradians_OA/RAnalysis") # Work computer

# LOAD DATA :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

resp.data    <- read.csv(file="Output/Respiration/Cumulative_resp_alpha0.4_15sectrunc1hour.csv", header=T) %>% dplyr::filter(!Date %in% "9/14/2021" | !Filename %in% 'Run_1_raw.txt') # read the calculate raw rates from 'resp_LoLin' script - contains the calculated rate (not normalized for blanks) for each sensor-channel
exp_metadata <- read.csv(file="Data/ExperimentMetadata.csv", header=T) # treatment assignments to 'Chamber_Tank'
lengths      <- read.csv(file="Data/Respiration/Lengths_Condition_resp_clearance.csv", header=T)
resp.ref     <- read.csv(file="Data/Respiration/Reference_master.csv", header=T) %>% dplyr::filter(!Date %in% "9/14/2021" | !Filename %in% 'Run_1_raw.txt')

```

## merge master resp data frame 

```{r merge resp with length data and treatment IDs, echo=FALSE}

# merge the exp_metadata with the resp.data
resp.ref_length_merged                 <- merge(resp.ref, lengths) # all TRUE allows us to keep the blanks
resp.data_merged                       <- merge(resp.data, resp.ref_length_merged) %>% # out master file moving forward....
                                            dplyr::mutate(filetype = str_sub(Filename, -3,-1)) %>% 
                                            dplyr::mutate(filetype = factor(ifelse(filetype == "csv", "SDR_data", "LoLigo_data")))
kable(head(resp.data_merged))

```

## Visual diagnostics of plots to correct poor data 

- View on github: Airradians_OA/RAnalysis/Output/Respiration/plots_alpha0.4_increm15sec/

#### found three calls that inaccurately represent the rates of oxygen consumption 

(1) https://github.com/SamGurr/Airradians_OA/blob/master/RAnalysis/Output/Respiration/plots_alpha0.4_increm15sec/20210930_Plate_2_Run_2_C5_regression.pdf
- solution = call 'Lz' instead of the default Leq

(2) https://github.com/SamGurr/Airradians_OA/blob/master/RAnalysis/Output/Respiration/plots_alpha0.4_increm15sec/20210930_Plate_2_Run_1_C1_regression.pdf
- solution = call 'Lz' instead of the default Leq

(3) https://github.com/SamGurr/Airradians_OA/blob/master/RAnalysis/Output/Respiration/plots_alpha0.4_increm15sec/20210930_Plate_1_Run_2_C1_regression.pdf
- solution = we reran this at the end of the LoLin script  for 0-20 minutes and got an Lpc  -0.0296, insert this 

```{r IMPORTANT correct poor data, echo=TRUE}
resp.data_merged[94,c(1:6)]  # 	C1 RR_9.30.21_AM_Plate_2_Run_1.csv # -0.02890813	-0.0608251	-0.0608251 - Lz and Leq call better regression than Lpc
resp.data_merged[110,c(1:6)] #  C5 RR_9.30.21_PM_Plate_2_Run_2.csv	0.029052351	-0.076034441	-0.076034441
resp.data_merged[95,c(1:6)]  # 	C1 RR_9.30.21_PM_Plate_1_Run_2.csv	0.011656487	0.011656487	0.011656487  - ommit this

resp.data_merged[94,4] <- resp.data_merged[94,5] # 20210930_Plate_2_Run_2_C5_regression - Lz and Leq call better regression than Lpc
resp.data_merged[110,4] <- resp.data_merged[110,5] # 20210930_Plate_2_Run_1_C1_regression - Lz and Leq call better regression than Lpc
resp.data_merged[95,4] <- -0.0296 # 20210930_Plate_1_Run_2_C1_regression - plot shows noise after the 20 minutes mark, we reran this at the end of the LoLin script, insert here!

resp.data_merged[94,c(1:6)]
resp.data_merged[110,c(1:6)]
resp.data_merged[95,c(1:6)]
```

# Calculate blanks, print all and means

```{r call blanks, echo=FALSE}

blanks_total <- data.frame() # start dataframe 
blanks.table <- data.frame(matrix(nrow = 1,ncol = 5)) # make a table template
colnames(blanks.table)<-c('Date', 'Channel', 'mean_Lpc', 'mean_Leq' , 'mean_Lz') # names for comuns in the for loop

blanks_all_raw <- data.frame(merge(resp.ref, resp.data, by = c('Date', 'Channel', 'Filename')) %>% 
                  dplyr::mutate(filetype = str_sub(Filename, -3,-1)) %>% 
                  dplyr::mutate(filetype = factor(ifelse(filetype == "csv", "SDR_data", "LoLigo_data"))) %>% 
                  dplyr::filter(Chamber_tank  == 'blank') %>% 
                  dplyr::filter(Lpc <0) %>% 
                  dplyr::filter(!Date == '9/30/2021' | !Lpc < -0.035) %>% #omits C6 RR_9.30.21_AM_Plate_1_Run_1.csv	8.0	blank - View the Lolin plot, looks noisy and a fast outlier from the others
                  dplyr::filter(!Date == '10/26/2021'  | !Channel == "CH8" | !Run == "2" )) # omit a bad blank that contained a bad seal, noted on the respiration sampling day during the trial 
kable((blanks_all_raw)[,c(1:3,6,8,12:14)])

blanks_means <- blanks_all_raw %>% 
     dplyr::group_by(Date, pH, filetype) %>% 
     dplyr::filter(Chamber_tank == "blank") %>% 
     dplyr::filter(Lpc <0) %>% # ommit blank calls that d/n represent oxygen consumption
     dplyr::summarise(BLANK.mean_Lpc = mean(abs(Lpc)),
                      BLANK.sd.Lpc   = sd(abs(Lpc)),
                      BLANK.mean_Leq = mean(abs(Leq)), 
                      BLANK.mean_Lz = mean(abs(Lz)),
                      n = n())
kable(blanks_means)


```

# Merge blanks with the master file by DAte, pCO2 treatment, and filetype

* 'filteype' is only important here on 20211026 when both Loligo and SDR were used due to difference in size for fed (larger) and unfed animals 

```{r merge blanks_means for a master file, echo=FALSE}

Resp.Master <- merge(resp.data_merged, blanks_means, by=c("Date", "pH",  "filetype")) %>% # NOTE: this repeats for every distinct length value
  dplyr::mutate(resp_norm = Lpc - BLANK.mean_Lpc) # ommits respiration rate values showing an increase in O2 over time 

```


# Master REsp file 

## dplyr::mutate for the following:

* 'volume' of the different vessels throughout the fed*OA challenge
* 'Age'
8 'Fed_unfed'
* 'pCO2'

```{r merge data to master file and write csv, echo=FALSE}

Resp.Master_OM <- Resp.Master %>% dplyr::filter(!resp_norm > 0) %>% # ommit respiration values that are positive  
  dplyr::mutate(volume = case_when(filetype == "LoLigo_data" & Date == '9/14/2021' ~ 1.7, filetype == "LoLigo_data" & Date == '10/26/2021' ~ 40, filetype == "SDR_data" ~ 2.2)) %>% # chamber volumes on different dates with
  dplyr::mutate(Age = case_when(Date == '9/14/2021' ~ 50, Date == '9/30/2021' ~ 66, Date == '10/26/2021' ~ 92)) %>% 
  dplyr::mutate(Fed_Unfed = case_when(Fed_Unfed == 'F' ~ "High food", is.na(Fed_Unfed) ~ "High food", Fed_Unfed == 'U' ~ "Low food")) %>% 
  dplyr::mutate(pCO2 = case_when(pH == 8.0 ~ "500 μatm", pH == 7.5 ~ "800 μatm"))
Resp.outliers <- Resp.Master %>% dplyr::filter(resp_norm > 0) # call the values with positive resp rates, measing they were slower than the blank!
print(Resp.outliers)

write.csv(Resp.Master_OM, "C:/Users/samjg/Documents/Github_repositories/Airradians_OA/RAnalysis/Output/Respiration/Calculated_Resp_Master.csv")
#write.csv(Resp.Master_OM, "C:/Users/samuel.gurr/Documents/Github_repositories/Airradians_OA/RAnalysis/Output/Respiration/Calculated_Resp_Master.csv")

```


# Calculate rates as ng L-1 O2 um shell length-1 hr-1

#### note: this chunk calls the data that used the 8-channel loligo system and the SDR system to correct for total respiration chamber (vial/vessel, well, etc.) volume separately 
- loligo 8-channel on 9/14/21 = 2.2 ml vessels 
- SDR 24-channel on 9/3-/21 = 1.7 ml wells 

```{r Calculate Resp Rates , echo=TRUE}
Resp.Master_OM <- Resp.Master_OM[!is.na(Resp.Master_OM$Length_um),]

# NORMALIZED for Shell Size (Length)
 Resp.Master_OM$resp_ng_L_μm_Length_hr <- ( 
          ( ( (abs(Resp.Master_OM$resp_norm)*1000000) * # call absolute value of resp in mg per minute - convert to ng min-1
                (Resp.Master_OM$volume/1000) ) / # vial volume for loligo 8 channel runs was 2.2 mL!!! - correct ng minute-1 to ng liter-1 by multiplying by the resp vial in liters
              Resp.Master_OM$Length_um) * # normalize by individual or larvae count - as to ng L-1 individual-1
            (60)) # correct for the time; final value is ng O2 Liter-1 um shell length-1 hour-1

 
 
# NORMALIZED for Dry Tissue Weight
 Resp.Master_OM$resp_mg_L_g_hr <- ( 
          ( ( (abs(Resp.Master_OM$resp_norm)) * # call absolute value of resp in mg per minute -  mg O2 L-1 per min-1
                (Resp.Master_OM$volume/1000) ) / # vial volume for loligo 8 channel runs was 2.2 mL!!! - correct ng minute-1 to ng liter-1 by multiplying by the resp vial in liters
              (Resp.Master_OM$Dry_Tissue_weight) ) * # normalize by Dry tissue weight  as to mg O2 L-1 g dry tissue weight-1
            (60)) # correct for the time; final value is ug O2 Liter -1 mg dry tissue weight-1 hour-1

```

# Mean standard error plot of all data 

```{r Line plot , echo=TRUE}

RespSumTab <- summarySE(Resp.Master_OM, measurevar="resp_ng_L_μm_Length_hr", groupvars=c("Age", "pCO2", "Fed_Unfed"))
RespSumTab$pCO2 <- factor(RespSumTab$pCO2, c("500 μatm","800 μatm"))
## Use geom_line and geom_point to plot over time
Resp_geomline<-ggplot(data=RespSumTab, aes(x=Age, y=resp_ng_L_μm_Length_hr, color=pCO2)) +
  geom_line(aes(linetype = factor(Fed_Unfed)), size = 0.5) +  
  geom_point()+ 
  scale_color_manual(values=c("forestgreen","darkorange2"))+
  geom_errorbar(aes(ymin=resp_ng_L_μm_Length_hr-se, ymax=resp_ng_L_μm_Length_hr+se), width=.2,
                position=position_dodge(.1))+
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  scale_x_continuous(name ="Age (days)") +
  labs(title = "F1 Scallops: Food x OA Experiment", 
       y = expression(Respiration~rate~"("~ng~L^{-1}~O[2]%.%μ*m^{-1}%.% hr^{-1}~")")) +
  scale_linetype_manual(values = c("High food" = "solid", "Low food" = "dashed"))  +
  theme(legend.position="none") +
  # facet_wrap(~factor(Fed_Unfed, level = c('Low food', 'High food'))) 
  facet_wrap(~pCO2)

#pdf(paste0("C:/Users/samjg/Documents/Github_repositories/Airradians_OA/RAnalysis/Output/Respiration/Juvenile_respiration_FoodxOA.pdf"))
pdf(paste0("C:/Users/samuel.gurr/Documents/Github_repositories/Airradians_OA/RAnalysis/Output/Respiration/Juvenile_respiration_FoodxOA.pdf"))

Resp_geomline
dev.off()

Resp_geomline
```


# Analysis 

## 9/14/2021 F1 juvenile scallops

**About**
- two pCO2 treatments 
- **before** we culled and started the food limitation trials


#### number of replicates for analysis...

```{r 9/14 replicates, echo=FALSE}

# model effect of treatment on resp rate 20210507
Resp_0914 <- Resp.Master_OM %>% 
              dplyr::filter(Date %in% '9/14/2021')  %>% # call only 9/14
              dplyr::filter(!Chamber_tank  %in% 'blank')

Resp_0914 %>% dplyr::group_by(Chamber_tank) %>% dplyr::summarise(n()) # tank replication

```

## 20210914 linear model, diagnostics, and plots

```{r 9/14 lm diag and figs, echo=TRUE}
LMmod_0914 <- aov(lm(resp_ng_L_μm_Length_hr~pCO2,data=Resp_0914))
pander(summary(LMmod_0914), style='rmarkdown')
check_model(LMmod_0914) # observe the diagnostics of the model
shapiro.test(residuals(LMmod_0914)) #  normal - 0.3875
leveneTest(LMmod_0914) # good - 0.6186

DF   <- paste( (summary(LMmod_0914)[[1]][["Df"]])[1], (summary(LMmod_0914)[[1]][["Df"]])[2], sep = '/')
Fval <- (summary(LMmod_0914)[[1]][["F value"]])[1]
pval <- (summary(LMmod_0914)[[1]][["Pr(>F)"]])[1]

# pdf(paste0("C:/Users/samuel.gurr/Documents/Github_repositories/Airradians_OA/RAnalysis/Output/Respiration/20210914_respiration.pdf"))
#pdf(paste0("C:/Users/samjg/Documents/Github_repositories/Airradians_OA/RAnalysis/Output/Respiration/20210914_respiration.pdf"))
pdf(paste0("C:/Users/samuel.gurr/Documents/Github_repositories/Airradians_OA/RAnalysis/Output/Respiration/20210914_respiration.pdf"))

ggplot(Resp_0914, aes(x = factor(pCO2, level = c('500 μatm', '800 μatm')), resp_ng_L_μm_Length_hr , fill = pCO2)) +
  theme(panel.grid=element_blank()) +
  geom_boxplot(size=0.2, width=0.5, alpha=0.1, aes(fill=pCO2)) +
  scale_fill_manual(values=c("white","grey50")) +
  geom_point(shape = 21, size = 2, position = position_jitterdodge(jitter.width = 0.1)) +
  theme_classic() +
  scale_x_discrete(labels= c('~500 μatm', '~800 μatm')) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 4.25)) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold")) +
  labs(title = "F1 Scallops: respiration rates on 20210914", 
       y = expression(Respiration~rate~"("~ng~L^{-1}~O[2]%.%μ*m^{-1}%.% hr^{-1}~")"), 
       x = expression(italic(p)*CO[2]~Treatment~"("~μ*atm~")")) # + 
  # annotate("text", x=1.2, y=2.8, size = 4, label = "aov(Resp~pCO2)") +
  # annotate("text", x=1.2, y=2.6, size = 4, label= paste('DF =',DF,'F =', signif(Fval, digits=3), 'p value =', signif(pval, digits=3), sep=" ")) 
dev.off()
```



## 9/14/2021 F1 juvenile scallops

**About**

- two pCO2 treatments 

- *before* we culled and started the food limitation trials


#### number of replicates for analysis...

```{r 9/30 replicates, echo=FALSE}

Resp_0930 <- Resp.Master_OM %>% 
  dplyr::filter(Date %in% '9/30/2021')  %>% # call only 9/14
  dplyr::select(-Center)

Resp_0930 %>% dplyr::group_by(Chamber_tank, Food ) %>% dplyr::summarise(n()) # tank replication

```

## 20210930 linear model, diagnostics, and plots

```{r 9/30 lm diag and figs, echo=TRUE}

LMmod_0930 <- aov(lm(resp_ng_L_μm_Length_hr~pCO2*Fed_Unfed ,data=Resp_0930))
pander(summary(LMmod_0930), style='rmarkdown')
check_model(LMmod_0930) # observe the diagnostics of the model
shapiro.test(residuals(LMmod_0930)) #  normal - 0.07641
leveneTest(LMmod_0930) # good - 0.1648



DF_pCO2   <- paste( (summary(LMmod_0930)[[1]][["Df"]])[1], (summary(LMmod_0930)[[1]][["Df"]])[4], sep = '/')
Fval_pCO2 <- (summary(LMmod_0930)[[1]][["F value"]])[1]
pval_pCO2 <- (summary(LMmod_0930)[[1]][["Pr(>F)"]])[1]

DF_Fed    <- paste( (summary(LMmod_0930)[[1]][["Df"]])[2], (summary(LMmod_0930)[[1]][["Df"]])[4], sep = '/')
Fval_Fed  <- (summary(LMmod_0930)[[1]][["F value"]])[2]
pval_Fed  <- (summary(LMmod_0930)[[1]][["Pr(>F)"]])[2]

Resp_0930$Fed_Unfed <- as.factor(Resp_0930$Fed_Unfed)

levels(Resp_0930$Fed_Unfed) <- c("High food", "Low food")

# pdf(paste0("C:/Users/samuel.gurr/Documents/Github_repositories/Airradians_OA/RAnalysis/Output/Respiration/20210930_respiration.pdf"))
#pdf(paste0("C:/Users/samjg/Documents/Github_repositories/Airradians_OA/RAnalysis/Output/Respiration/20210930_respiration.pdf"))
pdf(paste0("C:/Users/samuel.gurr/Documents/Github_repositories/Airradians_OA/RAnalysis/Output/Respiration/20210930_respiration.pdf"))

ggplot(Resp_0930, aes(x = factor(pCO2, level = c('500 μatm', '800 μatm')), resp_ng_L_μm_Length_hr , fill = pCO2)) +
  theme(panel.grid=element_blank()) +
  geom_boxplot(size=0.2, alpha=0.1, aes(fill=pCO2)) +
  scale_fill_manual(values=c("white","grey50")) +
  geom_point(shape = 21, size = 2, position = position_jitterdodge(jitter.width = 0.1)) +
  theme_classic() +
  scale_x_discrete(labels= c('~500 μatm', '~800 μatm')) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 4.25)) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold")) +
  stat_summary(fun.y=mean, geom="point", shape=18, size=4, color="black", fill="white") +
  labs(title = "Respiration rate; F1 Scallops (juveniles) 66 days post-fertilization", 
       y = expression(Respiration~rate~"("~ng~L^{-1}~O[2]%.%mu*m^{-1}%.% hr^{-1}~")"), 
       x = expression(italic(p)*CO[2]~Treatment~"("~mu*atm~")")) + 
  facet_wrap(~factor(Fed_Unfed, level = c('Low food', 'High food'))) # + 
dev.off()
```




## 10/26/2021 F1 juvenile scallops

**About**

- two pCO2 treatments 

- *before* we culled and started the food limitation trials


#### number of replicates for analysis...

```{r 10/26 replicates, echo=FALSE}

Resp_01026 <- Resp.Master_OM %>% 
  dplyr::filter(Date %in% '10/26/2021')  %>% # call only 10/14
  dplyr::select(-Center)

Resp_01026 %>% dplyr::group_by(Chamber_tank, Food ) %>% dplyr::summarise(n()) # tank replication

```


## 20211026 linear model, diagnostics, and plots

```{r 10/26 lm diag and figs, echo=TRUE}

LMmod_01026 <- aov(lm(resp_ng_L_μm_Length_hr~pCO2*Fed_Unfed ,data=Resp_01026))
pander(summary(LMmod_01026), style='rmarkdown')
check_model(LMmod_01026) # observe the diagnostics of the model
shapiro.test(residuals(LMmod_01026)) #  normal - 0.3096
leveneTest(LMmod_01026) # 0.1998
TukeyHSD(LMmod_01026)


DF_pCO2   <- paste( (summary(LMmod_01026)[[1]][["Df"]])[1], (summary(LMmod_01026)[[1]][["Df"]])[4], sep = '/')
Fval_pCO2 <- (summary(LMmod_01026)[[1]][["F value"]])[1]
pval_pCO2 <- (summary(LMmod_01026)[[1]][["Pr(>F)"]])[1]

DF_Fed    <- paste( (summary(LMmod_01026)[[1]][["Df"]])[2], (summary(LMmod_01026)[[1]][["Df"]])[4], sep = '/')
Fval_Fed  <- (summary(LMmod_01026)[[1]][["F value"]])[2]
pval_Fed  <- (summary(LMmod_01026)[[1]][["Pr(>F)"]])[2]


DF_Int    <- paste( (summary(LMmod_01026)[[1]][["Df"]])[3], (summary(LMmod_01026)[[1]][["Df"]])[4], sep = '/')
Fval_Int  <- (summary(LMmod_01026)[[1]][["F value"]])[3]
pval_Int  <- (summary(LMmod_01026)[[1]][["Pr(>F)"]])[3]


Resp_01026$Fed_Unfed <- as.factor(Resp_01026$Fed_Unfed)

levels(Resp_01026$Fed_Unfed) <- c("High food", "Low food")

# pdf(paste0("C:/Users/samuel.gurr/Documents/Github_repositories/Airradians_OA/RAnalysis/Output/Respiration/202101026_respiration.pdf"))
#pdf(paste0("C:/Users/samjg/Documents/Github_repositories/Airradians_OA/RAnalysis/Output/Respiration/202101026_respiration.pdf"))
pdf(paste0("C:/Users/samuel.gurr/Documents/Github_repositories/Airradians_OA/RAnalysis/Output/Respiration/202101026_respiration.pdf"))

ggplot(Resp_01026, aes(x = factor(pCO2, level = c('500 μatm', '800 μatm')), resp_ng_L_μm_Length_hr , fill = pCO2)) +
  theme(panel.grid=element_blank()) +
  geom_boxplot(size=0.2, alpha=0.1, aes(fill=pCO2)) +
  scale_fill_manual(values=c("white","grey50")) +
  geom_point(shape = 21, size = 2, position = position_jitterdodge(jitter.width = 0.1)) +
  theme_classic() +
  #ylim(0, 3) +
  scale_x_discrete(labels= c('~500 μatm', '~800 μatm')) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 4.25)) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold")) +
  stat_summary(fun.y=mean, geom="point", shape=18, size=4, color="black", fill="white") +
  labs(title = "Respiration rate; F1 Scallops (juveniles) 92 days post-fertilization", 
       y = expression(Respiration~rate~"("~ng~L^{-1}~O[2]%.%mu*m^{-1}%.% hr^{-1}~")"), 
       x = expression(italic(p)*CO[2]~Treatment~"("~mu*atm~")")) + 
  facet_wrap(~factor(Fed_Unfed, level = c('Low food', 'High food'))) # + 
dev.off()


# see what the dry tissue weight looks like for the data we have so far.... ( only have it for the fed animals ! - filter first and then run it)
Resp_fed_drywt <- Resp_01026 %>% dplyr::filter(Food %in% "fed") %>% 
                ggplot(aes(x = factor(pCO2, level = c('500 μatm', '800 μatm')), resp_mg_L_g_hr, fill = pCO2)) + # DRY TISSUE WEIGHT! 'resp_μg_L_g_hr' - note: look at Length_um, resp_norm, and finally resp_mg_L_g_hr to determine why we see this difference..
                theme(panel.grid=element_blank()) +
                geom_boxplot(size=0.2, alpha=0.1, aes(fill=pCO2)) +
                scale_fill_manual(values=c("white","grey50")) +
                geom_point(shape = 21, size = 2, position = position_jitterdodge(jitter.width = 0.1)) +
                theme_classic() +
                #ylim(0, 3) +
                scale_x_discrete(labels= c('~500 μatm', '~800 μatm')) +
                #scale_y_continuous(expand = c(0, 0), limits = c(0, 4.25)) +
                theme(axis.text=element_text(size=12),
                      axis.title=element_text(size=14,face="bold")) +
                stat_summary(fun.y=mean, geom="point", shape=18, size=4, color="black", fill="white") +
                labs(title = "Respiration rate; F1 Scallops (juveniles) 92 days post-fertilization", 
                     y = expression(Respiration~rate~"("~mg~L^{-1}~O[2]%.%g^{-1}%.% hr^{-1}~")"), 
                     x = expression(italic(p)*CO[2]~Treatment~"("~mu*atm~")")) 
Resp_fed_drywt # the effect with normalization to shell size persists here...
```