---
  title: "Respiration Analysis F1 Scallops 2021"
author: "Samuel Gurr"
date: "1/29/2023"
output:
  html_document:
  df_print: paged
pdf_document:
  latex_engine: xelatex
---
  
  
```{r setup, include=FALSE}

# LOAD PACKAGES :::::::::::::::::::::::::::::::::::::::::::::::::::::::

library(dplyr)
library(ggplot2)
library(forcats)
library(lme4)
library(lmerTest)
library(see)
library(performance)
library(car)
library(kableExtra)
library(pander)
library(data.table)
library(stringr)
library(latex2exp)
library(Rmisc)
# library(devtools)
library(ggpubr)
library(hrbrthemes)
library(nlme)
# SET WORKING DIRECTORY :::::::::::::::::::::::::::::::::::::::::::::::

setwd("C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis") # personal computer

# Resp.Master_OM    <- read.csv(file="C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/Calculated_Resp_Master.csv", header=T) # personnel computer 
Resp.Master  <- read.csv(file="C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/Calculated_Resp_Master.csv", header=T) # work computer

# what is our N at each timepoint? 
#9/30/2021 - timepoint Day 0
Resp.Master %>% dplyr::filter(Date == '9/14/2021') %>% 
                       summarySE(measurevar="Length_um", 
                                 groupvars=c("Replicate", "pH", "Fed_Unfed")) # N = 2-3 per replicate
#9/30/2021 - timepoint Day 14
Resp.Master %>% dplyr::filter(Date == '9/30/2021') %>% 
                       summarySE(measurevar="Length_um", 
                                 groupvars=c("Replicate", "pH", "Fed_Unfed")) # N = 3-5 per replicate
#10/26/2021 - timepoint Day 42
Resp.Master %>% dplyr::filter(Date == '10/26/2021') %>% 
                       summarySE(measurevar="Length_um", 
                                 groupvars=c("Replicate", "pH", "Fed_Unfed")) # N = 2-3 per replicate


```



# Analysis 





# 9/14/2021 F1 juvenile scallops (50 DPF; Day 0)

**About**

- two pCO2 treatments 

- **before** we culled and started the food limitation trials

#### number of replicates for analysis...

```{r Day 0 replicates and mean resp, echo=FALSE}

# model effect of treatment on resp rate 20210507
Resp_0914 <- Resp.Master %>% 
              dplyr::filter(Date %in% '9/14/2021')  %>% # call only 9/14
              dplyr::filter(!Chamber_tank  %in% 'blank')

Resp_0914 %>% dplyr::group_by(Chamber_tank) %>% dplyr::summarise(n()) # tank replication
# 7.5_A	3			
# 7.5_B	3			
# 7.5_C	3			
# 7.5_D	3			
# 8_A	2	   *2 rep			
# 8_B	3			
# 8_C	2		 *2 rep	
# 8_D	2	   *2 rep

Resp_0914 %>% summarySE(measurevar="resp_umol_hr_bFactorNormLength", groupvars=c("pCO2"))
# 500 μatm	9	0.1656607	0.07775551	0.02591850	0.05976817
# 800 μatm	12	0.1449237	0.06321486	0.01824856	0.04016480
Resp_0914 %>% summarySE(measurevar="resp_µmol_L_mm_Length_hr", groupvars=c("pCO2"))
# 500 μatm	9	0.02215083	0.009248787	0.003082929	0.007109247
# 800 μatm	12	0.02100752	0.011146946	0.003217846	0.007082431


```

### 9/14/2021 linear model, diagnostics, and plots

```{r Day 0 b factor ALL, echo=TRUE, message = FALSE, warning = FALSE}

# Objective: run AOV and LME for the data, rationale being that we have mutliple samples per replicate tank
# thus important that we address this random effect. Performing AOV and LME allows us to run model selection using AIC 
# to determine the model with the better fit 



# b FACTOR ALL ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# note: day 0 of initiating the food treatment thus ONLY b factor ALL is used in this chuck for 9/14



# plot the replicates (visual diagnostics of random factor)
Resp_0914_menas         <- Resp_0914 %>% summarySE(measurevar="resp_umol_hr_bFactorNormLength", groupvars=(c("Replicate", "pCO2")))
Resp914_bLengthALL_reps <- ggboxplot(Resp_0914, 
                                    x = "pCO2", 
                                    y = "resp_umol_hr_bFactorNormLength", 
                                    color = "Replicate",
                              add = c("mean_se", "dotplot"),
                              palette = c("#00AFBB", "#E7B800", "brown", "grey"))
Resp914_bLengthALL_reps

# One-way ANOVA (without the random effect) 
AOV914.bfactALL <- aov(resp_umol_hr_bFactorNormLength ~ 
                       pCO2, 
                     data=Resp_0914_menas) # run mod
# check model assumptions
shapiro.test(residuals(AOV914.bfactALL)) # normal - 0.3459
leveneTest(AOV914.bfactALL) # homogeneity of variance (equal variance) - 0.5633
# all is good, lets see the results
pander(anova(AOV914.bfactALL), style='rmarkdown') # anova table of lm
# |    &nbsp;     | Df |  Sum Sq   |  Mean Sq  | F value | Pr(>F) |
# |:-------------:|:--:|:---------:|:---------:|:-------:|:------:|
# |   **pCO2**    | 1  | 0.0002315 | 0.0002315 | 0.06877 | 0.8019 |
# | **Residuals** | 6  |  0.0202   | 0.003367  |   NA    |   NA   |
# output results 
kable(data.frame(unclass(summary(AOV914.bfactALL)), 
                   check.names = FALSE, 
                   stringsAsFactors = FALSE)  ) %>%  # print a png of this table
  kable_styling() %>%
  save_kable(file = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/20210914_figs_tables/20210914_AOV_RR_bfactor_ALL.png", zoom = 1.5)


Resp_0914_menas %>% summarySE(measurevar="resp_umol_hr_bFactorNormLength", groupvars=(c("pCO2")))
# 500 μatm	4	0.1556832	0.06784226	0.03392113	
# 800 μatm	4	0.1449237	0.04615994	0.02307997	

# plot
Resp914_Length <- ggplot(Resp_0914, 
                         aes(x = factor(pCO2, level = c('500 μatm', '800 μatm')), 
                             resp_umol_hr_bFactorNormLength , 
                             fill = pCO2)) +
                    theme(panel.grid=element_blank()) +
                    geom_boxplot(size=0.2, width=0.5, alpha=0.1, aes(fill=pCO2)) +
                    scale_fill_manual(values=c("white","grey50")) +
                    geom_point(shape = 21, size = 2, position = position_jitterdodge(jitter.width = 0.1)) +
                    theme_classic() +
                    scale_x_discrete(labels= c('~500 μatm', '~800 μatm')) +
                   # scale_y_continuous(expand = c(0, 0), limits = c(0, 2)) +
                    labs(title = "F1 Scallops: respiration rates on 20210914 (b factor 2.13)", 
                         y = expression(Respiration~rate~"("~μmol~L^{-1}~O[2]%.%mm~shell~length^{-1}%.% hr^{-1}~")"),
                         x = expression(italic(p)*CO[2]~Treatment~"("~μ*atm~")")) + 
                    theme(axis.text=element_text(size=8),
                          axis.title=element_text(size=8,face="bold")) +
                     stat_summary(fun.y=mean, geom="point", shape=18, size=4, color="black", fill="white") 
Resp914_Length # print this figure...


# Export the figures to pdf
ggarrange(Resp914_Length,Resp914_bLengthALL_reps,nrow = 2) %>%
  ggexport(filename = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/20210914_figs_tables/20210914_RR_bfactor_ALL.pdf")

```

### density plot; 50 DPF b factor all 

```{r, Day 0 density respiration plot }
library(dplyr)
library(tidyr)
library(tidyverse)

Resp_0914$pCO2 <- as.factor(Resp_0914$pCO2)

df_mean <- Resp_0914 %>% 
  dplyr::group_by(pCO2) %>% 
  dplyr::summarize(average = mean(resp_umol_hr_bFactorNormLength)) %>%
  dplyr::ungroup()
p.box <- ggplot(Resp_0914, aes(x = pCO2, y = resp_umol_hr_bFactorNormLength)) + geom_boxplot() + geom_point(data= df_mean, mapping = aes(x = pCO2, y = average),
             color="red") 
p.box.data <- layer_data(p.box) %>%
  select(x, ymin, lower, middle, upper, ymax, outliers, flipped_aes) %>%
  dplyr::rename(mean = flipped_aes) %>% 
  dplyr::mutate(mean  = df_mean$average) %>% 
  mutate(pCO2 = factor(x, labels = levels(Resp_0914$pCO2), ordered = TRUE)) %>%
  select(-x)

p.box.data %>% unnest(outliers)

denisty_box_resp_50DPF <-ggplot(p.box.data) +
                            # manually plot flipped boxplot
                            geom_segment(aes(x = ymin, xend = ymax, y = -0.15, yend = -0.15)) +
                            geom_rect(aes(xmin = lower, xmax = upper, ymin = -0.3, ymax = 0,  fill = pCO2),color = "black") +
                            # geom_point(data = . %>% unnest(outliers), aes(x = outliers, y = -0.15), color = "grey60", size = 1) +
                            # vertical lines at Q1 / Q2 / Q3
                            geom_vline(data = . %>% select(pCO2, lower, mean, upper) %>% gather(key, value, -pCO2), aes(xintercept = value)) +
                            # density plot
                            geom_density(data = Resp_0914, aes(x = resp_umol_hr_bFactorNormLength, group=pCO2, fill=pCO2, ..scaled..), alpha=.4, adjust=1.5) +
                            #  theme
                            theme_classic() +
                            xlim(0, 0.4) +
                            facet_grid(pCO2 ~ .) +
                            theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.position = "none", plot.title = element_text(size=10))+
                            labs(title = "F1 Scallops: respiration rates 50 DPF - b factor ALL", 
                                 x = expression(Respiration~rate~"("~μmol~L^{-1}~O[2]%.%mm^{-1}~shell~length%.% hr^{-1}~")"),
                                 y = "Scaled density") +
                            scale_fill_manual(values=c("grey85", "grey40"))
denisty_box_resp_50DPF


pdf(paste0(filename = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/20210914_figs_tables/20210914_RRbfactorALL_density_plot.pdf"), width = 5, height = 5)
denisty_box_resp_50DPF # print the model diagnostics 
dev.off()


```







# 9/30/2021 F1 juvenile scallops (64 DPF; Day 14)

**About**

- two pCO2 treatments 

- *before* we culled and started the food limitation trials

#### number of replicates for analysis...

```{r Day 14 replicates, echo=FALSE}

Resp_0930 <- Resp.Master %>% 
  dplyr::filter(Date %in% '9/30/2021')  %>% # call only 9/14
  dplyr::mutate(pHxFood = paste(pH,Fed_Unfed, sep = "_")) %>% 
  dplyr::mutate(random_fact = as.factor(paste(Chamber_tank, Fed_Unfed, sep="_")))

kable(Resp_0930 %>% dplyr::group_by(Chamber_tank, Fed_Unfed) %>% dplyr::summarise(n())) # tank replication - lowest value was 2 for 7.5_D unfed

Resp_0930 %>% summarySE(measurevar="resp_umol_hr_bFactorNormLength", groupvars=c("Replicate", "pCO2", "Fed_Unfed")) # N = 3-5 per replicate
Resp_0930 %>% summarySE(measurevar="resp_umol_hr_bFactorNormLength", groupvars=c("pCO2", "Fed_Unfed"))
# 500 μatm	High food	19	0.08614212	0.04664712	0.01070158	0.02248319
# 500 μatm	Low food	14	0.07446157	0.04203543	0.01123444	0.02427054
# 800 μatm	High food	19	0.12394695	0.07472190	0.01714238	0.03601481
# 800 μatm	Low food	13	0.08622311	0.08609035	0.02387717	0.0520
Resp_0930 %>% summarySE(measurevar="resp_µmol_L_mm_Length_hr", groupvars=c("pCO2", "Fed_Unfed"))
# 500 μatm	High food	19	0.02029274	0.012767128	0.002928980	0.006153559
# 500 μatm	Low food	14	0.01350541	0.008766077	0.002342833	0.005061382
# 800 μatm	High food	19	0.02719411	0.015975476	0.003665026	0.007699933
# 800 μatm	Low food	13	0.01426890	0.014730817	0.004085593	0.008901743
```

### Statistical models

```{r Day 14 Stats b factor, echo=TRUE, message = FALSE, warning = FALSE}

# Objective: run AOV and LME for the data, rationale being that we have mutliple samples per replicate tank
# thus important that we address this random effect. Performing AOV and LME allows us to run model selection using AIC 
# to determine the model with the better fit 


# NOTE: 
# this chunk demonstrates that our data is non-normally distributed, thus we will need 
# to either transform to resolve or resort to a nonparametric test
# given we have a two-way factorial design (in our simple linear model) we can use the Scheirer-Ray-Hare Test 
# https://rcompanion.org/handbook/F_14.html
library(rcompanion) # install.packages('rcompanion')
library(FSA)
# install.packages('FSA')


# b FACTOR ALL  'resp_umol_hr_bFactorNormLength.ALL' ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# note: day 0 of initiating the food treatment thus ONLY b factor ALL is used in this chuck for 9/14

# Visualize the data with the random effect of tank replicate 
Resp930_bLengthALL_reps <- ggboxplot(Resp_0930, 
                                 x = "pHxFood", 
                                 y = "resp_umol_hr_bFactorNormLength", 
                                 color = "Replicate",
          add = c("mean_se", "dotplot"),
          palette = c("#00AFBB", "#E7B800", "brown", "grey"))
Resp930_bLengthALL_reps

# One-way ANOVA (without the random effect) 
Resp_0930_means <- Resp_0930 %>% summarySE(measurevar="resp_umol_hr_bFactorNormLength", groupvars=(c("Replicate", "Fed_Unfed", "pCO2")))
AOV930.bfactALL <- aov(resp_umol_hr_bFactorNormLength ~ 
                       pCO2 * Fed_Unfed, 
                     data=Resp_0930_means) # run mod
# check model assumptions
shapiro.test(residuals(AOV930.bfactALL)) # non-normal - 0.4293
leveneTest(AOV930.bfactALL) # 0.3586
pander(anova(AOV930.bfactALL), style='rmarkdown') # anova table of lm# run the non parametric
# |       &nbsp;       | Df |  Sum Sq   |  Mean Sq  | F value | Pr(>F) |
# |:------------------:|:--:|:---------:|:---------:|:-------:|:------:|
# |      **pCO2**      | 1  | 0.002403  | 0.002403  |  2.164  | 0.167  |
# |   **Fed_Unfed**    | 1  | 0.002821  | 0.002821  |  2.541  | 0.1369 |
# | **pCO2:Fed_Unfed** | 1  | 0.0007556 | 0.0007556 | 0.6805  | 0.4255 |
# |   **Residuals**    | 12 |  0.01332  |  0.00111  |   NA    |   NA   |

#output
kable(data.frame(unclass(summary(AOV930.bfactALL)), 
                   check.names = FALSE, 
                   stringsAsFactors = FALSE)  ) %>%  # print a png of this table
  kable_styling() %>%
  save_kable(file = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/20210930_figs_tables/20210930_AOV_RR_bfactor_ALL.png", zoom = 1.5)



# In summary, we looked at our non-normal LME and AOV and again found the simple model outweighs the variance 
# explained when the random factor was addressedin the LME, thus we will moved forward with the simple model 
# as opposed to transforming the data, used the Scheirer-Ray-Hare Test as a nonparametric two-factor test 
# the outcome of which did not change relative to the non-normal AOV 
# result: report the SRH test 

# food supply diff - report this percent difference alonside the significant effect
Resp_0930 %>% summarySE(measurevar="resp_umol_hr_bFactorNormLength", groupvars="Fed_Unfed")
perc_diff <- (0.10504454 - 0.08012453)/0.10504454*100
perc_diff #23.72328 %


# plot
Resp930_Length <- ggplot(Resp_0930, 
                         aes(x = factor(pCO2, level = c('500 μatm', '800 μatm')), 
                             resp_umol_hr_bFactorNormLength , 
                             fill = pCO2)) +
                    theme(panel.grid=element_blank()) +
                    geom_boxplot(size=0.2, width=0.5, alpha=0.1, aes(fill=pCO2)) +
                    scale_fill_manual(values=c("white","grey50")) +
                    geom_point(shape = 21, size = 2, position = position_jitterdodge(jitter.width = 0.1)) +
                    theme_classic() +
                    scale_x_discrete(labels= c('~500 μatm', '~800 μatm')) +
                   # scale_y_continuous(expand = c(0, 0), limits = c(0, 2)) +
                    labs(title = "F1 Scallops: respiration rates on 20210930 (b factor 2.0)", 
                         y = expression(Respiration~rate~"("~μmol~L^{-1}~O[2]%.%mm~shell~length^{-1}%.% hr^{-1}~")"),
                         x = expression(italic(p)*CO[2]~Treatment~"("~μ*atm~")")) + 
                    theme(axis.text=element_text(size=8),
                          axis.title=element_text(size=8,face="bold")) +
                    stat_summary(fun.y=mean, geom="point", shape=18, size=4, color="black", fill="white") + 
                    facet_wrap(~Fed_Unfed)  
Resp930_Length # print this figure...


# Export the figures to pdf
ggarrange(Resp930_Length,Resp930_bLengthALL_reps,nrow = 2) %>%
  ggexport(filename = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/20210930_figs_tables/20210930_RR_bfactor_ALL.pdf")





```

### density plot - Day 64; b factor all 

```{r, Day 14 density plot - b factor ALL}
library(dplyr)
library(tidyr)
Resp_0930$pHxFood <- as.factor(Resp_0930$pHxFood)

df_mean <- Resp_0930 %>% 
  dplyr::group_by(pHxFood) %>% 
  dplyr::summarize(average = mean(resp_umol_hr_bFactorNormLength)) %>%
  dplyr::ungroup()
p.box <- ggplot(Resp_0930, aes(x = pHxFood, y = resp_umol_hr_bFactorNormLength)) + geom_boxplot() + geom_point(data= df_mean, mapping = aes(x = pHxFood, y = average),
             color="red") 
p.box.data <- layer_data(p.box) %>%
  select(x, ymin, lower, middle, upper, ymax, outliers, flipped_aes) %>%
  dplyr::rename(mean = flipped_aes) %>% 
  dplyr::mutate(mean  = df_mean$average) %>% 
  mutate(pHxFood = factor(x, labels = levels(Resp_0930$pHxFood), ordered = TRUE)) %>%
  select(-x)


p.box.data %>% unnest(outliers)

library(tidyverse)
denisty_box_resp_64DPF <-ggplot(p.box.data) +
                            # manually plot flipped boxplot
                            geom_segment(aes(x = ymin, xend = ymax, y = -0.15, yend = -0.15)) +
                            geom_rect(aes(xmin = lower, xmax = upper, ymin = -0.3, ymax = 0,  fill = pHxFood),color = "black") +
                            # geom_point(data = . %>% unnest(outliers), aes(x = outliers, y = -0.15), color = "grey60", size = 1) +
                            # vertical lines at Q1 / Q2 / Q3
                            geom_vline(data = . %>% select(pHxFood, lower, mean, upper) %>% gather(key, value, -pHxFood), aes(xintercept = value)) +
                            # density plot
                            geom_density(data = Resp_0930, aes(x = resp_umol_hr_bFactorNormLength, group=pHxFood, fill=pHxFood, ..scaled..), alpha=.4, adjust=1.5) +
                            #  theme
                            theme_classic() +
                            xlim(0, 0.22) +
                            facet_grid(pHxFood ~ .) +
                            theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.position = "none", plot.title = element_text(size=10))+
                            labs(title = "F1 Scallops: respiration rates 64 DPF - b factor ALL", 
                                 x = expression(Respiration~rate~"("~μmol~L^{-1}~O[2]%.%mm^{-1}~shell~length%.% hr^{-1}~")"),
                                 y = "Scaled density") +
                            scale_fill_manual(values=c("grey40", "grey40", "grey85", "grey85"))
denisty_box_resp_64DPF


pdf(paste0(filename = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/20210930_figs_tables/20210930_RRbfactorALL_density_plot.pdf"), width = 5, height = 5)
denisty_box_resp_64DPF # print the model diagnostics 
dev.off()

```










# 10/26/2021 F1 juvenile scallops  (92 DPF; Day 42)

**About**

- two pCO2 treatments 

- *before* we culled and started the food limitation trials


#### number of replicates for analysis...

```{r Day 42 replicates, echo=FALSE}

Resp_1026 <- Resp.Master %>% 
  dplyr::filter(Date %in% '10/26/2021')  %>% # call only 10/14
  dplyr::mutate(pHxFood = paste(pH,Fed_Unfed, sep = "_")) %>% 
  dplyr::mutate(random_fact = as.factor(paste(Chamber_tank, Fed_Unfed, sep="_")))

kable(Resp_1026 %>% dplyr::group_by(Chamber_tank, Fed_Unfed) %>% dplyr::summarise(n())) # tank replication

Resp_1026 %>% summarySE(measurevar="resp_umol_hr_bFactorNormLength", groupvars=c("Replicate", "pCO2", "Fed_Unfed")) # N = 1-2 per replicate
Resp_1026 %>% summarySE(measurevar="resp_umol_hr_bFactorNormLength", groupvars=c("pCO2", "Fed_Unfed"))
# 500 μatm	High food	8	0.06654692	0.01569754	0.005549918	0.01312347
# 500 μatm	Low food	7	0.05031502	0.02884012	0.010900542	0.02667267
# 800 μatm	High food	6	0.09383471	0.05018298	0.020487116	0.05266381
# 800 μatm	Low food	8	0.05709843	0.02716047	0.009602677	0.02270672
Resp_1026 %>% summarySE(measurevar="resp_µmol_L_mm_Length_hr", groupvars=c("pCO2", "Fed_Unfed"))
# 500 μatm	High food	8	0.045939505	0.015998508	0.005656327	0.013375087
# 500 μatm	Low food	7	0.009712373	0.006445488	0.002436165	0.005961082
# 800 μatm	High food	6	0.051158106	0.026602999	0.010860629	0.027918136
# 800 μatm	Low food	8	0.012445245	0.006443678	0.002278184	0.005387049

```

## Statistical models

```{r Day 42 Stats b factor, echo=TRUE, message = FALSE, warning = FALSE}


# Objective: run AOV and LME for the data, rationale being that we have mutliple samples per replicate tank
# thus important that we address this random effect. Performing AOV and LME allows us to run model selection using AIC 
# to determine the model with the better fit 


# NOTE: 
# this chunk demonstrates that our data is non-normally distributed, thus we will need 
# to either transform to resolve or resort to a nonparametric test
# given we have a two-way factorial design (in our simple linear model) we can use the Scheirer-Ray-Hare Test 
# https://rcompanion.org/handbook/F_14.html
library(rcompanion) # install.packages('rcompanion')
library(FSA)
# install.packages('FSA')



# b FACTOR ALL  'resp_umol_hr_bFactorNormLength.ALL' ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# note: day 0 of initiating the food treatment thus ONLY b factor ALL is used in this chuck for 9/14

# Visualize the data with the random effect of tank replicate 
Resp1026_bLengthALL_reps <- ggboxplot(Resp_1026, 
                                 x = "pHxFood", 
                                 y = "resp_umol_hr_bFactorNormLength", 
                                 color = "Replicate",
          add = c("mean_se", "dotplot"),
          palette = c("#00AFBB", "#E7B800", "brown", "grey"))
Resp1026_bLengthALL_reps

# One-way ANOVA (without the random effect) 
Resp_1026_means <- Resp_1026 %>% summarySE(measurevar="resp_umol_hr_bFactorNormLength", groupvars=(c("Replicate", "Fed_Unfed", "pCO2")))
AOV1026.bfactALL <- aov(resp_umol_hr_bFactorNormLength ~ 
                       pCO2 * Fed_Unfed, 
                     data=Resp_1026_means) # run mod
# check model assumptions
shapiro.test(residuals(AOV1026.bfactALL)) # normal - 0.03366
leveneTest(AOV1026.bfactALL) # homogeneity of variance (equal variance) - 0.07115 .
# run non parametric
SRH1026.bfactALL <- scheirerRayHare(resp_umol_hr_bFactorNormLength ~ 
                       pCO2 * Fed_Unfed, 
                     data=Resp_1026_means) # run mod
# all is good, lets see the results
pander(print(SRH1026.bfactALL), style='rmarkdown') # table for SRH test
# |       &nbsp;       | Df | Sum Sq |    H    | p.value |
# |:------------------:|:--:|:------:|:-------:|:-------:|
# |      **pCO2**      | 1  | 20.25  | 0.8934  | 0.3446  |
# |   **Fed_Unfed**    | 1  | 90.25  |  3.982  |  0.046  |
# | **pCO2:Fed_Unfed** | 1  |   1    | 0.04412 | 0.8336  |
# |   **Residuals**    | 12 | 228.5  |   NA    |   NA    |
# output results 
kable(data.frame(unclass(print(SRH1026.bfactALL)), 
                   check.names = FALSE, 
                   stringsAsFactors = FALSE)  ) %>%  # print a png of this table
  kable_styling() %>%
  save_kable(file = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/20211026_figs_tables/20211026_SRH_RR_bfactor_ALL.png", zoom = 1.5)


# food supply diff - report this percent difference alonside the significant effect
Resp_1026_means %>% summarySE(measurevar="resp_umol_hr_bFactorNormLength", groupvars=c("Fed_Unfed"))
perc_diff <- (0.08590237 - 0.05255883)/0.08590237*100
perc_diff #38.81562 %


# plot
Resp1026_Length <- ggplot(Resp_1026, 
                         aes(x = factor(pCO2, level = c('500 μatm', '800 μatm')), 
                             resp_umol_hr_bFactorNormLength , 
                             fill = pCO2)) +
                    theme(panel.grid=element_blank()) +
                    geom_boxplot(size=0.2, width=0.5, alpha=0.1, aes(fill=pCO2)) +
                    scale_fill_manual(values=c("white","grey50")) +
                    geom_point(shape = 21, size = 2, position = position_jitterdodge(jitter.width = 0.1)) +
                    theme_classic() +
                    scale_x_discrete(labels= c('~500 μatm', '~800 μatm')) +
                   # scale_y_continuous(expand = c(0, 0), limits = c(0, 2)) +
                    labs(title = "F1 Scallops: respiration rates on 202101026 (b factor 2.0)", 
                         y = expression(Respiration~rate~"("~μmol~L^{-1}~O[2]%.%mm~shell~length^{-1}%.% hr^{-1}~")"),
                         x = expression(italic(p)*CO[2]~Treatment~"("~μ*atm~")")) + 
                    theme(axis.text=element_text(size=8),
                          axis.title=element_text(size=8,face="bold")) +
                    stat_summary(fun.y=mean, geom="point", shape=18, size=4, color="black", fill="white") + 
                    facet_wrap(~Fed_Unfed)  
Resp1026_Length # print this figure...


# Export the figures to pdf
ggarrange(Resp1026_Length,Resp1026_bLengthALL_reps,nrow = 2) %>%
  ggexport(filename = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/20211026_figs_tables/202101026_RR_bfactor_ALL.pdf")


```


### density plot - Day 92; b factor all 

```{r, Day 42 density respiration plot }
library(dplyr)
library(tidyr)
Resp_1026$pHxFood <- as.factor(Resp_1026$pHxFood)

df_mean <- Resp_1026 %>% 
  dplyr::group_by(pHxFood) %>% 
  dplyr::summarize(average = mean(resp_umol_hr_bFactorNormLength)) %>%
  dplyr::ungroup()
p.box <- ggplot(Resp_1026, aes(x = pHxFood, y = resp_umol_hr_bFactorNormLength)) + geom_boxplot() + geom_point(data= df_mean, mapping = aes(x = pHxFood, y = average),
             color="red") 
p.box.data <- layer_data(p.box) %>%
  select(x, ymin, lower, middle, upper, ymax, outliers, flipped_aes) %>%
  dplyr::rename(mean = flipped_aes) %>% 
  dplyr::mutate(mean  = df_mean$average) %>% 
  mutate(pHxFood = factor(x, labels = levels(Resp_1026$pHxFood), ordered = TRUE)) %>%
  select(-x)


p.box.data %>% unnest(outliers)

library(tidyverse)
denisty_box_resp_92DPF <-ggplot(p.box.data) +
                            # manually plot flipped boxplot
                            geom_segment(aes(x = ymin, xend = ymax, y = -0.15, yend = -0.15)) +
                            geom_rect(aes(xmin = lower, xmax = upper, ymin = -0.3, ymax = 0,  fill = pHxFood),color = "black") +
                            # geom_point(data = . %>% unnest(outliers), aes(x = outliers, y = -0.15), color = "grey60", size = 1) +
                            # vertical lines at Q1 / Q2 / Q3
                            geom_vline(data = . %>% select(pHxFood, lower, mean, upper) %>% gather(key, value, -pHxFood), aes(xintercept = value)) +
                            # density plot
                            geom_density(data = Resp_1026, aes(x = resp_umol_hr_bFactorNormLength, group=pHxFood, fill=pHxFood, ..scaled..), alpha=.4, adjust=1.5) +
                            #  theme
                            theme_classic() +
                            xlim(0, 0.22) +
                            facet_grid(pHxFood ~ .) +
                            theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.position = "none", plot.title = element_text(size=10))+
                            labs(title = "F1 Scallops: respiration rates 92 DPF - b factor ALL", 
                                 x = expression(Respiration~rate~"("~μmol~L^{-1}~O[2]%.%mm^{-1}~shell~length%.% hr^{-1}~")"),
                                 y = "Scaled density") +
                            scale_fill_manual(values=c("grey40", "grey40", "grey85", "grey85"))
denisty_box_resp_92DPF


pdf(paste0(filename = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/20211026_figs_tables/20211026_RRbfactorALL_density_plot.pdf"), width = 5, height = 5)
denisty_box_resp_92DPF # print the model diagnostics 
dev.off()


```

