---
title: "Respiration Calc F1 Scallops 2021"
author: "Samuel Gurr"
date: "10/6/2021"
output:
  html_document:
    df_print: paged
  pdf_document:
    latex_engine: xelatex
---


```{r setup, include=FALSE}

# LOAD PACKAGES :::::::::::::::::::::::::::::::::::::::::::::::::::::::

library(dplyr)
library(ggplot2)
library(forcats)
library(lme4)
library(lmerTest)
library(see)
library(performance)
library(car)
library(kableExtra)
library(pander)
library(data.table)
library(stringr)
library(latex2exp)
library(Rmisc)
library(ggpubr)
library(hrbrthemes)
library(nlme)
# SET WORKING DIRECTORY :::::::::::::::::::::::::::::::::::::::::::::::

 setwd("C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis") # personal computer
# setwd("C:/Users/samuel.gurr/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis") # Work computer
# setwd("C:/Users/samjg/Documents/Github_repositories/Airradians_OA/RAnalysis") # Work computer

# LOAD DATA :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

resp.data       <- read.csv(file="Output/Respiration/Cumulative_resp_alpha0.4_15sectrunc1hour.csv", header=T) %>% 
                      dplyr::filter(!Date %in% "9/14/2021" | !Filename %in% 'Run_1_raw.txt') # read the calculate raw rates from 'resp_LoLin' script - contains the calculated rate (not normalized for blanks) for each sensor-channel
exp_metadata    <- read.csv(file="Data/ExperimentMetadata.csv", header=T) # treatment assignments to 'Chamber_Tank'
lengths         <- read.csv(file="Data/Respiration/Lengths_Condition_resp_clearance.csv", header=T)
resp.ref        <- read.csv(file="Data/Respiration/Reference_master.csv", header=T) %>% dplyr::filter(!Date %in% "9/14/2021" | !Filename %in% 'Run_1_raw.txt')
DWs_Len_1026    <- read.csv(file="Data/Survival_Size/20211026_lengths_dryweights.csv", header=T)
DWs_Len_914.930 <- read.csv(file="Data/Survival_Size/2021914_930_dryweights.csv", header=T)

```


### Merge master resp data frame with lengths

```{r merge resp with length data and treatment IDs, echo=FALSE}

# merge the exp_metadata with the resp.data
resp.ref_length_merged  <- merge(resp.ref, lengths) # all TRUE allows us to keep the blanks
resp.data_merged        <- merge(resp.data, resp.ref_length_merged) %>% # out master file moving forward....
                                            dplyr::mutate(filetype = 
                                                            str_sub(Filename, -3,-1)) %>%  # column as csv and txt
                                            dplyr::mutate(filetype = 
                                                            factor(ifelse(filetype == "csv", "SDR_data", "LoLigo_data"))) # asign SDR for all csv files and Loligo for all txt files
kable(head(resp.data_merged)) # print in a R markdown format to view

# View(resp.data_merged)
min(as.numeric(resp.data_merged$Length_um/1000)) # 1.011402
max(resp.data_merged$Length_um/1000) # 20.36

(nrow(resp.data_merged %>% dplyr::filter(Length_um/1000 < 3)) /nrow(resp.data_merged) ) *100 # 45.86466 % of data < 3mm length
```

#### Visual diagnostic plots to correct poor data (11 data points to change..)

- View on github: Airradians_OA/RAnalysis/Output/Respiration/plots_alpha0.4_increm15sec/

- below are three examples that represent inaccurate rates of oxygen consumption (and can be corrected!) 

(1) https://github.com/SamGurr/Airradians_OA/blob/master/RAnalysis/Output/Respiration/plots_alpha0.4_increm15sec/20210930_Plate_2_Run_2_C5_regression.pdf
- solution = call 'Lz' instead of the default Leq

(2) https://github.com/SamGurr/Airradians_OA/blob/master/RAnalysis/Output/Respiration/plots_alpha0.4_increm15sec/20210930_Plate_2_Run_1_C1_regression.pdf
- solution = call 'Lz' instead of the default Leq

(3) https://github.com/SamGurr/Airradians_OA/blob/master/RAnalysis/Output/Respiration/plots_alpha0.4_increm15sec/20210930_Plate_1_Run_2_C1_regression.pdf
- solution = we reran this at the end of the LoLin script  for 0-20 minutes and got an Lpc  -0.0296, insert this 

* for all other cases corrected below, either another weighting metric (LZ or Leq as opposed to the Lpc output by LoLinR) or 
a rerun of the data subset w/o noise/error/etc. allowed for a correction - in most cases the rerun was required

```{r IMPORTANT correct poor data, echo=TRUE, message = FALSE, warning = FALSE}

# VISAUL INSPECCTION:::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
#  914 runs...
resp.data_merged[48 ,c(1:6)]  #  CH5	Run_2_raw.txt	-0.005252180	-0.004583581	-0.004583581
resp.data_merged[44 ,c(1:6)]  #  CH3	Run_2_raw.txt	-0.010489214	-0.008507836	-0.008507836
resp.data_merged[36 ,c(1:6)]  #  CH1	Run_2_raw.txt	0.000995514	0.002014487	0.002014487
#resp.data_merged[23 ,c(1:6)]  #  CH5	Run_1_raw.txt	-0.00704407	-0.005910146	-0.005910146 
resp.data_merged[37 ,c(1:6)]  #  CH1	Run_3_raw.txt	-0.01067604	-0.01067604	-0.01067604
resp.data_merged[41 ,c(1:6)]  #  CH2	Run_3_raw.txt	-0.002221288	-0.00212516	-0.00212516
resp.data_merged[45 ,c(1:6)]  #  CH3	Run_3_raw.txt	-0.001386829	-0.00246828	-0.00246828
resp.data_merged[49 ,c(1:6)]  #  CH5	Run_3_raw.txt	-0.01019991	-0.01748781	-0.01748781

# 930 runs...

resp.data_merged[71 ,c(1:6)]  # A5	RR_9.30.21_AM_Plate_1_Run_1.csv	-0.002463294	-0.003383279	-0.003383279
resp.data_merged[95 ,c(1:6)]  #  C1 RR_9.30.21_AM_Plate_2_Run_1.csv # -0.02890813	-0.0608251	-0.0608251 - Lz and Leq  better 
resp.data_merged[111,c(1:6)]  #  C5 RR_9.30.21_PM_Plate_2_Run_2.csv	0.029052351	-0.076034441	-0.076034441
resp.data_merged[96 ,c(1:6)]  #  C1 RR_9.30.21_PM_Plate_1_Run_2.csv	0.011656487	0.011656487	0.011656487 


# CHANGES (based on rerun or whether Lz/Leq better explains) :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

# 914 changes..

resp.data_merged[48 ,4]  <- as.numeric(-0.0154) # RERUN
resp.data_merged[44 ,4]  <- as.numeric(-0.0205) # RERUN
resp.data_merged[36 ,4]  <- as.numeric(-0.0164) # RERUN
#resp.data_merged[23 ,4]  <- as.numeric(-0.0275) # RERUN
resp.data_merged[37 ,4]  <- as.numeric(-0.00123) # RERUN
resp.data_merged[41 ,4]  <- as.numeric(-0.0036)  # RERUN
resp.data_merged[45 ,4]  <- as.numeric(-0.0034)  # RERUN 
resp.data_merged[49 ,4]  <- as.numeric(-0.0207)  # RERUN

# 930 changes..

resp.data_merged[71 ,4]  <- as.numeric(-0.0128) # RERUN
resp.data_merged[95 ,4]  <- resp.data_merged[95,5] # 20210930_Plate_2_Run_2_C5_regression - Lz and Leq regression than Lpc
resp.data_merged[111,4]  <- resp.data_merged[111,5] # 20210930_Plate_2_Run_1_C1_regression - Lz and Leq  regression than Lpc
resp.data_merged[96 ,4]  <- as.numeric(-0.0296) # RERUN
#resp.data_merged[23 ,4]  <- as.numeric(-0.0275) # RERUN


# look at the data for sanity check...

resp.data_merged[44 ,c(1:6)] # -0.0205
resp.data_merged[36 ,c(1:6)] # -0.0164
resp.data_merged[23 ,c(1:6)] # -0.0275
#resp.data_merged[23 ,c(1:6)] # -0.0275
resp.data_merged[37 ,c(1:6)] # -0.00123 
resp.data_merged[41 ,c(1:6)] # -0.0036  
resp.data_merged[45 ,c(1:6)] # -0.0034
resp.data_merged[49 ,c(1:6)] # -0.0207
resp.data_merged[95 ,c(1:6)] # -0.0608251
resp.data_merged[111,c(1:6)] # -0.07603444
resp.data_merged[96 ,c(1:6)] # -0.0296	

# View(resp.data_merged)
```

#### Calculate blank rates, view means by day pH_treatment and instrument

* note: respiration rates were recorded using both SDR dish (24 channel) and Loligo 8-channel sensors - different blanks for each

```{r call blanks, echo=FALSE}

blanks_total <- data.frame() # start dataframe 
blanks.table <- data.frame(matrix(nrow = 1,ncol = 5)) # make a table template
colnames(blanks.table)<-c('Date', 'Channel', 'mean_Lpc', 'mean_Leq' , 'mean_Lz') # names for comuns in the for loop

# filter all blanks and edit where needed
blanks_all_raw <- data.frame(merge(resp.ref, resp.data, by = c('Date', 'Channel', 'Filename')) %>% 
                  dplyr::filter(!Date ==  '9/14/2021'   | !Filename == 'Run_1_raw.txt') %>%  # run 1 was restarted due to poor data
                  dplyr::mutate(filetype = str_sub(Filename, -3,-1)) %>% 
                  dplyr::mutate(filetype = factor(ifelse(filetype == "csv", "SDR_data", "LoLigo_data"))) %>% 
                  dplyr::filter(Chamber_tank  == 'blank') %>% # filter all ocurances of blank
                  dplyr::filter(!Date == '9/30/2021' | !Lpc < -0.035) %>% #omits C6 RR_9.30.21_AM_Plate_1_Run_1.csv	8.0	blank - View the Lolin plot, looks noisy and a fast outlier from the others
                  dplyr::filter(!Date == '10/26/2021'  | !Channel == "CH8" | !Run == "2" ) %>%  # omit a bad blank that contained a bad seal, noted on the respiration sampling day during the trial 
                  #dplyr::filter(!Date == '10/26/2021'  | !Channel == "CH8" | !Run == "3" ) %>%  # omit a bad blank that contained a bad seal, noted on the respiration sampling day during the trial 
                  dplyr::filter(!Date ==  '9/30/2021'   | !pH == "7.5" | !Channel == "B2" | !Run == "1" | !Plate == "1" ) %>% # abnormal high rate for a blank - omission approximates the mean blank for the other treatment (bad data)
                  dplyr::select(c(Date, pH, Run, Plate, Lpc, Leq ,Lz, Channel, Food, Filename, filetype, Chamber_tank)) %>% # select desired columns
                  dplyr::arrange(Date, Run, pH)) # arrange the dataset to have consistant read out for process below...
kable(blanks_all_raw)


# blank means by date*pH*run
blanks_means <- blanks_all_raw %>% 
     dplyr::group_by(Date, pH, Run, filetype) %>% 
     dplyr::filter(Chamber_tank == "blank") %>% 
     dplyr::filter(Lpc <0) %>% # ommit blank calls that d/n represent oxygen consumption
     dplyr::summarise(BLANK.mean_Lpc = mean(abs(Lpc)),
                      BLANK.sd.Lpc   = sd(abs(Lpc)),
                      BLANK.mean_Leq = mean(abs(Leq)), 
                      BLANK.mean_Lz = mean(abs(Lz)),
                      n = n()) %>% 
    dplyr::arrange(Date, Run)
kable(blanks_means) # IMPORTANT! notice there are no blanks for pH 7.5  runs 2 on 10/26 and run 1  9 /14

# we have some absent data, in this case 'dups_to_add' adds the opposite treatment blank (i.e. 7.5 no blank, assigned as 8's blank)
dups_to_add <- blanks_means[c(5,8),] %>% # call blanks for pH 8 runs 2 and 3 on 10/26 and run 1  9 /14
              dplyr:: mutate(pH = 7.5) # assign 7.5 pH
blanks_means <- rbind(blanks_means, dups_to_add) %>% # bind on the rows 
  dplyr::arrange(Date, Run) 
kable(blanks_means) # you can now see that each Date, Run, has a pH 8 and pH 7.5 blank
```


#### Merge blanks with the master file by Date, pCO2 treatment, and filetype

* 'filteype' is only important here on 20211026 when both Loligo and SDR were used due to difference in size for fed (larger) and unfed animals 

```{r merge blanks_means for a master file, echo=FALSE}

Resp.Master <- merge(resp.data_merged, 
                     blanks_means, by=c("Date", "pH", "Run", "filetype")) %>% # NOTE: this repeats for every distinct length value
               dplyr::mutate(resp_blankStand = 
                                abs(Lpc) - BLANK.mean_Lpc) # ommits respiration rate values showing an increase in O2 over time 

Resp.less.than.blank <- Resp.Master %>% 
                          dplyr::filter(resp_blankStand < 0) %>% 
                          dplyr::select(c(1:7,15,18,29)) %>% 
                          mutate(Lpc = abs(Lpc)) # call the values with positive resp rates, measing they were slower than the blank!
print(Resp.less.than.blank) # 17 total samples were less than the blank after the correction... (Lpc < BLANK.mean_LPC)

```


## Master Resp file 'Resp.Master_OM', with volumes and file types, etc. saved as 'Calculated_Resp_Master.csv'

######  dplyr::mutate for the following:

* 'volume' of the different vessels throughout the fed*OA challenge
* 'Age'
* 'Fed_unfed'
* 'pCO2'

```{r master resp file, echo=FALSE}

Resp.Master_OM <- Resp.Master[!is.na(Resp.Master$Length_um),] %>% 
  # omit resp values less than the blank
  dplyr::filter(!resp_blankStand < 0) %>% # omit respiration values subtracted by blank (resp_blankStand) that are negative (less than the blank)
  # new colums with the experimental conditions                   
  dplyr::mutate(Age = case_when(Date == '9/14/2021' ~ 50, Date == '9/30/2021' ~ 66, Date == '10/26/2021' ~ 92)) %>% 
  dplyr::mutate(Fed_Unfed = case_when(
    Fed_Unfed == 'F' ~ "High food", is.na(Fed_Unfed) ~ "High food", 
    Fed_Unfed == 'U' ~ "Low food")) %>% 
  dplyr::mutate(pCO2 = case_when(
    pH == 8.0 ~ "500 μatm", 
    pH == 7.5 ~ "800 μatm")) %>% 
  # the volume of the cahmbers 
  dplyr::mutate(volume = case_when(
     filetype == "LoLigo_data" & Date %in% c('9/14/2021','9/30/2021') ~ 2.2,# fed F1 foodxOA
     filetype == "SDR_data" & Date %in% c('9/30/2021','10/26/2021')~ 1.7, # small unfed F1s foodxOA; 24-well plate - 1700ul 
     # filetype == "LoLigo_data" & Date %in% c('10/26/2021') & Channel == 'CH1' ~ 23.1, 
     # filetype == "LoLigo_data" & Date %in% c('10/26/2021') & Channel == 'CH2' ~ 23.05, 
     # filetype == "LoLigo_data" & Date %in% c('10/26/2021') & Channel == 'CH4' ~ 22.55,
     # filetype == "LoLigo_data" & Date %in% c('10/26/2021') & Channel == 'CH5' ~ 23.18,
     # filetype == "LoLigo_data" & Date %in% c('10/26/2021') & Channel == 'CH6' ~ 23.24,
     # filetype == "LoLigo_data" & Date %in% c('10/26/2021') & Channel == 'CH7' ~ 22.63, 
     # filetype == "LoLigo_data" & Date %in% c('10/26/2021') & Channel == 'CH8' ~ 22.95,
     # filetype == "LoLigo_data" & Date %in% c('10/26/2021') & Channel == 'CH3' ~ 23.31
     filetype == "LoLigo_data" & Date %in% c('10/26/2021') & Channel == 'CH1' ~ 68.55323, # F1 data
     filetype == "LoLigo_data" & Date %in% c('10/26/2021') & Channel == 'CH2' ~ 68.85583, 
     filetype == "LoLigo_data" & Date %in% c('10/26/2021') & Channel == 'CH4' ~ 68.95481,
     filetype == "LoLigo_data" & Date %in% c('10/26/2021') & Channel == 'CH5' ~ 68.57288,
     filetype == "LoLigo_data" & Date %in% c('10/26/2021') & Channel == 'CH6' ~ 68.01878,
     filetype == "LoLigo_data" & Date %in% c('10/26/2021') & Channel == 'CH7' ~ 68.54551, 
     filetype == "LoLigo_data" & Date %in% c('10/26/2021') & Channel == 'CH8' ~ 68.53297,
     filetype == "LoLigo_data" & Date %in% c('10/26/2021') & Channel == 'CH3' ~ 68.87473)) %>% #larger custom vessels measured individually...
  # factor in the biovolume (volume displaced from the animal) to get the actual calculated volume of the chambers
  dplyr::mutate(Length_mm = Length_um/1000) %>% # Length in millimeters
  dplyr::mutate(Biovol_length3 = (0.000198*(Length_mm^3)))  %>% # biovoume calc using length(mm)^3; 0.000198 from a regression run with all F1 data 
  dplyr::mutate(calculated_volume = (volume - Biovol_length3)) %>%  # actual volume of the vessel accounting for the volume displaced (length^3 equivelent to the measured biovolume)
  # REspiration units mg minute -> mg L hr
  dplyr::mutate(resp_mg_L_hr =(resp_blankStand *  # resp corrected for blank (remember within Date, Run and treatment!) - currently as raw units of mg O2 per minute (output from LoLinR script)
                                      (calculated_volume/1000) * # mult vessel corrected in Liters - now units in  mg per L per min
                                       60))  %>% # mult by 60 to convert to hours - now units in mg L per hour
  dplyr::mutate(resp_umol_L_hr =  (resp_mg_L_hr * 1000) / 32) #  convert mg L per hr to umol L hr- first by mg to ug (mg*1000 = ug) and then ug to umol (1 umol = 32 ug -  ug O2 div 32 ug/umol)          

Resp.Master %>% dplyr::filter(resp_blankStand < 0) # 17 rows omitted 
```

# ALOMETRIC COEFFICIENT (b factor) 

## by SHELL AND INDIVIDUAL LENGTH (only for biovolume calculated using length^3)

* why? - we want to compare resp data across time however we did not measure dry tissue nor biovolume in samll animals, thus 
to calculate resp using the sample methods across time, we used length^3 correction for biovolume and will further use a bfactor for shell length in these data 

* note: this is in contrast to resp values used for SFG, O:N, and any overlaid phys with ecretion and biodeposition becasue animals were large enough to have tissue dry weights and biovolumes 

## Using OLS Linear Regression Models! 

* OLS is the ordinary least squares to find the simple linear regression for your data 
* this method is common when your variance in Y outweighs the variance in X (e.g. populations X axis and rates of growth Y axis)
```{r b factor SHELL LENGTH outlier omitted, echo=TRUE, echo = FALSE,message = FALSE, warning = FALSE, results='hide'}

# FOR SHELL ENGTH WE WILL USE THE 'resp_umol_hr_biovolcalc' data to employ all resp data files across time! 
# ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# GET B FACTOR FOR ALL AVAILABLE INDIVIDUALS WITH LENGTH AND MO2 ::::::::::::::::::::::::::::::
nrow(Resp.Master_OM) # 115

Resp.Master_bfactor_plotting <- Resp.Master_OM %>% 
  dplyr::mutate(log10_VO2     = log10(as.numeric(Resp.Master_OM$resp_umol_L_hr)) ) %>%  # assign resp value
  dplyr::mutate(log10_Length  = log10(as.numeric(Resp.Master_OM$Length_um)) ) %>% # assign length value 
  dplyr::mutate(Food_OA       = paste(Resp.Master_OM$pCO2, Resp.Master_OM$Fed_Unfed, sep = "_")) # two-way factor to facet plots by  

Resp.Master_bfactor_plottingOM <- Resp.Master_bfactor_plotting %>% 
  # one outlier value that is omitted for parallet graphical outputsn with the non-omitted data 
  dplyr::filter(!(log10_Length > 3.8 & log10_VO2 < -2))  # outliers ommited (a ingle data point)


MO2_b.factorLENGTH_PLOT <- Resp.Master_bfactor_plotting %>% 
                           ggplot(aes(x=log10_Length, y=log10_VO2)) +
                              geom_point(size=2) +
                              theme(panel.grid.major = element_blank(), 
                                    panel.grid.minor = element_blank())+ 
                              scale_x_continuous(name ="log10_Length; in mm") +
                              scale_y_continuous(name ="log10_MO2; RR in umol L-1 hr-1)") +
                              theme_classic() +
                              theme(legend.position="none",
                                              element_line(linewidth = 0.5, 
                                                           color = 'black'),
                                              axis.title.y=element_text(size=12),
                                              axis.text.x=element_text(size=(15)),
                                              axis.text.y=element_text(size=(15))) + # legend.position="none",
                              ggtitle("Metabolic scaling: log10_MO2 = log10_a + 
                                      (b.factor * log10_Length)") +
                              geom_smooth(method = lm, color = 'black') +
                              ggpmisc::stat_poly_eq(parse=T, 
                                                    aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
                                                    label.x.npc = "left")
MO2_b.factorLENGTH_PLOT_facetted <- Resp.Master_bfactor_plotting %>% 
                                     ggplot(aes(x=log10_Length, y=log10_VO2, color = pCO2)) +
                                        geom_point() +
                                        scale_color_manual(values=c("blue","orange")) +
                                        theme(panel.grid.major = element_blank(), 
                                              panel.grid.minor = element_blank())+ 
                                        scale_x_continuous(name ="log10_Length; in mm") +
                                        scale_y_continuous(name ="log10_MO2; RR in umol L-1 hr-1)") +
                                        theme_classic() +
                                        theme(legend.position="none",axis.title.y=element_text(size=7)) +
                                        ggtitle("Metabolic scaling: log10_MO2 = log10_a + 
                                                (b.factor * log10_Length)") +
                                        geom_smooth(method = lm, color = 'red') +
                                        ggpmisc::stat_poly_eq(parse=T, 
                                                              aes(label = paste(..eq.label..,
                                                                                ..rr.label.., sep = "~~~")),
                                                              label.x.npc = "left") +
                                        facet_wrap(~Food_OA)
MO2_b.factorLENGTH_PLOT_facetted_food <- Resp.Master_bfactor_plotting %>% 
                                     ggplot(aes(x=log10_Length, y=log10_VO2)) + # omitted , color = pCO2
                                        geom_point() +
                                        #scale_color_manual(values=c("blue","orange")) +
                                        theme(panel.grid.major = element_blank(), 
                                              panel.grid.minor = element_blank())+ 
                                        scale_x_continuous(name ="log10_Length; in mm") +
                                        scale_y_continuous(name ="log10_MO2; RR in umol L-1 hr-1)") +
                                        theme_classic() +
                                        theme(legend.position="none",axis.title.y=element_text(size=7)) +
                                        ggtitle("Metabolic scaling: log10_MO2 = log10_a + 
                                                (b.factor * log10_Length)") +
                                        geom_smooth(method = lm, color = 'red') +
                                        ggpmisc::stat_poly_eq(parse=T, 
                                                              aes(label = paste(..eq.label..,
                                                                                ..rr.label.., sep = "~~~")),
                                                              label.x.npc = "left") +
                                        facet_wrap(~Fed_Unfed)
MO2_b.factorLENGTH_PLOT_facetted_pCO2 <- Resp.Master_bfactor_plotting %>% 
                                     ggplot(aes(x=log10_Length, y=log10_VO2)) +
                                        geom_point() +
                                        #scale_color_manual(values=c("blue","orange")) +
                                        theme(panel.grid.major = element_blank(), 
                                              panel.grid.minor = element_blank())+ 
                                        scale_x_continuous(name ="log10_Length; in mm") +
                                        scale_y_continuous(name ="log10_MO2; RR in umol L-1 hr-1)") +
                                        theme_classic() +
                                        theme(legend.position="none",axis.title.y=element_text(size=7)) +
                                        ggtitle("Metabolic scaling: log10_MO2 = log10_a + 
                                                (b.factor * log10_Length)") +
                                        geom_smooth(method = lm, color = 'red') +
                                        ggpmisc::stat_poly_eq(parse=T, 
                                                              aes(label = paste(..eq.label..,
                                                                                ..rr.label.., sep = "~~~")),
                                                              label.x.npc = "left") +
                                        facet_wrap(~pCO2)


 # OUTPUT PLOTS 
pdf(paste0(filename = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/metabolic_scaling/MetabolicScaling_bFactor_Length_ALL.pdf"), width = 8, height = 25)
print(ggarrange(MO2_b.factorLENGTH_PLOT, 
                MO2_b.factorLENGTH_PLOT_facetted, 
                MO2_b.factorLENGTH_PLOT_facetted_pCO2,
                MO2_b.factorLENGTH_PLOT_facetted_food,
                nrow = 4, ncol = 1)) # print the model diagnostics
dev.off()



MO2_b.factorLENGTH_PLOT_facetted_ALL <- Resp.Master_bfactor_plotting %>% 
                                     ggplot(aes(x=log10_Length, 
                                                y=log10_VO2, 
                                                color = Food_OA,
                                                shape = Food_OA)) +
                                        geom_point(size = 2) +
                                        #scale_color_manual(values=c("blue","orange")) +
                                        scale_color_manual(values=c("black","black", "grey50", "grey50")) +
                                        scale_shape_manual(values=c(19,1, 19, 1)) +
                                        theme(panel.grid.major = element_blank(), 
                                              panel.grid.minor = element_blank())+ 
                                        scale_x_continuous(name ="log10_Length; in mm") +
                                        scale_y_continuous(name ="log10_MO2; RR in umol L-1 hr-1)") +
                                        theme_classic() +
                                        theme(legend.position="none",
                                              element_line(linewidth = 0.5, 
                                                           color = 'black'),
                                              axis.title.y=element_text(size=12),
                                              axis.text.x=element_text(size=(15)),
                                              axis.text.y=element_text(size=(15))) + # legend.position="none",
                                        ggtitle("Metabolic scaling: log10_MO2 = log10_a + 
                                                (b.factor * log10_Length)") +
                                        geom_smooth(aes(group=Food_OA, 
                                                        linetype=Fed_Unfed),
                                                    method = lm, 
                                                    #color = c("black","black", "grey50", "grey50"), 
                                                    #linetype = c("solid","dashed", "solid", "dashed"),
                                                    se=F) +
                                        scale_linetype_discrete(name="Food x pCO2", 
                                                    breaks=c("500 μatm_High food", 
                                                             "500 μatm_Low food", 
                                                             "800 μatm_High food", 
                                                             "800 μatm_Low food"), 
                                                    labels = c("high food x low pCO2", 
                                                               "low food x low pCO2", 
                                                               "high food x high pCO2",
                                                               "high food x high pCO2")) +
                                        ggpmisc::stat_poly_eq(parse=T, 
                                                              aes(label = paste(..eq.label..,
                                                                                ..rr.label.., sep = "~~~")),
                                                              label.x.npc = "left")

pdf(paste0(filename = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/metabolic_scaling/MetabolicScaling_bFactor_Length_ALL2.pdf"), width = 10, height = 5)
print(ggarrange(MO2_b.factorLENGTH_PLOT, 
                MO2_b.factorLENGTH_PLOT_facetted_ALL,
                nrow = 1, ncol = 2)) 
dev.off()
# b factor == 1.46

```

# In summunary from the b factors above...

- listed below all combinations (the single outlier omitted)
  * b factor ALL = 2
  
  * b factor low food  = 2.86 # very different
  * b factor high food = 1.76
  
  * b factor low pCO2  = 1.96 # very similar
  * b factor high pCO2 = 2.12
  
  * b factor lowpCO2  x high food = 1.76 # similar based on food NOT pCO2
  * b factor highpCO2 x high food = 1.82
  * b factor lowpCO2  x low food  = 2.72 
  * b factor highpCO2 x low food  = 3.03
 

- move forward with the following: 

  * b factor 'all'
  * b factor 'foodsupply' as high food & low food


## Using SMA Linear Regression Models! 

* SMA is the slope of standardized major axis regression 
* this method is common when your variance in X is similar to the varaince in Y and tends to be the OLS slope div. by the corr. coeff.
* in summary, the slope is always steeper for SMA relative to OLS, however the stronger the corr. coef. the similar these regressions are
```{r b factor SHELL LENGTH outlier omitted, echo=TRUE, echo = FALSE,message = FALSE, warning = FALSE, results='hide'}

# install.packages('smatr') # if you havent installed yet!
library(smatr) # load the SMA regression package

Resp.Master_bfactor_plottingOM # already run in the OLS chunk above!  

summary(lm(log10_VO2 ~ log10_Length, 
           data = (Resp.Master_bfactor_plotting %>% 
                                               dplyr::filter(Food_OA %in% '800 μatm_High food'))))

obj <- (sma(log10_VO2 ~ log10_Length, 
            data = (Resp.Master_bfactor_plotting %>% 
                                                dplyr::filter(Food_OA %in% '800 μatm_High food'))))

obj <- (sma(log10_VO2 ~ log10_Length, 
            data = (Resp.Master_bfactor_plotting)))
obj_slope <- obj$groupsummary$Slope
obj_int <- obj$groupsummary$Int
eq <- paste('y = ', obj_slope,'x + ',obj_int, sep = '')


MO2_b.factorLENGTH_PLOT_SMA <- Resp.Master_bfactor_plotting %>% 
                           ggplot(aes(x=log10_Length, y=log10_VO2)) +
                              geom_point(size=2) +
                              theme(panel.grid.major = element_blank(), 
                                    panel.grid.minor = element_blank())+ 
                              scale_x_continuous(name ="log10_Length; in mm") +
                              scale_y_continuous(name ="log10_MO2; RR in umol L-1 hr-1)") +
                              theme_classic() +
                              theme(legend.position="none",
                                              element_line(linewidth = 0.5, 
                                                           color = 'black'),
                                              axis.title.y=element_text(size=12),
                                              axis.text.x=element_text(size=(15)),
                                              axis.text.y=element_text(size=(15))) + # legend.position="none",
                              ggtitle("Metabolic scaling: log10_MO2 = log10_a + 
                                      (b.factor * log10_Length)") +
                              geom_abline(aes(slope=obj_slope, intercept=obj_int)) +
                              ggpmisc::stat_poly_eq(parse=T, 
                                                     aes(label = paste(eq, obj$groupsummary$r2, sep = "~~~")),
                                                     label.x.npc = "left")
                              
                              
MO2_b.factorLENGTH_PLOT_facetted <- Resp.Master_bfactor_plotting %>% 
                                     ggplot(aes(x=log10_Length, y=log10_VO2, color = pCO2)) +
                                        geom_point() +
                                        scale_color_manual(values=c("blue","orange")) +
                                        theme(panel.grid.major = element_blank(), 
                                              panel.grid.minor = element_blank())+ 
                                        scale_x_continuous(name ="log10_Length; in mm") +
                                        scale_y_continuous(name ="log10_MO2; RR in umol L-1 hr-1)") +
                                        theme_classic() +
                                        theme(legend.position="none",axis.title.y=element_text(size=7)) +
                                        ggtitle("Metabolic scaling: log10_MO2 = log10_a + 
                                                (b.factor * log10_Length)") +
                                        geom_smooth(method = lm, color = 'red') +
                                        ggpmisc::stat_poly_eq(parse=T, 
                                                              aes(label = paste(..eq.label..,
                                                                                ..rr.label.., sep = "~~~")),
                                                              label.x.npc = "left") +
                                        facet_wrap(~Food_OA)
MO2_b.factorLENGTH_PLOT_facetted_food <- Resp.Master_bfactor_plotting %>% 
                                     ggplot(aes(x=log10_Length, y=log10_VO2)) + # omitted , color = pCO2
                                        geom_point() +
                                        #scale_color_manual(values=c("blue","orange")) +
                                        theme(panel.grid.major = element_blank(), 
                                              panel.grid.minor = element_blank())+ 
                                        scale_x_continuous(name ="log10_Length; in mm") +
                                        scale_y_continuous(name ="log10_MO2; RR in umol L-1 hr-1)") +
                                        theme_classic() +
                                        theme(legend.position="none",axis.title.y=element_text(size=7)) +
                                        ggtitle("Metabolic scaling: log10_MO2 = log10_a + 
                                                (b.factor * log10_Length)") +
                                        geom_smooth(method = lm, color = 'red') +
                                        ggpmisc::stat_poly_eq(parse=T, 
                                                              aes(label = paste(..eq.label..,
                                                                                ..rr.label.., sep = "~~~")),
                                                              label.x.npc = "left") +
                                        facet_wrap(~Fed_Unfed)
MO2_b.factorLENGTH_PLOT_facetted_pCO2 <- Resp.Master_bfactor_plotting %>% 
                                     ggplot(aes(x=log10_Length, y=log10_VO2)) +
                                        geom_point() +
                                        #scale_color_manual(values=c("blue","orange")) +
                                        theme(panel.grid.major = element_blank(), 
                                              panel.grid.minor = element_blank())+ 
                                        scale_x_continuous(name ="log10_Length; in mm") +
                                        scale_y_continuous(name ="log10_MO2; RR in umol L-1 hr-1)") +
                                        theme_classic() +
                                        theme(legend.position="none",axis.title.y=element_text(size=7)) +
                                        ggtitle("Metabolic scaling: log10_MO2 = log10_a + 
                                                (b.factor * log10_Length)") +
                                        geom_smooth(method = lm, color = 'red') +
                                        ggpmisc::stat_poly_eq(parse=T, 
                                                              aes(label = paste(..eq.label..,
                                                                                ..rr.label.., sep = "~~~")),
                                                              label.x.npc = "left") +
                                        facet_wrap(~pCO2)


 # OUTPUT PLOTS 
pdf(paste0(filename = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/metabolic_scaling/MetabolicScaling_bFactor_Length_ALL.pdf"), width = 8, height = 25)
print(ggarrange(MO2_b.factorLENGTH_PLOT, 
                MO2_b.factorLENGTH_PLOT_facetted, 
                MO2_b.factorLENGTH_PLOT_facetted_pCO2,
                MO2_b.factorLENGTH_PLOT_facetted_food,
                nrow = 4, ncol = 1)) # print the model diagnostics
dev.off()



MO2_b.factorLENGTH_PLOT_facetted_ALL <- Resp.Master_bfactor_plotting %>% 
                                     ggplot(aes(x=log10_Length, 
                                                y=log10_VO2, 
                                                color = Food_OA,
                                                shape = Food_OA)) +
                                        geom_point(size = 2) +
                                        #scale_color_manual(values=c("blue","orange")) +
                                        scale_color_manual(values=c("black","black", "grey50", "grey50")) +
                                        scale_shape_manual(values=c(19,1, 19, 1)) +
                                        theme(panel.grid.major = element_blank(), 
                                              panel.grid.minor = element_blank())+ 
                                        scale_x_continuous(name ="log10_Length; in mm") +
                                        scale_y_continuous(name ="log10_MO2; RR in umol L-1 hr-1)") +
                                        theme_classic() +
                                        theme(legend.position="none",
                                              element_line(linewidth = 0.5, 
                                                           color = 'black'),
                                              axis.title.y=element_text(size=12),
                                              axis.text.x=element_text(size=(15)),
                                              axis.text.y=element_text(size=(15))) + # legend.position="none",
                                        ggtitle("Metabolic scaling: log10_MO2 = log10_a + 
                                                (b.factor * log10_Length)") +
                                        geom_smooth(aes(group=Food_OA, 
                                                        linetype=Fed_Unfed),
                                                    method = lm, 
                                                    #color = c("black","black", "grey50", "grey50"), 
                                                    #linetype = c("solid","dashed", "solid", "dashed"),
                                                    se=F) +
                                        scale_linetype_discrete(name="Food x pCO2", 
                                                    breaks=c("500 μatm_High food", 
                                                             "500 μatm_Low food", 
                                                             "800 μatm_High food", 
                                                             "800 μatm_Low food"), 
                                                    labels = c("high food x low pCO2", 
                                                               "low food x low pCO2", 
                                                               "high food x high pCO2",
                                                               "high food x high pCO2")) +
                                        ggpmisc::stat_poly_eq(parse=T, 
                                                              aes(label = paste(..eq.label..,
                                                                                ..rr.label.., sep = "~~~")),
                                                              label.x.npc = "left")

pdf(paste0(filename = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/metabolic_scaling/MetabolicScaling_bFactor_Length_ALL2.pdf"), width = 10, height = 5)
print(ggarrange(MO2_b.factorLENGTH_PLOT, 
                MO2_b.factorLENGTH_PLOT_facetted_ALL,
                nrow = 1, ncol = 2)) 
dev.off()
# b factor == 1.46


```


```{r Calculate Resp Rates , echo=TRUE, message = FALSE, warning = FALSE}

# NORMALIZED for Shell length
# as (RR) * ([mean_length / individual length]^b_factor)
bLength_all      = 2 #  the scaling exponent that we found for all our cumulative F1 data- also a similar b factor for SMO and length found in literature  (2.199)

meanLengthALL    <-mean(Resp.Master_OM$Length_mm) #4.161787 - the mean for the normalization 

Resp.Masterfinal <- Resp.Master_OM %>% 
                       # the 'all' b factor 
                       dplyr::mutate(resp_umol_hr_bFactorNormLength = 
                                    (resp_umol_L_hr)*
                                    ((meanLengthALL/Length_mm)^bLength_all) ) %>% 
                      #   the non-bfactor correction simply dividing by individual shell length
                       dplyr::mutate(resp_µmol_L_mm_Length_hr = 
                                       (resp_umol_L_hr /(Length_um/1000)) ) %>% 
                       dplyr::select(c(Date,
                                      Age,
                                      pH,
                                      pCO2,
                                      Fed_Unfed,
                                      Replicate,
                                      Chamber_tank,
                                      Number,
                                      Run,
                                      Channel,
                                      Length_um,
                                      Length_mm,
                                      # Dry_Shell_weight,
                                      # Dry_Tissue_weight,
                                      # whole_Dry_weight,
                                      volume,
                                      Biovol_length3,
                                      calculated_volume, # as vessel volume - (biovol calc from length^3)
                                      Lpc,
                                      BLANK.mean_Lpc,
                                      resp_blankStand,
                                      resp_mg_L_hr, 
                                      resp_umol_L_hr,
                                      resp_µmol_L_mm_Length_hr,
                                      resp_umol_hr_bFactorNormLength)) %>% 
                      dplyr::rename(raw_resp_rate = Lpc)

# write.csv(Resp.Master_OM, "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/Calculated_Resp_Master.csv")
 write.csv(Resp.Masterfinal, "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/Calculated_Resp_Master.csv")

 
View(Resp.Masterfinal)
```



### Plot the RAW rates by the size metrics 

####  (1) Shell length vs. Raw respiration rate (umol O2 L- hr-1)...
``` {r Shell length vs. raw respiration rate, echo=TRUE, message = FALSE, warning = FALSE}

# by Length ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

P_Length_resp_all <- Resp.Masterfinal%>% 
                        ggplot(aes(
                          x = Length_mm, 
                          y = resp_umol_L_hr, 
                          color = as.factor(pCO2))) +
                         scale_color_manual(values=c("forestgreen","darkorange2"))+
                          geom_smooth(method = "lm", 
                                      se=FALSE, 
                                      color="black", 
                                      formula = resp_umol_L_hr ~ Length_mm) +
                          theme_classic() +
                          theme(panel.grid.major = element_blank(), 
                                panel.grid.minor = element_blank(), 
                                plot.title = element_text(size=10))+ 
                          labs(title = "Raw Resp v. Shell length (mm)", 
                               y = expression(μmol~O[2]%.%hr^{-1})) +
                          xlab("Shell length (mm)") +
                          theme(legend.position="none") +
                          geom_point()

P_Length_resp_facet <- Resp.Masterfinal %>% 
                        ggplot(aes(x = Length_mm, 
                                   y = resp_umol_L_hr, 
                                   color = as.factor(pCO2))) +
                         scale_color_manual(values=c("forestgreen",
                                                     "darkorange2"))+
                          geom_smooth(method = "lm", 
                                      se=FALSE, 
                                      color="black", 
                                      formula = resp_umol_L_hr ~ Length_mm) +
                          theme_classic() +
                           theme(panel.grid.major = element_blank(), 
                                 panel.grid.minor = element_blank(), 
                                 legend.position = "none", 
                                 plot.title = element_text(size=10))+ 
                          labs(y = expression(μmol~O[2]%.%hr^{-1})) +
                          xlab("Shell length (mm)") +
                          geom_point() + 
                          facet_wrap(~Age*Fed_Unfed, scales = "free")
# print in markdown file 
ggarrange(P_Length_resp_all, P_Length_resp_facet, nrow = 2)



# by b factor length all  == 2.0 :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

P_bfactorLength_all <- Resp.Masterfinal %>% 
                        ggplot(aes(
                          x = Length_mm, 
                          y = resp_umol_hr_bFactorNormLength, 
                          color = as.factor(pCO2))) +
                         scale_color_manual(values=c("forestgreen","darkorange2"))+
                          geom_smooth(method = "lm", 
                                      se=FALSE, 
                                      color="black", 
                                      formula = resp_umol_hr_bFactorNormLength ~ Length_mm) +
                          theme_classic() +
                          theme(panel.grid.major = element_blank(), 
                                panel.grid.minor = element_blank(), 
                                plot.title = element_text(size=10))+ 
                          labs(title = "Resp bfactor 2.18 v. Shell length (mm)", 
                               y = expression(b~factor~μmol~O[2]%.%hr^{-1})) +
                          xlab("Shell length (mm)") +
                          theme(legend.position="none") +
                          geom_point()

P_bfactorLength_all_facet <- Resp.Masterfinal %>% 
                        ggplot(aes(x = Length_mm, 
                                   y = resp_umol_hr_bFactorNormLength, 
                                   color = as.factor(pCO2))) +
                         scale_color_manual(values=c("forestgreen",
                                                     "darkorange2"))+
                          geom_smooth(method = "lm", 
                                      se=FALSE, 
                                      color="black", 
                                      formula = resp_umol_hr_bFactorNormLength ~ Length_mm) +
                          theme_classic() +
                           theme(panel.grid.major = element_blank(), 
                                 panel.grid.minor = element_blank(), 
                                 legend.position = "none", 
                                 plot.title = element_text(size=10))+ 
                          labs(y = expression(b~factor~μmol~O[2]%.%hr^{-1})) +
                          xlab("Shell length (mm)") +
                          geom_point() + 
                          facet_wrap(~Age*Fed_Unfed, scales = "free")
# print in markdown file 
ggarrange(P_bfactorLength_all, P_bfactorLength_all_facet,nrow = 2)





# Export to pdf

# raw vs. shell length
pdf(paste0(filename = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/Shell_length_resp_raw.pdf"), width = 10, height = 6)
ggarrange(P_Length_resp_all, P_Length_resp_facet,ncol = 2)
dev.off()


# b factor corrected (ALL) vs. shell length
pdf(paste0(filename = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/Shell_length_resp_bfactorALL.pdf"), width = 10, height = 6)
ggarrange(P_bfactorLength_all, P_bfactorLength_all_facet,ncol = 2)
dev.off()



```







