---
  title: "Respiration Analysis F1 Scallops 2021"
author: "Samuel Gurr"
date: "10/6/2021"
output:
  html_document:
  df_print: paged
pdf_document:
  latex_engine: xelatex
---
  
  
```{r setup, include=FALSE}

# LOAD PACKAGES :::::::::::::::::::::::::::::::::::::::::::::::::::::::

library(dplyr)
library(ggplot2)
library(forcats)
library(lme4)
library(lmerTest)
library(see)
library(performance)
library(car)
library(kableExtra)
library(pander)
library(data.table)
library(stringr)
library(latex2exp)
library(Rmisc)
# library(devtools)
library(ggpubr)
library(hrbrthemes)
library(nlme)
# SET WORKING DIRECTORY :::::::::::::::::::::::::::::::::::::::::::::::

setwd("C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis") # personal computer

# Resp.Master_OM    <- read.csv(file="C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/Calculated_Resp_Master.csv", header=T) # personnel computer 
Resp.Master_OM  <- read.csv(file="C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/Calculated_Resp_Master.csv", header=T, fileEncoding = "latin1") # work computer

```



# Analysis 



### 9/14/2021 F1 juvenile scallops

**About**
  - two pCO2 treatments 
- **before** we culled and started the food limitation trials


##### number of replicates for analysis...

```{r 9/14 replicates and mean resp, echo=FALSE}

# model effect of treatment on resp rate 20210507
Resp_0914 <- Resp.Master_OM %>% 
  dplyr::filter(Date %in% '9/14/2021')  %>% # call only 9/14
  dplyr::filter(!Chamber_tank  %in% 'blank')

Resp_0914 %>% dplyr::group_by(Chamber_tank) %>% dplyr::summarise(n()) # tank replication
# 7.5_A	3			
# 7.5_B	3			
# 7.5_C	3			
# 7.5_D	3			
# 8_A	2	   *2 rep			
# 8_B	3			
# 8_C	3			
# 8_D	2	   *2 rep

Resp_0914 %>% summarySE(measurevar="resp_µmol_L_mm_Length_hr", groupvars=c("pH")) %>% 
  dplyr::mutate(pCO2 = case_when(pH == 8  ~ "500 μatm", pH == 7.5 ~ "800 μatm"))


```

### 9/14/2021 linear model, diagnostics, and plots

#### Length standardized

```{r 9/14 Length standardized, echo=TRUE, message = FALSE, warning = FALSE}

# Shell length standardized (SL) ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
Resp_0914 %>% summarySE(measurevar="resp_µmol_L_mm_Length_hr", groupvars=("pH")) %>% 
  dplyr::mutate(pCO2 = case_when(pH == 8  ~ "500 μatm", pH == 7.5 ~ "800 μatm"))

# plot the replicates (visual diagnostics of random factor)
Resp914_Length_reps<- ggboxplot(Resp_0914, 
                                x = "pH", 
                                y = "resp_µmol_L_mm_Length_hr", 
                                color = "Replicate",
                                add = c("mean_se", "dotplot"),
                                palette = c("#00AFBB", "#E7B800", "brown", "grey"))
Resp914_Length_reps

# One-way ANOVA (without the random effect) 
Resp914_ANOVA <- aov(resp_µmol_L_mm_Length_hr ~ 
                       pCO2, 
                     data=Resp_0914) # run mod
summary(Resp914_ANOVA) # summary mod
kable(data.frame(unclass(summary(Resp914_ANOVA)), check.names = FALSE, stringsAsFactors = FALSE)  ) %>%  # print a png of this table
  kable_styling() %>%
  save_kable(file = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/20210914_figs_tables/20210914_resp_OneWayANOVA_Table.png", zoom = 1.5)
#             Df   Sum Sq   Mean Sq F value Pr(>F)
# pCO2         1 0.000027 0.0000267   0.061  0.807
# Residuals   19 0.008241 0.0004337   
shapiro.test(residuals(Resp914_ANOVA)) # normal - 0.7462
leveneTest(Resp914_ANOVA) # homogeneity of variance (equal variance - 0.7901


# Linear mixed effects model with random effect of Replicate 
LMEmod_0914_SL <- lmer(resp_µmol_L_mm_Length_hr ~ pCO2 + (1|Chamber_tank), data=Resp_0914, REML = FALSE) # lme4 (can run leenes test with this package output), TRUE when NOT addressing AIC for model selection

LMEmod_0914_SL<-lme(resp_µmol_L_mm_Length_hr ~ 
                      pCO2, 
                    random=~1|Chamber_tank, 
                    data=Resp_0914) # with the random effect as an LME model
qqnorm(resid(LMEmod_0914_SL))
shapiro.test(resid(LMEmod_0914_SL)) # 0.8512
leveneTest(residuals(LMEmod_0914_SL) ~ Resp_0914$pCO2) # 0.06434 . PASS
pander(anova(LMEmod_0914_SL), style='rmarkdown') # anova table of lmer
# |     &nbsp;      | numDF | denDF | F-value  |  p-value  |
# |:---------------:|:-----:|:-----:|:--------:|:---------:|
# | **(Intercept)** |   1   |  13   |  43.61   | 1.706e-05 |
# |    **pCO2**     |   1   |   6   | 0.001242 |   0.973   |
kable(as.data.frame(anova(LMEmod_0914_SL))) %>%  # print a png of this table
  kable_styling() %>%
  save_kable(file = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/20210914_figs_tables/20210914_resp_LME_Table.png", zoom = 1.5)
pdf(paste0(filename = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/20210914_figs_tables/20210914_resp_LME_Diagnostics.pdf"))
dev.off()
# levene's test


# test linear mixed model
library('HLMdiag')
# REML == Residual maximum likelihood (REML)
# technique for estimating variance components in multi-classified data.

#compute a model where the effect of pCO2 is estimated
fm1 <- lme4::lmer(resp_µmol_L_mm_Length_hr ~ 
                    pCO2 + 
                    (1 | Chamber_tank), 
                  data=Resp_0914, 
                  REML = FALSE)#because we want to compare models on likelihood; you cannot compare models that differ in fixed effects if they are fitted by REML thus FALSE
#next, compute a model where the effect of status is not estimated
fm2 <- lme4::lmer(resp_µmol_L_mm_Length_hr ~ 
                    (1 | Chamber_tank), 
                  data=Resp_0914, 
                  REML = FALSE)#because we want to compare models on likelihood; you cannot compare models that differ in fixed effects if they are fitted by REML thus FALSE
#compute the AIC-corrected log-base-2 likelihood ratio (a.k.a. "bits" of evidence)
(AIC(fm2)-AIC(fm1))*log2(exp(1)) # -2.880164
(AIC(fm2)-AIC(fm1)) # -1.996378
# simple anova on the unrestricted 
anova(lmer(resp_µmol_L_mm_Length_hr ~ 
             pCO2 + 
             (1 | Chamber_tank), 
           data=Resp_0914, 
           REML = T)) #  0.9533


fm1_resid <- hlm_resid(fm1)
resid1_fm1<- hlm_resid(fm1, standardize = TRUE, include.ls = FALSE)


ggplot(data = resid1_fm1, 
       aes(x = resp_µmol_L_mm_Length_hr, y = .std.resid)) + 
  geom_point(alpha = 0.2) +
  geom_smooth(method = "loess", se = FALSE) + 
  labs(y = "LS level-1 residuals", 
       title = "LS residuals against standardized LRT score")
# look for linear realtionship 
fm1b <- update(fm1, .~. + I(resp_µmol_L_mm_Length_hr^2) 
               + I(resp_µmol_L_mm_Length_hr^3))
resid1_fm1b <- hlm_resid(fm1b, level = 1, standardize = TRUE)
ggplot(data = resid1_fm1b, 
       aes(x = resp_µmol_L_mm_Length_hr, y = .std.resid)) + 
  geom_point(alpha = 0.2) +
  geom_smooth(method = "loess", se = FALSE) + 
  labs(y = "LS level-1 residuals", 
       title = "LS residuals against standardized LRT score")

# random effect
resid2_fm1b <- hlm_resid(fm1, level = "Chamber_tank", include.ls = FALSE)
ggplot(data = resid2_fm1b, aes(x = Chamber_tank, y = .ranef.intercept)) + 
  geom_point() +
  labs(y = "Random effects - intercept", 
       title = "Intercept random effects against Chamber_tank") + 
  coord_flip()


fm1     <- lme4::lmer(resp_µmol_L_mm_Length_hr ~ pCO2 
                      + (1 | Chamber_tank), data=Resp_0914, REML = FALSE)
shapiro.test(resid(fm1)) # 0.9627
shapiro.test(pull_resid(fm1, level = "Chamber_tank")) # 0.2039
shapiro.test(pull_resid(fm1, level = "pCO2")) # 0.2039
qqnorm(resid(fm1))
qqnorm(pull_resid(fm1, level = "pCO2"))



fm1.aug <- hlm_augment(fm1)
shapiro.test(fm1.aug$.ls.resid)# 0.2039
qqnorm(fm1.aug$.ls.resid)
tibble::glimpse(fm1.aug)

fm1_resid  <- hlm_resid(fm1)
shapiro.test(fm1_resid$.resid) #0.9627
qqnorm(fm1_resid$.resid)

fm1_resid2 <- hlm_resid(fm1, standardize = TRUE, include.ls = FALSE)
shapiro.test(fm1_resid2$.std.resid) # 0.9627
shapiro.test(fm1_resid2$.chol.mar.resid) # 0.9221
qqnorm(fm1_resid2$.std.resid)


fm1_resid
qqnorm(fm1_resid$.resid)
shapiro.test(fm1_resid$.resid)

mdffits(fm1)
pull_resid(fm1)



# call the results of LMER to add to boxplot below 
DF   <- paste( (anova(LMEmod_0914_SL)[[1]])[2], (anova(LMEmod_0914_SL)[[2]])[2], sep = '/') # call DF
Fval <- (anova(LMEmod_0914_SL)[[3]])[2] # call f
pval <- (anova(LMEmod_0914_SL)[[4]])[2] # call p value

# plot
Resp914_Length <- ggplot(Resp_0914, aes(x = factor(pCO2, level = c('500 μatm', '800 μatm')), resp_µmol_L_mm_Length_hr , fill = pCO2)) +
  theme(panel.grid=element_blank()) +
  geom_boxplot(size=0.2, width=0.5, alpha=0.1, aes(fill=pCO2)) +
  scale_fill_manual(values=c("white","grey50")) +
  geom_point(shape = 21, size = 2, position = position_jitterdodge(jitter.width = 0.1)) +
  theme_classic() +
  scale_x_discrete(labels= c('~500 μatm', '~800 μatm')) +
  # scale_y_continuous(expand = c(0, 0), limits = c(0, 2)) +
  labs(title = "F1 Scallops: respiration rates on 20210914 (shell length stand.)", 
       y = expression(Respiration~rate~"("~μmol~L^{-1}~O[2]%.%mm~shell~length^{-1}%.% hr^{-1}~")"),
       x = expression(italic(p)*CO[2]~Treatment~"("~μ*atm~")")) + 
  theme(axis.text=element_text(size=8),
        axis.title=element_text(size=8,face="bold")) +
  stat_summary(fun.y=mean, geom="point", shape=18, size=4, color="black", fill="white") # +
# annotate("text", x=2, y=0.000005, size = 4, label = "shapiro wilk = 0.3347") +
# annotate("text", x=2, y=0.0000075, size = 4, label = "levene's = ???") +
# annotate("text", x=2, y=0.0000115, size = 4, label= paste('DF =',DF,'F =', signif(Fval, digits=3), 'p value =', signif(pval, digits=3), sep=" ")) 
Resp914_Length # print this figure...


# Export the figures to pdf
ggarrange(Resp914_Length,Resp914_Length_reps,nrow = 2) %>%
  ggexport(filename = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/20210914_figs_tables/20210914_respiration_length.pdf")

```


# 9/30/2021 F1 juvenile scallops

**About**
  
  - two pCO2 treatments 

- *before* we culled and started the food limitation trials


#### number of replicates for analysis...

```{r 9/30 replicates, echo=FALSE}

Resp_0930 <- Resp.Master_OM %>% 
  dplyr::filter(Date %in% '9/30/2021')  %>% # call only 9/14
  dplyr::select(-Center) %>% 
  dplyr::mutate(pHxFood = paste(pH,Food, sep = "_")) %>% 
  dplyr::mutate(random_fact = as.factor(paste(Chamber_tank, Food, sep="_")))

kable(Resp_0930 %>% dplyr::group_by(Chamber_tank, Food) %>% dplyr::summarise(n())) # tank replication - lowest value was 2 for 7.5_D unfed

Resp_0930 %>% summarySE(measurevar="resp_µmol_L_mm_Length_hr", groupvars=(c("pH", "Food"))) %>% 
  dplyr::mutate(pCO2 = case_when(pH == 8  ~ "500 μatm", pH == 7.5 ~ "800 μatm"))
```


## 9/30/2021 linear model, diagnostics, and plots

#### Length standardized

```{r 9/30 Length standardized, echo=TRUE, message = FALSE, warning = FALSE}


# Shell length standardized (SL) ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

# Visualize the data with the random effet as treplicate 
Resp930_Length_reps <- ggboxplot(Resp_0930, x = "pHxFood", y = "resp_µmol_L_mm_Length_hr", color = "Replicate",
                                 add = c("mean_se", "dotplot"),
                                 palette = c("#00AFBB", "#E7B800", "brown", "grey"))
Resp930_Length_reps
?lmer
# Linear mixed effects model with random effect of Replicate
LMEmod_0930<-lme(resp_µmol_L_mm_Length_hr ~ 
                   pCO2 * Food, 
                 random=~1|random_fact, 
                 data=Resp_0930)
LMEmod_0930<-lmer(resp_µmol_L_mm_Length_hr ~ 
                   pCO2 * Food +
                  (1|random_fact), data=Resp_0930, REML = TRUE) 
qqnorm(resid(LMEmod_0930))
shapiro.test(residuals(LMEmod_0930)) #  non-normal - 0.005481
leveneTest(residuals(LMEmod_0930) ~ Resp_0930$pCO2*Resp_0930$Food) # 0.3248 PASS
pander(anova(LMEmod_0930), style='rmarkdown')
# |     &nbsp;      | numDF | denDF | F-value | p-value  |
# |:---------------:|:-----:|:-----:|:-------:|:--------:|
# | **(Intercept)** |   1   |  49   |  112.3  | 2.82e-14 |
# |    **pCO2**     |   1   |  12   |  1.487  |  0.2461  |
# |    **Food**     |   1   |  12   |  7.219  | 0.01979  | # significant
# |  **pCO2:Food**  |   1   |  12   | 0.6779  |  0.4264  |

LMEmod_0930_T<-lme(asin(sqrt(resp_µmol_L_mm_Length_hr)) ~ # arsin sqrt transformation
                   pCO2 * Food, 
                 random=~1|random_fact, 
                 data=Resp_0930)

LMEmod_0930_T<-lmer(asin(sqrt(resp_µmol_L_mm_Length_hr)) ~ # arsin sqrt transformation
                   pCO2 * Food +
                  (1|random_fact), data=Resp_0930, REML = TRUE) 

shapiro.test(residuals(LMEmod_0930_T)) #  normal - 0.3287
qqnorm(resid(LMEmod_0930_T))
leveneTest(residuals(LMEmod_0930_T) ~ Resp_0930$pCO2*Resp_0930$Food) # 0.484 PASS
pander(anova(LMEmod_0930_T), style='rmarkdown')
# |     &nbsp;      | numDF | denDF | F-value | p-value |
# |:---------------:|:-----:|:-----:|:-------:|:-------:|
# | **(Intercept)** |   1   |  49   |   337   |    0    |
# |    **pCO2**     |   1   |  12   | 0.9207  | 0.3562  |
# |    **Food**     |   1   |  12   |  7.38   | 0.01872 | # significant - transformation did not change the outcome of the model
# |  **pCO2:Food**  |   1   |  12   |  1.011  | 0.3345  |

kable(as.data.frame(anova(LMEmod_0930_T))) %>% 
  kable_styling() %>%
  save_kable(file = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/20210930_figs_tables/20210930_resp_LME_Table.png", zoom = 1.5)
pdf(paste0(filename = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/20210930_figs_tables/20210930_resp_LME_Diagnostics.pdf"))

dev.off()

ggarrange( QQplot_930 ,QQplot_T_930 )
# food supply diff
Resp_0930 %>% summarySE(measurevar="resp_µmol_L_mm_Length_hr", groupvars="Food")
perc_diff <- (0.04791220 - 0.02785341)/0.04791220*100
perc_diff #41.86573 %



# plot
Resp930_Length <- ggplot(Resp_0930, aes(x = factor(pCO2, level = c('500 μatm', '800 μatm')), resp_µmol_L_mm_Length_hr , fill = pCO2)) +
  theme(panel.grid=element_blank()) +
  geom_boxplot(size=0.2, width=0.5, alpha=0.1, aes(fill=pCO2)) +
  scale_fill_manual(values=c("white","grey50")) +
  geom_point(shape = 21, size = 2, position = position_jitterdodge(jitter.width = 0.1)) +
  theme_classic() +
  scale_x_discrete(labels= c('~500 μatm', '~800 μatm')) +
  #scale_y_continuous(expand = c(0, 0), limits = c(0, 120)) +
  theme(axis.text=element_text(size=8),
        axis.title=element_text(size=8,face="bold")) +
  labs(title = "F1 Scallops: respiration rates on 20210930 (shell length stand.)", 
       y = expression(Respiration~rate~"("~μmol~L^{-1}~O[2]%.%mm~shell~length^{-1}%.% hr^{-1}~")"),
       x = expression(italic(p)*CO[2]~Treatment~"("~μ*atm~")"))  + 
  stat_summary(fun.y=mean, geom="point", shape=18, size=4, color="black", fill="white") +
  facet_wrap(~factor(Fed_Unfed, level = c('Low food', 'High food')))
Resp930_Length

# Export to pdf
ggarrange(Resp930_Length,Resp930_Length_reps,nrow = 2) %>%
  ggexport(filename = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/20210930_figs_tables/20210930_resp_Figures.pdf")

```


# density plot - Day 64

```{r, Day 64 density respiration plot }
library(dplyr)
library(tidyr)
Resp_0930$pHxFood <- as.factor(Resp_0930$pHxFood)

df_mean <- Resp_0930 %>% 
  dplyr::group_by(pHxFood) %>% 
  dplyr::summarize(average = mean(resp_µmol_L_mm_Length_hr)) %>%
  dplyr::ungroup()
p.box <- ggplot(Resp_0930, aes(x = pHxFood, y = resp_µmol_L_mm_Length_hr)) + geom_boxplot() + geom_point(data= df_mean, mapping = aes(x = pHxFood, y = average),
                                                                                                         color="red") 
p.box.data <- layer_data(p.box) %>%
  select(x, ymin, lower, middle, upper, ymax, outliers, flipped_aes) %>%
  dplyr::rename(mean = flipped_aes) %>% 
  dplyr::mutate(mean  = df_mean$average) %>% 
  mutate(pHxFood = factor(x, labels = levels(Resp_0930$pHxFood), ordered = TRUE)) %>%
  select(-x)


p.box.data %>% unnest(outliers)


denisty_box_resp_64DPF <-ggplot(p.box.data) +
  # manually plot flipped boxplot
  geom_segment(aes(x = ymin, xend = ymax, y = -0.15, yend = -0.15)) +
  geom_rect(aes(xmin = lower, xmax = upper, ymin = -0.3, ymax = 0,  fill = pHxFood),color = "black") +
  # geom_point(data = . %>% unnest(outliers), aes(x = outliers, y = -0.15), color = "grey60", size = 1) +
  # vertical lines at Q1 / Q2 / Q3
  geom_vline(data = . %>% select(pHxFood, lower, mean, upper) %>% gather(key, value, -pHxFood), aes(xintercept = value)) +
  # density plot
  geom_density(data = Resp_0930, aes(x = resp_µmol_L_mm_Length_hr, group=pHxFood, fill=pHxFood, ..scaled..), alpha=.4, adjust=1.5) +
  #  theme
  theme_classic() +
  xlim(0, 0.22) +
  facet_grid(pHxFood ~ .) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.position = "none", plot.title = element_text(size=10))+
  labs(title = "F1 Scallops: respiration rates 64 DPF)", 
       x = expression(Respiration~rate~"("~μmol~L^{-1}~O[2]%.%mm^{-1}~shell~length%.% hr^{-1}~")"),
       y = "Scaled density") +
  scale_fill_manual(values=c("grey40", "grey40", "grey85", "grey85"))
denisty_box_resp_64DPF

pdf(paste0(filename = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/20210930_figs_tables/20210930_resp_density_plot.pdf"), width = 5, height = 5)
pdf(paste0(filename = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/20210930_figs_tables/20210930_resp_density_plot.pdf"), width = 5, height = 5)
denisty_box_resp_64DPF # print the model diagnostics 
dev.off()

```

# 10/26/2021 F1 juvenile scallops

**About**
  
  - two pCO2 treatments 

- *before* we culled and started the food limitation trials


#### number of replicates for analysis...

```{r 10/26 replicates, echo=FALSE}

Resp_1026 <- Resp.Master_OM %>% 
  dplyr::filter(Date %in% '10/26/2021')  %>% # call only 10/14
  dplyr::select(-Center) %>% 
  dplyr::mutate(pHxFood = paste(pH,Food, sep = "_")) %>% 
  dplyr::mutate(random_fact = as.factor(paste(Chamber_tank, Food, sep="_")))

kable(Resp_1026 %>% dplyr::group_by(Chamber_tank, Food) %>% dplyr::summarise(n())) # tank replication

Resp_1026 %>% summarySE(measurevar="resp_µmol_L_mm_Length_hr", groupvars=(c("Food","pH"))) %>% 
  dplyr::mutate(pCO2 = case_when(pH == 8  ~ "500 μatm", pH == 7.5 ~ "800 μatm"))
```


### 10/26/2021 Linear mixed-effects models, diagnostics, and plots


#### Length standardized

```{r 10/26 Length standardized, echo=TRUE, message = FALSE, warning = FALSE}

# Shell length standardized (SL) ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

# Visualize the data with the random effet as treplicate 
Res1026_Length_reps <- ggboxplot(Resp_1026, 
                                 x = "pHxFood", 
                                 y = "resp_µmol_L_mm_Length_hr", 
                                 color = "Replicate",
                                 add = c("mean_se", "dotplot"),
                                 palette = c("#00AFBB", 
                                             "#E7B800", 
                                             "brown", 
                                             "grey"))
Res1026_Length_reps

# ANOVA (wihtout the random effect
AOVmod_1026 <-lm(resp_µmol_L_mm_Length_hr ~ pCO2 * Food, data=Resp_1026) # lm
# shapiro wilk normality test
shapiro.test(residuals(AOVmod_1026)) #  normal - 0.9677
# levene's test
leveneTest(residuals(AOVmod_1026) ~ Resp_1026$pCO2*Resp_1026$Food) # 2.08e-06 *** no pass


require(nlme)
# Linear mixed effects model with random effect of Replicate 
LMEmod_1026_SL<-lme(resp_µmol_L_mm_Length_hr 
                    ~ pCO2 * Food, 
                    random=~1|random_fact, 
                    data=Resp_1026)
# shapiro wilk normality test
shapiro.test(residuals(LMEmod_1026_SL)) #  normal - 0.9677
# levene's test
leveneTest(residuals(LMEmod_1026_SL) ~ Resp_1026$pCO2*Resp_1026$Food) # 2.08e-06 *** no pass
pander(anova(LMEmod_1026_SL), style='rmarkdown')
# |     &nbsp;      | numDF | denDF | F-value |  p-value  |
# |:---------------:|:-----:|:-----:|:-------:|:---------:|
# | **(Intercept)** |   1   |  15   |  72.15  | 4.086e-07 |
# |    **pCO2**     |   1   |  12   | 0.2441  |  0.6302   |
# |    **Food**     |   1   |  12   |  23.56  | 0.0003955 | **
# |  **pCO2:Food**  |   1   |  12   | 0.5343  |  0.4788   |

LMEmod_1026_SL_T<-lme(sqrt(resp_µmol_L_mm_Length_hr) ~
                    pCO2 * Food, 
                    random=~1|random_fact, 
                    data=Resp_1026)
qqnorm(resid(LMEmod_1026_SL_T))
# shapiro wilk normality test
shapiro.test(residuals(LMEmod_1026_SL_T)) #  normal - 0.9677
# levene's test
leveneTest(residuals(LMEmod_1026_SL_T) ~ Resp_1026$pCO2*Resp_1026$Food) # 2.08e-06 *** no pass
pander(anova(LMEmod_1026_SL_T), style='rmarkdown')


LMEmod_1026_SL_T <- lmer(log(resp_µmol_L_mm_Length_hr) ~  pCO2 * Food + (1|random_fact), data=Resp_1026, REML = TRUE) # lme4 (can run leenes test with this package output), TRUE when NOT addressing AIC for model selection



kable(as.data.frame(anova(LMEmod_1026_SL))) %>% 
  kable_styling() %>%
  save_kable(file = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/20211026_figs_tables/20211026_resp_LME_Table.png", zoom = 1.5)
pdf(paste0(filename = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/20211026_figs_tables/20211026_resp_LME_Diagnostics.pdf"))
check_model(LMEmod_1026_SL) 
dev.off()



# food supply diff
Resp_1026 %>% summarySE(measurevar="resp_µmol_L_mm_Length_hr", groupvars="Food")
perc_diff <- (0.08566193 - 0.02248406)/0.08566193*100
perc_diff #42.7 %

# call the results of LMER to add to boxplot below 
DF   <- paste( (anova(LMEmod_01026_SL)[[1]])[3], (anova(LMEmod_01026_SL)[[2]])[3], sep = '/') # call DF
Fval <- (anova(LMEmod_01026_SL)[[3]])[3] # call f
pval <- (anova(LMEmod_01026_SL)[[4]])[3] # call p value

# plot
Resp1026_Length <- ggplot(Resp_1026, aes(x = factor(pCO2, level = c('500 μatm', '800 μatm')), resp_µmol_L_mm_Length_hr , fill = pCO2)) +
  theme(panel.grid=element_blank()) +
  geom_boxplot(size=0.2, width=0.5, alpha=0.1, aes(fill=pCO2)) +
  scale_fill_manual(values=c("white","grey50")) +
  geom_point(shape = 21, size = 2, position = position_jitterdodge(jitter.width = 0.1)) +
  theme_classic() +
  scale_x_discrete(labels= c('~500 μatm', '~800 μatm')) +
  # scale_y_continuous(expand = c(0, 0), limits = c(0, 250)) +
  theme(axis.text=element_text(size=8),
        axis.title=element_text(size=8,face="bold")) +
  labs(title = "F1 Scallops: respiration rates on 20211026 (shell length stand.)", 
       y = expression(Respiration~rate~"("~μmol~L^{-1}~O[2]%.%mm^{-1}~shell~length%.% hr^{-1}~")"),
       x = expression(italic(p)*CO[2]~Treatment~"("~μ*atm~")"))  + 
  facet_wrap(~factor(Fed_Unfed, level = c('Low food', 'High food'))) # +
Resp1026_Length # the CH5 Run 1 (10/26 data) appears to be an outlier - this was rerun and inserted in a cluster above - the raw plots data shows that this very rapid rate was delayed, possibly a resp vessel malfunction??


# Export to pdf
ggarrange(Resp1026_Length, Res1026_Length_reps,nrow = 2) %>% 
  ggexport(filename = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/20211026_figs_tables/20211026_resp_Figures.pdf")

```


# density plot - Day 92

```{r, Day 92 density respiration plot }
library(dplyr)
library(tidyr)
Resp_1026$pHxFood <- as.factor(Resp_1026$pHxFood)
Resp_1026$resp_µmol_L_mm_Length_hr.noSCI     <- format(as.numeric(Resp_1026$resp_µmol_L_mm_Length_hr), scientific = FALSE, digits = 3)
Resp_1026$resp_µmol_L_mm_Length_hr.NUM       <- as.numeric(sprintf("%s", Resp_1026$resp_µmol_L_mm_Length_hr.noSCI))

df_mean <- Resp_1026 %>% 
  dplyr::group_by(pHxFood) %>% 
  dplyr::summarize(average = mean(resp_µmol_L_mm_Length_hr.NUM)) %>%
  dplyr::ungroup()
p.box <- ggplot(Resp_1026, aes(x = pHxFood, y = resp_µmol_L_mm_Length_hr.NUM)) + geom_boxplot() + geom_point(data= df_mean, mapping = aes(x = pHxFood, y = average),
                                                                                                             color="red") 
p.box.data <- layer_data(p.box) %>%
  select(x, ymin, lower, middle, upper, ymax, outliers, flipped_aes) %>%
  dplyr::rename(mean = flipped_aes) %>% 
  dplyr::mutate(mean  = df_mean$average) %>% 
  mutate(pHxFood = factor(x, labels = levels(Resp_1026$pHxFood), ordered = TRUE)) %>%
  select(-x)


p.box.data %>% unnest(outliers)


denisty_box_resp_92DPF <-ggplot(p.box.data) +
  # manually plot flipped boxplot
  geom_segment(aes(x = ymin, xend = ymax, y = -0.15, yend = -0.15)) +
  geom_rect(aes(xmin = lower, xmax = upper, ymin = -0.3, ymax = 0,  fill = pHxFood),color = "black") +
  #geom_point(data = . %>% unnest(outliers), aes(x = outliers, y = -0.15), color = "grey60", size = 1) +
  # vertical lines at Q1 / Q2 / Q3
  geom_vline(data = . %>% select(pHxFood, lower, mean, upper) %>% gather(key, value, -pHxFood), aes(xintercept = value)) +
  # density plot
  geom_density(data = Resp_1026, aes(x = resp_µmol_L_mm_Length_hr.NUM, group=pHxFood, fill=pHxFood, ..scaled..), alpha=.4, adjust=1.5) +
  #  theme
  theme_classic() +
  facet_grid(pHxFood ~ .) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.position = "none", plot.title = element_text(size=10))+
  labs(title = "F1 Scallops: respiration rates 92 DPF)", 
       x = expression(Respiration~rate~"("~μmol~L^{-1}~O[2]%.%mm^{-1}~shell~length%.% hr^{-1}~")"),
       y = "Scaled density") +
  scale_fill_manual(values=c("grey40", "grey40", "grey85", "grey85"))
denisty_box_resp_92DPF

pdf(paste0(filename = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/20211026_figs_tables/20211026_resp_density_plot.pdf"), width = 5, height = 5)
denisty_box_resp_92DPF # print the model diagnostics 
dev.off()

```
