---
title: "Respiration Analysis F1 Scallops 2021"
author: "Samuel Gurr"
date: "10/6/2021"
output:
  pdf_document:
    latex_engine: xelatex
---


```{r setup, include=FALSE}

# LOAD PACKAGES :::::::::::::::::::::::::::::::::::::::::::::::::::::::

library(dplyr)
library(ggplot2)
library(forcats)
library(lme4)
library(lmerTest)
library(see)
library(performance)
library(car)
library(kableExtra)
library(pander)
library(data.table)
library(stringr)
library(latex2exp)
library(Rmisc)
library(devtools)
# SET WORKING DIRECTORY :::::::::::::::::::::::::::::::::::::::::::::::

# setwd("C:/Users/samjg/Documents/Github_repositories/Airradians_OA/RAnalysis") # personal computer
# setwd("C:/Users/samuel.gurr/Documents/Github_repositories/Airradians_OA/RAnalysis") # Work computer
 setwd("C:/Users/samjg/Documents/Github_repositories/Airradians_OA/RAnalysis") # Work computer

# LOAD DATA :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

resp.data       <- read.csv(file="Output/Respiration/Cumulative_resp_alpha0.4_15sectrunc1hour.csv", header=T) %>% 
                      dplyr::filter(!Date %in% "9/14/2021" | !Filename %in% 'Run_1_raw.txt') # read the calculate raw rates from 'resp_LoLin' script - contains the calculated rate (not normalized for blanks) for each sensor-channel
exp_metadata    <- read.csv(file="Data/ExperimentMetadata.csv", header=T) # treatment assignments to 'Chamber_Tank'
lengths         <- read.csv(file="Data/Respiration/Lengths_Condition_resp_clearance.csv", header=T)
resp.ref        <- read.csv(file="Data/Respiration/Reference_master.csv", header=T) %>% dplyr::filter(!Date %in% "9/14/2021" | !Filename %in% 'Run_1_raw.txt')
DWs_Len_1026    <- read.csv(file="Data/Survival_Size/20211026_lengths_dryweights.csv", header=T)
DWs_Len_914.930 <- read.csv(file="Data/Survival_Size/2021914_930_dryweights.csv", header=T)

```

# Standardize rates by dry tissue weight 

* NOTE: we have tissue dry weights for the large animals on 1026 (was able to dissect them) whereas we have whole animal dry weights for 914 and 930 
* here we run regressions on the 1026 dats (shell length v. tissue dry weight) to extrapolate tissue weight for smaller shell sizes (914 and 930) 


```{r dry weight and length regs, echo=FALSE}

# Tissue Dry Weight (DW) vs Shell length :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

# filter data
Tissue_DW_1026 <- DWs_Len_1026 %>% dplyr::filter(shell.or.tissue %in% "tissue")

# note: the raw shell length data yields a curved equation - shell length^2 yields a near-linear fit 

Tissue_DW_1026_subset <- Tissue_DW_1026 %>% dplyr::filter(Shell.Length < 10)  # animals < 10 um shelllength
fit                   <- lm(weight ~ (Shell.Length)^2, data = Tissue_DW_1026_subset)

P_DW_v_ShellLen      <- ggplot(data = Tissue_DW_1026_subset, aes(x = (Shell.Length), y = weight)) +
                                geom_smooth(method = "lm", se=FALSE, color="black", formula = weight ~ Shell.Length) +
                                theme_classic() +
                                ylab("Tissue dry weight (mg)") +
                                xlab("Shell length (um)") +
                                # stat_function(fun=my_eq, colour="red") +
                                geom_point() + 
                                xlim(0,15) +
                                geom_smooth(method='lm') # y~0+x if you want it through the origin (0,0)
                           
P_DW_v_ShellLen    


P_DW_v_ShellLen2      <- ggplot(data = Tissue_DW_1026_subset, aes(x = (Shell.Length)^2, y = weight)) +
                                geom_smooth(method = "lm", se=FALSE, color="black", formula = weight ~ Shell.Length) +
                                theme_classic() +
                                ylab("Tissue dry weight (mg)") +
                                xlab("[ Shell length (um) ]^2") +
                                # stat_function(fun=my_eq, colour="red") +
                                geom_point() + 
                                xlim(0,100) +
                                annotate(label = sprintf("y = %.3f x\nR² = %.2f", coef(fit), summary(fit)$r.squared),
                                         geom = "text", x = 80, y = 0.0010, size = 5) +
                                geom_smooth(method='lm') # y~0+x if you want it through the origin (0,0)
                           
P_DW_v_ShellLen2     


DW

# 20210914 ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
WholeScal_DW_914     <- lengths %>% dplyr::filter(Date %in% '9/14/2021')
DWs_Len_914          <- DWs_Len_914.930 %>% dplyr::filter(Date %in% '20210914') %>% dplyr::filter(Purpose %in% 'resp_filtration')
Scallop_DW_mg




# 20210930 ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
WholeScal_DW_930     <- lengths %>% dplyr::filter(Date %in% '9/30/2021') %>% dplyr::rename(Rep = Replicate) %>% dplyr::rename(Fed_unfed = Food) %>% dplyr::rename(Treatment = pH)  %>% dplyr::rename(Num = Number)
DWs_Len_930          <- DWs_Len_914.930 %>% dplyr::filter(Date %in% '20210930') %>% dplyr::filter(Purpose %in% 'resp_filtration') 

MasterDWLength_930 <- merge(WholeScal_DW_930, DWs_Len_930, by = c('Treatment','Num','Rep','Plate','Run', 'Fed_unfed'))

ggplot(data = MasterDWLength_930, aes(x = (Length_um)/1000, y = Scallop_DW_mg)) +
                                geom_smooth(method = "loess", se=FALSE, color="black", formula = Scallop_DW_mg ~ Length_um) +
                                geom_point() + 
                                theme_classic() +
                                ylab("Whole animal dry weight (mg)") +
                                xlab("Shell length (mm)") +
                                # stat_function(fun=my_eq, colour="red") +
                                xlim(0,6) +
                                geom_smooth(method='loess') # y~0+x if you want it through the origin (0,0)

ggplot(data = MasterDWLength_930, aes(x = ((Length_um)/1000)^2, y = Scallop_DW_mg)) +
                                geom_smooth(method = "lm", se=FALSE, color="black", formula = Scallop_DW_mg ~ Length_um) +
                                geom_point() + 
                                theme_classic() +
                                ylab("Whole animal dry weight (mg)") +
                                xlab("[Shell length (mm)]^2") +
                                # stat_function(fun=my_eq, colour="red") +
                                xlim(0,35) +
                                geom_smooth(method='lm') # y~0+x if you want it through the origin (0,0)


```



## merge master resp data frame 

```{r merge resp with length data and treatment IDs, echo=FALSE}

# merge the exp_metadata with the resp.data
resp.ref_length_merged                 <- merge(resp.ref, lengths) # all TRUE allows us to keep the blanks
resp.data_merged                       <- merge(resp.data, resp.ref_length_merged) %>% # out master file moving forward....
                                            dplyr::mutate(filetype = str_sub(Filename, -3,-1)) %>% 
                                            dplyr::mutate(filetype = factor(ifelse(filetype == "csv", "SDR_data", "LoLigo_data")))
kable(head(resp.data_merged))

```

## Visual diagnostics of plots to correct poor data 

- View on github: Airradians_OA/RAnalysis/Output/Respiration/plots_alpha0.4_increm15sec/

#### found three calls that inaccurately represent the rates of oxygen consumption 

(1) https://github.com/SamGurr/Airradians_OA/blob/master/RAnalysis/Output/Respiration/plots_alpha0.4_increm15sec/20210930_Plate_2_Run_2_C5_regression.pdf
- solution = call 'Lz' instead of the default Leq

(2) https://github.com/SamGurr/Airradians_OA/blob/master/RAnalysis/Output/Respiration/plots_alpha0.4_increm15sec/20210930_Plate_2_Run_1_C1_regression.pdf
- solution = call 'Lz' instead of the default Leq

(3) https://github.com/SamGurr/Airradians_OA/blob/master/RAnalysis/Output/Respiration/plots_alpha0.4_increm15sec/20210930_Plate_1_Run_2_C1_regression.pdf
- solution = we reran this at the end of the LoLin script  for 0-20 minutes and got an Lpc  -0.0296, insert this 

```{r IMPORTANT correct poor data, echo=TRUE}
resp.data_merged[94,c(1:6)]  # 	C1 RR_9.30.21_AM_Plate_2_Run_1.csv # -0.02890813	-0.0608251	-0.0608251 - Lz and Leq call better regression than Lpc
resp.data_merged[110,c(1:6)] #  C5 RR_9.30.21_PM_Plate_2_Run_2.csv	0.029052351	-0.076034441	-0.076034441
resp.data_merged[95,c(1:6)]  # 	C1 RR_9.30.21_PM_Plate_1_Run_2.csv	0.011656487	0.011656487	0.011656487  - ommit this

resp.data_merged[94,4] <- resp.data_merged[94,5] # 20210930_Plate_2_Run_2_C5_regression - Lz and Leq call better regression than Lpc
resp.data_merged[110,4] <- resp.data_merged[110,5] # 20210930_Plate_2_Run_1_C1_regression - Lz and Leq call better regression than Lpc
resp.data_merged[95,4] <- -0.0296 # 20210930_Plate_1_Run_2_C1_regression - plot shows noise after the 20 minutes mark, we reran this at the end of the LoLin script, insert here!

resp.data_merged[94,c(1:6)]
resp.data_merged[110,c(1:6)]
resp.data_merged[95,c(1:6)]
```

# Calculate blanks, print all and means

```{r call blanks, echo=FALSE}

blanks_total <- data.frame() # start dataframe 
blanks.table <- data.frame(matrix(nrow = 1,ncol = 5)) # make a table template
colnames(blanks.table)<-c('Date', 'Channel', 'mean_Lpc', 'mean_Leq' , 'mean_Lz') # names for comuns in the for loop

blanks_all_raw <- data.frame(merge(resp.ref, resp.data, by = c('Date', 'Channel', 'Filename')) %>% 
                  dplyr::mutate(filetype = str_sub(Filename, -3,-1)) %>% 
                  dplyr::mutate(filetype = factor(ifelse(filetype == "csv", "SDR_data", "LoLigo_data"))) %>% 
                  dplyr::filter(Chamber_tank  == 'blank') %>% 
                  dplyr::filter(Lpc <0) %>% 
                  dplyr::filter(!Date == '9/30/2021' | !Lpc < -0.035) %>% #omits C6 RR_9.30.21_AM_Plate_1_Run_1.csv	8.0	blank - View the Lolin plot, looks noisy and a fast outlier from the others
                  dplyr::filter(!Date == '10/26/2021'  | !Channel == "CH8" | !Run == "2" )) # omit a bad blank that contained a bad seal, noted on the respiration sampling day during the trial 
kable((blanks_all_raw)[,c(1:3,6,8,12:14)])

blanks_means <- blanks_all_raw %>% 
     dplyr::group_by(Date, pH, filetype) %>% 
     dplyr::filter(Chamber_tank == "blank") %>% 
     dplyr::filter(Lpc <0) %>% # ommit blank calls that d/n represent oxygen consumption
     dplyr::summarise(BLANK.mean_Lpc = mean(abs(Lpc)),
                      BLANK.sd.Lpc   = sd(abs(Lpc)),
                      BLANK.mean_Leq = mean(abs(Leq)), 
                      BLANK.mean_Lz = mean(abs(Lz)),
                      n = n())
kable(blanks_means)


```

# Blank-standardized rates as 'resp_blankStand'

## Merge blanks with the master file by Date, pCO2 treatment, and filetype

* 'filteype' is only important here on 20211026 when both Loligo and SDR were used due to difference in size for fed (larger) and unfed animals 

```{r merge blanks_means for a master file, echo=FALSE}

Resp.Master <- merge(resp.data_merged, blanks_means, by=c("Date", "pH",  "filetype")) %>% # NOTE: this repeats for every distinct length value
  dplyr::mutate(resp_blankStand = Lpc - BLANK.mean_Lpc) # ommits respiration rate values showing an increase in O2 over time 

```


# Master Resp file, with volumes and file types, etc. as 'Calculated_Resp_Master.csv'

## dplyr::mutate for the following:

* 'volume' of the different vessels throughout the fed*OA challenge
* 'Age'
8 'Fed_unfed'
* 'pCO2'

```{r merge data to master file and write csv, echo=FALSE}

Resp.Master_OM <- Resp.Master %>% dplyr::filter(!resp_blankStand > 0) %>% # ommit respiration values that are positive  
  dplyr::mutate(volume = case_when(filetype == "LoLigo_data" & Date == '9/14/2021' ~ 1.7, # small vessels for loligo system
                                   filetype == "LoLigo_data" & Date == '10/26/2021' & Channel == 'CH1' ~ 68.55323, # larger custom vessels measured individually...
                                   filetype == "LoLigo_data" & Date == '10/26/2021' & Channel == 'CH2' ~ 68.85583, # larger custom vessels measured individually...
                                   filetype == "LoLigo_data" & Date == '10/26/2021' & Channel == 'CH3' ~ 68.87473, # larger custom vessels measured individually...
                                   filetype == "LoLigo_data" & Date == '10/26/2021' & Channel == 'CH4' ~ 68.95481, # larger custom vessels measured individually...
                                   filetype == "LoLigo_data" & Date == '10/26/2021' & Channel == 'CH5' ~ 68.57288, # larger custom vessels measured individually...
                                   filetype == "LoLigo_data" & Date == '10/26/2021' & Channel == 'CH6' ~ 68.01878, # larger custom vessels measured individually...
                                   filetype == "LoLigo_data" & Date == '10/26/2021' & Channel == 'CH7' ~ 68.54551, # larger custom vessels measured individually...
                                   filetype == "LoLigo_data" & Date == '10/26/2021' & Channel == 'CH8' ~ 68.53297, # larger custom vessels measured individually...
                                   filetype == "SDR_data" ~ 2.2)) %>% # 24-well plate 
  
  dplyr::mutate(Age = case_when(Date == '9/14/2021' ~ 50, Date == '9/30/2021' ~ 66, Date == '10/26/2021' ~ 92)) %>% 
  dplyr::mutate(Fed_Unfed = case_when(Fed_Unfed == 'F' ~ "High food", is.na(Fed_Unfed) ~ "High food", Fed_Unfed == 'U' ~ "Low food")) %>% 
  dplyr::mutate(pCO2 = case_when(pH == 8.0 ~ "500 μatm", pH == 7.5 ~ "800 μatm"))
Resp.outliers <- Resp.Master %>% dplyr::filter(resp_blankStand > 0) # call the values with positive resp rates, measing they were slower than the blank!
print(Resp.outliers)

#write.csv(Resp.Master_OM, "C:/Users/samjg/Documents/Github_repositories/Airradians_OA/RAnalysis/Output/Respiration/Calculated_Resp_Master.csv")
write.csv(Resp.Master_OM, "C:/Users/samuel.gurr/Documents/Github_repositories/Airradians_OA/RAnalysis/Output/Respiration/Calculated_Resp_Master.csv")

```



# b factor plots 

## Shell length

All physiological rates were standardized for a _____ um shell length per individual. This length, corresponding to the median shell length of all individuals monitored during this experiment, was chosen to keep standardized rates consistent with  one  length and  minimize error.


### EQ: Ys=(Ws/Wsc)^b(Ye)

* Ys   =  shell length-standardized physiological rate (respiration in this case..) 
* Ws   =  median shell length per individual in this experiment (fed v. unfed betwen 9/14 - 10/26)
* Wsc  =  shell length for each bay scllop 
* b    =  allometric coefficient estimated from the shell length and the physiolgoical process (in this case respiration rate) as Ye = (a)Wsc^b 
* Ye   =  the experimentally measured rate 

```{r b factor, echo=TRUE}

Resp.Master_OM$resp_volStand_mg_L_hr <- ( (abs(Resp.Master_OM$resp_blankStand)) * # call absolute value of resp in mg per minute - convert to ng min-1
                (Resp.Master_OM$volume/1000) ) * 60

Resp.Master_OM$Length_um <- (as.numeric(Resp.Master_OM$Length_um))
Resp.Master_OM$Length_mm <- (Resp.Master_OM$Length_um/1000)

AllLength_lm_eqn <- function(Resp.Master_OM){
                    #m <- lm(resp_volStand_mg_L_hr ~ Length_um, Resp.Master_OM);
                    m <- lm(resp_volStand_mg_L_hr ~ exp(Length_mm), Resp.Master_OM);
                    eq <- substitute(italic(y) == a %.% (x)^b*","~~italic(r)^2~"="~r2, 
                         list(a = format(unname(coef(m)[1]), digits = 2),
                              b = format(unname(coef(m)[2]), digits = 2),
                             r2 = format(summary(m)$r.squared, digits = 3)))
                    as.character(as.expression(eq));
}


Length_pH8  <- Resp.Master_OM %>% dplyr::filter(pH %in% 8)
Length_8_lm_eqn  <- function(Length_pH8){
                    #m <- lm(resp_volStand_mg_L_hr ~ Length_um, Length_pH8);
                    m <- lm(resp_volStand_mg_L_hr ~  exp(Length_um), Length_pH8);
                    eq <- substitute(italic(y) == a %.% (x)^b*","~~italic(r)^2~"="~r2, 
                         list(a = format(unname(coef(m)[1]), digits = 2),
                              b = format(unname(coef(m)[2]), digits = 2),
                             r2 = format(summary(m)$r.squared, digits = 3)))
                    as.character(as.expression(eq));
}
Length_pH7.5  <- Resp.Master_OM %>% dplyr::filter(pH %in% 7.5)
Length_7.5_lm_eqn <- function(Length_pH7.5){
                    #m <- lm(resp_volStand_mg_L_hr ~ Length_um, Length_pH7.5);
                    m <- lm(resp_volStand_mg_L_hr ~  exp(Length_um), Length_pH7.5);
                    eq <- substitute(italic(y) == a %.% (x)^b*","~~italic(r)^2~"="~r2, 
                         list(a = format(unname(coef(m)[1]), digits = 2),
                              b = format(unname(coef(m)[2]), digits = 2),
                             r2 = format(summary(m)$r.squared, digits = 3)))
                    as.character(as.expression(eq));
}

??method.args 



Resp.Master_OM %>% dplyr::filter(pH %in% 8) %>%
ggplot(aes(x =  Length_um, y = resp_volStand_mg_L_hr)) +
            geom_point() +
            geom_smooth(method="glm",
            method.args=list(family= quasibinomial(link = 'logit'))) #+





Resp.Master_OM %>% dplyr::filter(pH %in% 7.5) %>%
ggplot(aes(x =  Length_um, y = resp_volStand_mg_L_hr)) +
            geom_point() +
            geom_smooth(method="glm",
            method.args=list(family= quasibinomial(link = 'logit'))) #+
            # method.args=list(family="binomial"))

            #geom_smooth(method = "loess", se=FALSE, color="black", formula = Length_um ~ resp_volStand_mg_L_hr) +
            geom_point(aes(colour = as.factor(pH)), size=3) +
            scale_color_manual(values=c("#E69F00", "#56B4E9")) +
            theme_classic() +
            geom_text(x = 4000, y = .06, label = AllLength_lm_eqn(Resp.Master_OM), parse = TRUE) +
            geom_text(x = 4000, y = .05, label = Length_8_lm_eqn(Length_pH8), color="#56B4E9", parse = TRUE) +
            geom_text(x = 4000, y = .04, label = Length_7.5_lm_eqn(Length_pH7.5), color="#E69F00", parse = TRUE)

```

```{r Ws median shell length, echo=TRUE}
Resp.Master_OM <- Resp.Master_OM[!is.na(Resp.Master_OM$Length_um),]
summarySE(Resp.Master_OM, measurevar="Length_um")
print(paste( "Median shell length 9/14-10/26 = ", median(Resp.Master_OM$Length_um))) # 3148.36 
Ws <- 3148.36
```




# Calculate rates as ng L-1 O2 um shell length-1 hr-1

#### note: this chunk calls the data that used the 8-channel loligo system and the SDR system to correct for total respiration chamber (vial/vessel, well, etc.) volume separately 
- loligo 8-channel on 9/14/21 = 2.2 ml vessels 
- SDR 24-channel on 9/3-/21 = 1.7 ml wells 

```{r Calculate Resp Rates , echo=TRUE}
Resp.Master_OM <- Resp.Master_OM[!is.na(Resp.Master_OM$Length_um),]

# NORMALIZED for Shell Size (Length)
 Resp.Master_OM$resp_ng_L_μm_Length_hr <- ( 
          ( ( (abs(Resp.Master_OM$resp_blankStand)*1000000) * # call absolute value of resp in mg per minute - convert to ng min-1
                (Resp.Master_OM$volume/1000) ) / # vial volume for loligo 8 channel runs was 2.2 mL!!! - correct ng minute-1 to ng liter-1 by multiplying by the resp vial in liters
              Resp.Master_OM$Length_um) * # normalize by individual or larvae count - as to ng L-1 individual-1
            (60)) # correct for the time; final value is ng O2 Liter-1 um shell length-1 hour-1

 
 
# NORMALIZED for Dry Tissue Weight
 Resp.Master_OM$resp_mg_L_g_hr <- ( 
          ( ( (abs(Resp.Master_OM$resp_blankStand)) * # call absolute value of resp in mg per minute -  mg O2 L-1 per min-1
                (Resp.Master_OM$volume/1000) ) / # vial volume for loligo 8 channel runs was 2.2 mL!!! - correct ng minute-1 to ng liter-1 by multiplying by the resp vial in liters
              (Resp.Master_OM$Dry_Tissue_weight) ) * # normalize by Dry tissue weight  as to mg O2 L-1 g dry tissue weight-1
            (60)) # correct for the time; final value is ug O2 Liter -1 mg dry tissue weight-1 hour-1

```

# Mean standard error plot of all data 

```{r Line plot , echo=TRUE}
RespSumTab <- summarySE(Resp.Master_OM, measurevar="resp_ng_L_μm_Length_hr", groupvars=c("Age", "pCO2", "Fed_Unfed"))
RespSumTab$pCO2 <- factor(RespSumTab$pCO2, c("500 μatm","800 μatm"))
## Use geom_line and geom_point to plot over time
Resp_geomline<-ggplot(data=RespSumTab, aes(x=Age, y=resp_ng_L_μm_Length_hr, color=pCO2)) +
  geom_line(aes(linetype = factor(Fed_Unfed)), size = 0.5) +  
  geom_point()+ 
  scale_color_manual(values=c("forestgreen","darkorange2"))+
  geom_errorbar(aes(ymin=resp_ng_L_μm_Length_hr-se, ymax=resp_ng_L_μm_Length_hr+se), width=.2,
                position=position_dodge(.1))+
  theme_bw() +  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  scale_x_continuous(name ="Age (days)") +
  labs(title = "F1 Scallops: Food x OA Experiment", 
       y = expression(Respiration~rate~"("~ng~L^{-1}~O[2]%.%μ*m^{-1}%.% hr^{-1}~")")) +
  scale_linetype_manual(values = c("High food" = "solid", "Low food" = "dashed"))  +
  theme(legend.position="none") +
  # facet_wrap(~factor(Fed_Unfed, level = c('Low food', 'High food'))) 
  facet_wrap(~pCO2)

#pdf(paste0("C:/Users/samjg/Documents/Github_repositories/Airradians_OA/RAnalysis/Output/Respiration/Juvenile_respiration_FoodxOA.pdf"))
pdf(paste0("C:/Users/samjg/Documents/Github_repositories/Airradians_OA/RAnalysis/Output/Respiration/Juvenile_respiration_FoodxOA.pdf"))

Resp_geomline
dev.off()

Resp_geomline
```


# Analysis 

## 9/14/2021 F1 juvenile scallops

**About**
- two pCO2 treatments 
- **before** we culled and started the food limitation trials


#### number of replicates for analysis...

```{r 9/14 replicates, echo=FALSE}

# model effect of treatment on resp rate 20210507
Resp_0914 <- Resp.Master_OM %>% 
              dplyr::filter(Date %in% '9/14/2021')  %>% # call only 9/14
              dplyr::filter(!Chamber_tank  %in% 'blank')

Resp_0914 %>% dplyr::group_by(Chamber_tank) %>% dplyr::summarise(n()) # tank replication

```

## 20210914 linear model, diagnostics, and plots

```{r 9/14 lm diag and figs, echo=TRUE}
LMmod_0914 <- aov(lm(resp_ng_L_μm_Length_hr~pCO2,data=Resp_0914))
pander(summary(LMmod_0914), style='rmarkdown')
check_model(LMmod_0914) # observe the diagnostics of the model
shapiro.test(residuals(LMmod_0914)) #  normal - 0.3875
leveneTest(LMmod_0914) # good - 0.6186

DF   <- paste( (summary(LMmod_0914)[[1]][["Df"]])[1], (summary(LMmod_0914)[[1]][["Df"]])[2], sep = '/')
Fval <- (summary(LMmod_0914)[[1]][["F value"]])[1]
pval <- (summary(LMmod_0914)[[1]][["Pr(>F)"]])[1]

# pdf(paste0("C:/Users/samuel.gurr/Documents/Github_repositories/Airradians_OA/RAnalysis/Output/Respiration/20210914_respiration.pdf"))
#pdf(paste0("C:/Users/samjg/Documents/Github_repositories/Airradians_OA/RAnalysis/Output/Respiration/20210914_respiration.pdf"))
pdf(paste0("C:/Users/samjg/Documents/Github_repositories/Airradians_OA/RAnalysis/Output/Respiration/20210914_respiration.pdf"))

ggplot(Resp_0914, aes(x = factor(pCO2, level = c('500 μatm', '800 μatm')), resp_ng_L_μm_Length_hr , fill = pCO2)) +
  theme(panel.grid=element_blank()) +
  geom_boxplot(size=0.2, width=0.5, alpha=0.1, aes(fill=pCO2)) +
  scale_fill_manual(values=c("white","grey50")) +
  geom_point(shape = 21, size = 2, position = position_jitterdodge(jitter.width = 0.1)) +
  theme_classic() +
  scale_x_discrete(labels= c('~500 μatm', '~800 μatm')) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 4.25)) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold")) +
  labs(title = "F1 Scallops: respiration rates on 20210914", 
       y = expression(Respiration~rate~"("~ng~L^{-1}~O[2]%.%μ*m^{-1}%.% hr^{-1}~")"), 
       x = expression(italic(p)*CO[2]~Treatment~"("~μ*atm~")")) # + 
  # annotate("text", x=1.2, y=2.8, size = 4, label = "aov(Resp~pCO2)") +
  # annotate("text", x=1.2, y=2.6, size = 4, label= paste('DF =',DF,'F =', signif(Fval, digits=3), 'p value =', signif(pval, digits=3), sep=" ")) 
dev.off()
```



## 9/14/2021 F1 juvenile scallops

**About**

- two pCO2 treatments 

- *before* we culled and started the food limitation trials


#### number of replicates for analysis...

```{r 9/30 replicates, echo=FALSE}

Resp_0930 <- Resp.Master_OM %>% 
  dplyr::filter(Date %in% '9/30/2021')  %>% # call only 9/14
  dplyr::select(-Center)

Resp_0930 %>% dplyr::group_by(Chamber_tank, Food ) %>% dplyr::summarise(n()) # tank replication

```

## 20210930 linear model, diagnostics, and plots

```{r 9/30 lm diag and figs, echo=TRUE}

LMmod_0930 <- aov(lm(resp_ng_L_μm_Length_hr~pCO2*Fed_Unfed ,data=Resp_0930))
pander(summary(LMmod_0930), style='rmarkdown')
check_model(LMmod_0930) # observe the diagnostics of the model
shapiro.test(residuals(LMmod_0930)) #  normal - 0.07641
leveneTest(LMmod_0930) # good - 0.1648



DF_pCO2   <- paste( (summary(LMmod_0930)[[1]][["Df"]])[1], (summary(LMmod_0930)[[1]][["Df"]])[4], sep = '/')
Fval_pCO2 <- (summary(LMmod_0930)[[1]][["F value"]])[1]
pval_pCO2 <- (summary(LMmod_0930)[[1]][["Pr(>F)"]])[1]

DF_Fed    <- paste( (summary(LMmod_0930)[[1]][["Df"]])[2], (summary(LMmod_0930)[[1]][["Df"]])[4], sep = '/')
Fval_Fed  <- (summary(LMmod_0930)[[1]][["F value"]])[2]
pval_Fed  <- (summary(LMmod_0930)[[1]][["Pr(>F)"]])[2]

Resp_0930$Fed_Unfed <- as.factor(Resp_0930$Fed_Unfed)

levels(Resp_0930$Fed_Unfed) <- c("High food", "Low food")

# pdf(paste0("C:/Users/samuel.gurr/Documents/Github_repositories/Airradians_OA/RAnalysis/Output/Respiration/20210930_respiration.pdf"))
#pdf(paste0("C:/Users/samjg/Documents/Github_repositories/Airradians_OA/RAnalysis/Output/Respiration/20210930_respiration.pdf"))
pdf(paste0("C:/Users/samjg/Documents/Github_repositories/Airradians_OA/RAnalysis/Output/Respiration/20210930_respiration.pdf"))

ggplot(Resp_0930, aes(x = factor(pCO2, level = c('500 μatm', '800 μatm')), resp_ng_L_μm_Length_hr , fill = pCO2)) +
  theme(panel.grid=element_blank()) +
  geom_boxplot(size=0.2, alpha=0.1, aes(fill=pCO2)) +
  scale_fill_manual(values=c("white","grey50")) +
  geom_point(shape = 21, size = 2, position = position_jitterdodge(jitter.width = 0.1)) +
  theme_classic() +
  scale_x_discrete(labels= c('~500 μatm', '~800 μatm')) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 4.25)) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold")) +
  stat_summary(fun.y=mean, geom="point", shape=18, size=4, color="black", fill="white") +
  labs(title = "Respiration rate; F1 Scallops (juveniles) 66 days post-fertilization", 
       y = expression(Respiration~rate~"("~ng~L^{-1}~O[2]%.%mu*m^{-1}%.% hr^{-1}~")"), 
       x = expression(italic(p)*CO[2]~Treatment~"("~mu*atm~")")) + 
  facet_wrap(~factor(Fed_Unfed, level = c('Low food', 'High food'))) # + 
dev.off()
```




## 10/26/2021 F1 juvenile scallops

**About**

- two pCO2 treatments 

- *before* we culled and started the food limitation trials


#### number of replicates for analysis...

```{r 10/26 replicates, echo=FALSE}

Resp_01026 <- Resp.Master_OM %>% 
  dplyr::filter(Date %in% '10/26/2021')  %>% # call only 10/14
  dplyr::select(-Center)

Resp_01026 %>% dplyr::group_by(Chamber_tank, Food ) %>% dplyr::summarise(n()) # tank replication

```


## 20211026 linear model, diagnostics, and plots

```{r 10/26 lm diag and figs, echo=TRUE}

LMmod_01026 <- aov(lm(resp_ng_L_μm_Length_hr~pCO2*Fed_Unfed ,data=Resp_01026))
pander(summary(LMmod_01026), style='rmarkdown')
check_model(LMmod_01026) # observe the diagnostics of the model
shapiro.test(residuals(LMmod_01026)) #  normal - 0.3096
leveneTest(LMmod_01026) # 0.1998
TukeyHSD(LMmod_01026)


DF_pCO2   <- paste( (summary(LMmod_01026)[[1]][["Df"]])[1], (summary(LMmod_01026)[[1]][["Df"]])[4], sep = '/')
Fval_pCO2 <- (summary(LMmod_01026)[[1]][["F value"]])[1]
pval_pCO2 <- (summary(LMmod_01026)[[1]][["Pr(>F)"]])[1]

DF_Fed    <- paste( (summary(LMmod_01026)[[1]][["Df"]])[2], (summary(LMmod_01026)[[1]][["Df"]])[4], sep = '/')
Fval_Fed  <- (summary(LMmod_01026)[[1]][["F value"]])[2]
pval_Fed  <- (summary(LMmod_01026)[[1]][["Pr(>F)"]])[2]


DF_Int    <- paste( (summary(LMmod_01026)[[1]][["Df"]])[3], (summary(LMmod_01026)[[1]][["Df"]])[4], sep = '/')
Fval_Int  <- (summary(LMmod_01026)[[1]][["F value"]])[3]
pval_Int  <- (summary(LMmod_01026)[[1]][["Pr(>F)"]])[3]


Resp_01026$Fed_Unfed <- as.factor(Resp_01026$Fed_Unfed)

levels(Resp_01026$Fed_Unfed) <- c("High food", "Low food")

# pdf(paste0("C:/Users/samuel.gurr/Documents/Github_repositories/Airradians_OA/RAnalysis/Output/Respiration/202101026_respiration.pdf"))
#pdf(paste0("C:/Users/samjg/Documents/Github_repositories/Airradians_OA/RAnalysis/Output/Respiration/202101026_respiration.pdf"))
pdf(paste0("C:/Users/samjg/Documents/Github_repositories/Airradians_OA/RAnalysis/Output/Respiration/202101026_respiration.pdf"))

ggplot(Resp_01026, aes(x = factor(pCO2, level = c('500 μatm', '800 μatm')), resp_ng_L_μm_Length_hr , fill = pCO2)) +
  theme(panel.grid=element_blank()) +
  geom_boxplot(size=0.2, alpha=0.1, aes(fill=pCO2)) +
  scale_fill_manual(values=c("white","grey50")) +
  geom_point(shape = 21, size = 2, position = position_jitterdodge(jitter.width = 0.1)) +
  theme_classic() +
  #ylim(0, 3) +
  scale_x_discrete(labels= c('~500 μatm', '~800 μatm')) +
  scale_y_continuous(expand = c(0, 0), limits = c(0, 4.25)) +
  theme(axis.text=element_text(size=12),
        axis.title=element_text(size=14,face="bold")) +
  stat_summary(fun.y=mean, geom="point", shape=18, size=4, color="black", fill="white") +
  labs(title = "Respiration rate; F1 Scallops (juveniles) 92 days post-fertilization", 
       y = expression(Respiration~rate~"("~ng~L^{-1}~O[2]%.%mu*m^{-1}%.% hr^{-1}~")"), 
       x = expression(italic(p)*CO[2]~Treatment~"("~mu*atm~")")) + 
  facet_wrap(~factor(Fed_Unfed, level = c('Low food', 'High food'))) # + 
dev.off()


# see what the dry tissue weight looks like for the data we have so far.... ( only have it for the fed animals ! - filter first and then run it)
Resp_fed_drywt <- Resp_01026 %>% dplyr::filter(Food %in% "fed") %>% 
                ggplot(aes(x = factor(pCO2, level = c('500 μatm', '800 μatm')), resp_mg_L_g_hr, fill = pCO2)) + # DRY TISSUE WEIGHT! 'resp_μg_L_g_hr' - note: look at Length_um, resp_blankStand, and finally resp_mg_L_g_hr to determine why we see this difference..
                theme(panel.grid=element_blank()) +
                geom_boxplot(size=0.2, alpha=0.1, aes(fill=pCO2)) +
                scale_fill_manual(values=c("white","grey50")) +
                geom_point(shape = 21, size = 2, position = position_jitterdodge(jitter.width = 0.1)) +
                theme_classic() +
                #ylim(0, 3) +
                scale_x_discrete(labels= c('~500 μatm', '~800 μatm')) +
                #scale_y_continuous(expand = c(0, 0), limits = c(0, 4.25)) +
                theme(axis.text=element_text(size=12),
                      axis.title=element_text(size=14,face="bold")) +
                stat_summary(fun.y=mean, geom="point", shape=18, size=4, color="black", fill="white") +
                labs(title = "Respiration rate; F1 Scallops (juveniles) 92 days post-fertilization", 
                     y = expression(Respiration~rate~"("~mg~L^{-1}~O[2]%.%g^{-1}%.% hr^{-1}~")"), 
                     x = expression(italic(p)*CO[2]~Treatment~"("~mu*atm~")")) 
Resp_fed_drywt # the effect with normalization to shell size persists here...
```