---
title: "Respiration Analysis F1 Scallops 2021"
author: "Samuel Gurr"
date: "10/6/2021"
output:
  html_document:
    df_print: paged
  pdf_document:
    latex_engine: xelatex
---


```{r setup, include=FALSE}

# LOAD PACKAGES :::::::::::::::::::::::::::::::::::::::::::::::::::::::

library(dplyr)
library(ggplot2)
library(forcats)
library(lme4)
library(lmerTest)
library(see)
library(performance)
library(car)
library(kableExtra)
library(pander)
library(data.table)
library(stringr)
library(latex2exp)
library(Rmisc)
# library(devtools)
library(ggpubr)
library(hrbrthemes)
library(nlme)
# SET WORKING DIRECTORY :::::::::::::::::::::::::::::::::::::::::::::::

 setwd("C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis") # personal computer
# setwd("C:/Users/samuel.gurr/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis") # Work computer
# setwd("C:/Users/samjg/Documents/Github_repositories/Airradians_OA/RAnalysis") # Work computer

# LOAD DATA :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

resp.data       <- read.csv(file="Output/Respiration/Cumulative_resp_alpha0.4_15sectrunc1hour.csv", header=T) %>% 
                      dplyr::filter(!Date %in% "9/14/2021" | !Filename %in% 'Run_1_raw.txt') # read the calculate raw rates from 'resp_LoLin' script - contains the calculated rate (not normalized for blanks) for each sensor-channel
exp_metadata    <- read.csv(file="Data/ExperimentMetadata.csv", header=T) # treatment assignments to 'Chamber_Tank'
lengths         <- read.csv(file="Data/Respiration/Lengths_Condition_resp_clearance.csv", header=T)
resp.ref        <- read.csv(file="Data/Respiration/Reference_master.csv", header=T) %>% dplyr::filter(!Date %in% "9/14/2021" | !Filename %in% 'Run_1_raw.txt')
DWs_Len_1026    <- read.csv(file="Data/Survival_Size/20211026_lengths_dryweights.csv", header=T)
DWs_Len_914.930 <- read.csv(file="Data/Survival_Size/2021914_930_dryweights.csv", header=T)

```


### Merge master resp data frame with lengths

```{r merge resp with length data and treatment IDs, echo=FALSE}

# merge the exp_metadata with the resp.data
resp.ref_length_merged                 <- merge(resp.ref, lengths) # all TRUE allows us to keep the blanks
resp.data_merged                       <- merge(resp.data, resp.ref_length_merged) %>% # out master file moving forward....
                                            dplyr::mutate(filetype = str_sub(Filename, -3,-1)) %>% 
                                            dplyr::mutate(filetype = factor(ifelse(filetype == "csv", "SDR_data", "LoLigo_data")))
kable(head(resp.data_merged))

```

#### Visual diagnostic plots to correct poor data (3 data points to change..)

- View on github: Airradians_OA/RAnalysis/Output/Respiration/plots_alpha0.4_increm15sec/

- found three calls that inaccurately represent the rates of oxygen consumption 

(1) https://github.com/SamGurr/Airradians_OA/blob/master/RAnalysis/Output/Respiration/plots_alpha0.4_increm15sec/20210930_Plate_2_Run_2_C5_regression.pdf
- solution = call 'Lz' instead of the default Leq

(2) https://github.com/SamGurr/Airradians_OA/blob/master/RAnalysis/Output/Respiration/plots_alpha0.4_increm15sec/20210930_Plate_2_Run_1_C1_regression.pdf
- solution = call 'Lz' instead of the default Leq

(3) https://github.com/SamGurr/Airradians_OA/blob/master/RAnalysis/Output/Respiration/plots_alpha0.4_increm15sec/20210930_Plate_1_Run_2_C1_regression.pdf
- solution = we reran this at the end of the LoLin script  for 0-20 minutes and got an Lpc  -0.0296, insert this 

```{r IMPORTANT correct poor data, echo=TRUE, message = FALSE, warning = FALSE}
resp.data_merged[95 ,c(1:6)]  # 	C1 RR_9.30.21_AM_Plate_2_Run_1.csv # -0.02890813	-0.0608251	-0.0608251 - Lz and Leq call better regression than Lpc
resp.data_merged[111,c(1:6)] #  C5 RR_9.30.21_PM_Plate_2_Run_2.csv	0.029052351	-0.076034441	-0.076034441
resp.data_merged[96 ,c(1:6)]  # 	C1 RR_9.30.21_PM_Plate_1_Run_2.csv	0.011656487	0.011656487	0.011656487  - ommit this
resp.data_merged[23 ,c(1:6)] # CH5	Run_1_raw.txt	-0.00704407	-0.005910146	-0.005910146 - omit and change based on visual of the raw data - resp between 60-100 minuntss = -0.0275 (LoLin.R scrip tat the end - redo error data)


resp.data_merged[95 ,4]  <- resp.data_merged[95,5] # 20210930_Plate_2_Run_2_C5_regression - Lz and Leq call better regression than Lpc
resp.data_merged[111,4]  <- resp.data_merged[111,5] # 20210930_Plate_2_Run_1_C1_regression - Lz and Leq call better regression than Lpc
resp.data_merged[96 ,4]  <- as.numeric(-0.0296) # 20210930_Plate_1_Run_2_C1_regression - plot shows noise after the 20 minutes mark, we reran this at the end of the LoLin script, insert here!
resp.data_merged[23 ,4]  <- as.numeric(-0.0275)


resp.data_merged[95 ,c(1:6)]  # -0.0608251
resp.data_merged[111,c(1:6)] # -0.07603444
resp.data_merged[96 ,c(1:6)]  # -0.0296	
resp.data_merged[23 ,c(1:6)]  # -0.0275
# View(resp.data_merged)
```

#### Calculate blank rates, view means by day pH_treatment and instrument

* note: respiration rates were recorded using both SDR dish (24 channel) and Loligo 8-channel sensors - different blanks for each

```{r call blanks, echo=FALSE}

blanks_total <- data.frame() # start dataframe 
blanks.table <- data.frame(matrix(nrow = 1,ncol = 5)) # make a table template
colnames(blanks.table)<-c('Date', 'Channel', 'mean_Lpc', 'mean_Leq' , 'mean_Lz') # names for comuns in the for loop

blanks_all_raw <- data.frame(merge(resp.ref, resp.data, by = c('Date', 'Channel', 'Filename')) %>% 
                  dplyr::filter(!Date ==  '9/14/2021'   | !Filename == 'Run_1_raw.txt') %>%  # run 1 was restarted due to poor data
                  dplyr::mutate(filetype = str_sub(Filename, -3,-1)) %>% 
                  dplyr::mutate(filetype = factor(ifelse(filetype == "csv", "SDR_data", "LoLigo_data"))) %>% 
                  dplyr::filter(Chamber_tank  == 'blank') %>% 
                  # dplyr::filter(Lpc <0) %>% 
                  dplyr::filter(!Date == '9/30/2021' | !Lpc < -0.035) %>% #omits C6 RR_9.30.21_AM_Plate_1_Run_1.csv	8.0	blank - View the Lolin plot, looks noisy and a fast outlier from the others
                  dplyr::filter(!Date == '10/26/2021'  | !Channel == "CH8" | !Run == "2" ) %>%  # omit a bad blank that contained a bad seal, noted on the respiration sampling day during the trial 
                  dplyr::filter(!Date == '10/26/2021'  | !Channel == "CH8" | !Run == "3" ) %>%  # omit a bad blank that contained a bad seal, noted on the respiration sampling day during the trial 
                  dplyr::filter(!Date ==  '9/30/2021'   | !pH == "7.5" | !Channel == "B2" | !Run == "1" | !Plate == "1" ) %>% 
                  dplyr::select(c(Date, pH, Run, Plate, Lpc, Leq ,Lz, Channel, Food, Filename, filetype, Chamber_tank)) %>% 
                  dplyr::arrange(Date, Run, pH))
kable(blanks_all_raw)



blanks_means <- blanks_all_raw %>% 
     dplyr::group_by(Date, pH, Run, filetype) %>% 
     dplyr::filter(Chamber_tank == "blank") %>% 
     dplyr::filter(Lpc <0) %>% # ommit blank calls that d/n represent oxygen consumption
     dplyr::summarise(BLANK.mean_Lpc = mean(abs(Lpc)),
                      BLANK.sd.Lpc   = sd(abs(Lpc)),
                      BLANK.mean_Leq = mean(abs(Leq)), 
                      BLANK.mean_Lz = mean(abs(Lz)),
                      n = n()) %>% 
    dplyr::arrange(Date, Run)
kable(blanks_means)

dups_to_add <- blanks_means[c(5:7),] %>% mutate(pH = 7.5) # only pH 8 contains a positive blank on 9/14 Run 1 and 10/26 Run 2- duplicate and save as pH 7.5 
blanks_means <- rbind(blanks_means, dups_to_add) %>% dplyr::arrange(Date, Run) 
kable(blanks_means) # you can now see that each Date, Run, has a pH 8 and pH 7.5 blank
```


#### Merge blanks with the master file by Date, pCO2 treatment, and filetype

* 'filteype' is only important here on 20211026 when both Loligo and SDR were used due to difference in size for fed (larger) and unfed animals 

```{r merge blanks_means for a master file, echo=FALSE}

Resp.Master <- merge(resp.data_merged, blanks_means, by=c("Date", "pH", "Run", "filetype")) %>% # NOTE: this repeats for every distinct length value
  dplyr::mutate(resp_blankStand = abs(Lpc) - BLANK.mean_Lpc) # ommits respiration rate values showing an increase in O2 over time 

Resp.less.than.blank <- Resp.Master %>% dplyr::filter(resp_blankStand < 0) %>% dplyr::select(c(1:7,15,18,29)) %>% mutate(Lpc = abs(Lpc)) # call the values with positive resp rates, measing they were slower than the blank!
print(Resp.less.than.blank) # 15 total samples were less than the blank after the correction... (Lpc < BLANK.mean_LPC)

```


## Master Resp file 'Resp.Master_OM', with volumes and file types, etc. saved as 'Calculated_Resp_Master.csv'

######  dplyr::mutate for the following:

* 'volume' of the different vessels throughout the fed*OA challenge
* 'Age'
* 'Fed_unfed'
* 'pCO2'

```{r master resp file, echo=FALSE}

Resp.Master_OM <- Resp.Master[!is.na(Resp.Master$Length_um),] %>% dplyr::filter(!resp_blankStand < 0) %>% # omit respiration values subtracted by blank (resp_blankStand) that are negative (less than the blank)
  dplyr::mutate(volume = case_when(filetype == "LoLigo_data" & Date == '9/14/2021' ~ 2.2, # small vessels for loligo system - 22 ml vessels
                                   filetype == "LoLigo_data" & Date == '10/26/2021' & Channel == 'CH1' ~ 68.55323, # larger custom vessels measured individually...
                                   filetype == "LoLigo_data" & Date == '10/26/2021' & Channel == 'CH2' ~ 68.85583, # larger custom vessels measured individually...
                                   filetype == "LoLigo_data" & Date == '10/26/2021' & Channel == 'CH3' ~ 68.87473, # larger custom vessels measured individually...
                                   filetype == "LoLigo_data" & Date == '10/26/2021' & Channel == 'CH4' ~ 68.95481, # larger custom vessels measured individually...
                                   filetype == "LoLigo_data" & Date == '10/26/2021' & Channel == 'CH5' ~ 68.57288, # larger custom vessels measured individually...
                                   filetype == "LoLigo_data" & Date == '10/26/2021' & Channel == 'CH6' ~ 68.01878, # larger custom vessels measured individually...
                                   filetype == "LoLigo_data" & Date == '10/26/2021' & Channel == 'CH7' ~ 68.54551, # larger custom vessels measured individually...
                                   filetype == "LoLigo_data" & Date == '10/26/2021' & Channel == 'CH8' ~ 68.53297, # larger custom vessels measured individually...
                                   filetype == "SDR_data" ~ 1.7)) %>% # 24-well plate - 1700ul 
  # mg minute -> mg L hr
  dplyr::mutate(resp_mg_L_hr =(resp_blankStand *  # resp corrected for blank (remember within Date, Run and treatment!) - currently as raw units of mg O2 per minute (output from LoLinR script)
                                      (volume/1000) * # mult by volume of the resp vessel corrected in Liters - now units in  mg per L per min
                                       60))  %>% # mult by 60 to convert to hours - now units in mg L per hour
  # mg L hr -> umol L hr
  dplyr::mutate(resp_umol_L_hr = ( (resp_mg_L_hr * 1000) / 16) ) %>% #  convert mg L per hr to umol L hr- first by mg to ug (mg*1000 = ug) and then ug to umol (1 umol = 32 ug -  ug O2 div 32 ug/umol)                                
  dplyr::mutate(Age = case_when(Date == '9/14/2021' ~ 50, Date == '9/30/2021' ~ 66, Date == '10/26/2021' ~ 92)) %>% 
  dplyr::mutate(Fed_Unfed = case_when(Fed_Unfed == 'F' ~ "High food", is.na(Fed_Unfed) ~ "High food", Fed_Unfed == 'U' ~ "Low food")) %>% 
  dplyr::mutate(pCO2 = case_when(pH == 8.0 ~ "500 μatm", pH == 7.5 ~ "800 μatm"))

Resp.Master %>% dplyr::filter(resp_blankStand < 0) # 15 rows omitted 
```


### Relationship between Whole dry weight  v. Shell length 

```{r DW v shell length plot,  echo=TRUE, message = FALSE, warning = FALSE}
Resp.Master_OM %>% ggplot(aes(x = Length_um, y = resp_umol_L_hr)) +
                                geom_smooth(method = "lm") +
                                theme_classic() +
                                ylab("resp_umol_L_hr") +
                                xlab("Length_um") +
                                geom_point()  +
                                facet_wrap(~Age + Fed_Unfed, scales = 'free')

```


### Standardize rates as...

##### (1) shell length: umol L-1 O2 mm shell length hour-1
##### (2) whole dry weight: umol L-1 O2 g whole dry weight hour-1 
##### (3) Standardized by shell length (allometric coefficient)


```{r Calculate Resp Rates , echo=TRUE, message = FALSE, warning = FALSE}
# Resp.Master_OM <- Resp.Master_OM[!is.na(Resp.Master_OM$Length_um),]

# (1)  umol O2 L-1 g dry tissue weight-1 ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# NORMALIZED for Shell length
Resp.Master_OM$resp_µmol_L_mm_Length_hr <- (Resp.Master_OM$resp_umol_L_hr / # multiple by 1000 to convert mmol/ O2 to umol/L O2
              (Resp.Master_OM$Length_um/1000)) # normalize by Dry tissue weight  as to mg O2 L-1 g dry tissue weight-1

# (2) mg O2 L-1 g dry tissue weight-1 :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# NORMALIZED for Whole animal dry weight (g)
Resp.Master_OM$resp_µmol_mg_hr <- (Resp.Master_OM$resp_umol_L_hr / 
              (Resp.Master_OM$whole_Dry_weight)) # normalize by Dry tissue weight  as to mg O2 L-1 g dry tissue weight-1



# write.csv(Resp.Master_OM, "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/Calculated_Resp_Master.csv")
 write.csv(Resp.Master_OM, "C:/Users/samuel.gurr/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/Calculated_Resp_Master.csv")

```



### Plot the RAW rates by the size metrics 

####  (1) Shell length vs. Raw respiration rate (umol O2 L- hr-1)...
``` {r Shell length vs. raw respiration rate, echo=TRUE, message = FALSE, warning = FALSE}

# by Length :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

P_Length_resp_all <- Resp.Master_OM[!is.na(Resp.Master_OM$resp_umol_L_hr),] %>% 
                        ggplot(aes(x = (Length_um/1000), y = resp_umol_L_hr, color = as.factor(pCO2))) +
                         scale_color_manual(values=c("forestgreen","darkorange2"))+
                          geom_smooth(method = "lm", se=FALSE, color="black", formula = resp_umol_L_hr ~ Length_um) +
                          theme_classic() +
                          theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), plot.title = element_text(size=10))+ 
                          labs(title = "Raw Resp v. Shell length (μm)", y = expression(μmol~L^{-1}~O[2]%.%hr^{-1})) +
                          xlab("Shell length (mm)") +
                          theme(legend.position="none") +
                          geom_point()

P_Length_resp_facet <- Resp.Master_OM[!is.na(Resp.Master_OM$resp_umol_L_hr),] %>% 
                        ggplot(aes(x = (Length_um/1000), y = resp_umol_L_hr, color = as.factor(pCO2))) +
                         scale_color_manual(values=c("forestgreen","darkorange2"))+
                          geom_smooth(method = "lm", se=FALSE, color="black", formula = resp_umol_L_hr ~ Length_um) +
                          theme_classic() +
                           theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.position = "none", plot.title = element_text(size=10))+ 
                          labs(y = expression(μmol~L^{-1}~O[2]%.%hr^{-1})) +
                          xlab("Shell length (mm)") +
                          geom_point() + 
                          facet_wrap(~Age*Food, scales = "free")

# print in markdown file 
ggarrange(P_Length_resp_all, P_Length_resp_facet,nrow = 2)
# Export to pdf
pdf(paste0(filename = "C:/Users/samuel.gurr/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/Shell_length_resp_raw.pdf"), width = 10, height = 6)
pdf(paste0(filename = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/Shell_length_resp_raw.pdf"), width = 10, height = 6)
ggarrange(P_Length_resp_all, P_Length_resp_facet,ncol = 2)
dev.off()

```


#### (2) Whole animal dry weight vs. Raw respiration rate (umol O2 L- hr-1)...
```{r Whole dry weight length vs. raw respiration rate, echo=TRUE, message = FALSE, warning = FALSE}

# by WHOLE animal dry weight  :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

P_WholeDW_resp_all  <- Resp.Master_OM[!is.na(Resp.Master_OM$resp_umol_L_hr),] %>% 
                          ggplot(aes(x = whole_Dry_weight, y = resp_umol_L_hr, color = as.factor(pCO2))) +
                            scale_color_manual(values=c("forestgreen","darkorange2"))+
                            geom_smooth(method = "lm", se=FALSE, color="black", formula = resp_umol_L_hr ~ whole_Dry_weight) +
                            theme_classic() +
                            theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), plot.title = element_text(size=10))+ 
                            labs(title = "Raw Resp v. Whole dry weight (mg)", y = expression(μmol~L^{-1}~O[2]%.%hr^{-1})) +
                            theme(legend.position="none") +
                            xlab("Whole dry weight (mg)") +
                            geom_point()

P_WholeDW_resp_facet <- Resp.Master_OM[!is.na(Resp.Master_OM$resp_umol_L_hr),] %>% 
                          ggplot(aes(x = whole_Dry_weight, y = resp_umol_L_hr, color = as.factor(pCO2))) +
                            scale_color_manual(values=c("forestgreen","darkorange2"))+
                            geom_smooth(method = "lm", se=FALSE, color="black", formula = resp_umol_L_hr ~ whole_Dry_weight) +
                            theme_classic() +
                            theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.position = "none",plot.title = element_text(size=10))+ 
                            labs(y = expression(μmol~L^{-1}~O[2]%.%hr^{-1})) +
                            xlab("Whole dry weight (mg)") +
                            geom_point() + 
                            facet_wrap(~Age*Food, scales = "free")


# print in markdown file 
ggarrange(P_WholeDW_resp_all, P_WholeDW_resp_facet,ncol = 2)
# Export to pdf
pdf(paste0(filename = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/WholeDW_resp_raw.pdf"), width = 10, height = 6)
#pdf(paste0(filename = "C:/Users/samuel.gurr/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/WholeDW_resp_raw.pdf"), width = 10, height = 6)
ggarrange(P_WholeDW_resp_all, P_WholeDW_resp_facet,ncol = 2) 
dev.off()


```


### (1,2, and 3) Assemble Standrdized rate (allometric coeff) and corrected rates for shell length and dry tissue weight...
```{r Line plot , echo=TRUE, message = FALSE, warning = FALSE}


 
# Length :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

# Length_um
SumTab_Len      <- Resp.Master_OM[!is.na(Resp.Master_OM$Length_um),] %>%  
            mutate(Length_mm = Length_um/1000) %>% 
            summarySE(measurevar="Length_mm", groupvars=c("Age", "pCO2", "Fed_Unfed"))
SumTab_Len$pCO2 <- factor(SumTab_Len$pCO2, c("500 μatm","800 μatm"))
## Use geom_line and geom_point to plot over time
Length_time    <- ggplot(data=SumTab_Len, aes(x=Age, y=Length_mm, color=pCO2)) +
            geom_line(aes(linetype = factor(Fed_Unfed)), size = 0.5) +  
            geom_point()+ 
            scale_color_manual(values=c("forestgreen","darkorange2"))+
            geom_errorbar(aes(ymin=Length_mm-se, ymax=Length_mm+se), width=.2,
                          position=position_dodge(.1))+
            theme_bw() +  
            theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), plot.title = element_text(size=10))+ 
            scale_x_continuous(name ="Age (d)") +
            labs(title =  "Shell length over time..", 
                 y = "Shell length (mm)") +
            scale_linetype_manual(values = c("High food" = "solid", "Low food" = "dashed"))  +
            theme(legend.position="none") +
            # facet_wrap(~factor(Fed_Unfed, level = c('Low food', 'High food'))) 
            facet_wrap(~pCO2)
Length_time


# resp_µmol_L_mm_Length_hr
RespSumTab_Len      <- Resp.Master_OM[!is.na(Resp.Master_OM$resp_µmol_L_mm_Length_hr),] %>%  
            summarySE(measurevar="resp_µmol_L_mm_Length_hr", groupvars=c("Age", "pCO2", "Fed_Unfed"))
RespSumTab_Len$pCO2 <- factor(RespSumTab_Len$pCO2, c("500 μatm","800 μatm"))
## Use geom_line and geom_point to plot over time
Resp_LengthStand    <- ggplot(data=RespSumTab_Len, aes(x=Age, y=resp_µmol_L_mm_Length_hr, color=pCO2)) +
            geom_line(aes(linetype = factor(Fed_Unfed)), size = 0.5) +  
            geom_point()+ 
            scale_color_manual(values=c("forestgreen","darkorange2"))+
            geom_errorbar(aes(ymin=resp_µmol_L_mm_Length_hr-se, ymax=resp_µmol_L_mm_Length_hr+se), width=.2,
                          position=position_dodge(.1))+
            theme_bw() +  
            theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), plot.title = element_text(size=10))+ 
            scale_x_continuous(name ="Age (d)") +
            labs(title = "Resp corrected by shell length", 
                 y = expression(μmol~L^{-1}~O[2]%.%mm^{-1}~shell~length%.% hr^{-1})) +
            scale_linetype_manual(values = c("High food" = "solid", "Low food" = "dashed"))  +
            theme(legend.position="none") +
            # facet_wrap(~factor(Fed_Unfed, level = c('Low food', 'High food'))) 
            facet_wrap(~pCO2)


# Whole dry weight :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

# resp_µmol_mg_hr
SumTab_WholeDW      <- Resp.Master_OM[!is.na(Resp.Master_OM$resp_µmol_mg_hr),] %>%  
            summarySE(measurevar="whole_Dry_weight", groupvars=c("Age", "pCO2", "Fed_Unfed"))
SumTab_WholeDW$pCO2 <- factor(SumTab_WholeDW$pCO2, c("500 μatm","800 μatm"))
## Use geom_line and geom_point to plot over time
WholeDW_time    <- ggplot(data=SumTab_WholeDW, aes(x=Age, y=whole_Dry_weight, color=pCO2)) +
            geom_line(aes(linetype = factor(Fed_Unfed)), size = 0.5) +  
            geom_point()+ 
            scale_color_manual(values=c("forestgreen","darkorange2"))+
            geom_errorbar(aes(ymin=whole_Dry_weight-se, ymax=whole_Dry_weight+se), width=.2,
                          position=position_dodge(.1))+
            theme_bw() +  
            theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), plot.title = element_text(size=10))+ 
            scale_x_continuous(name ="Age (d)") +
            labs(title = "Whole dry weight over time..", 
                 y = "Whole dry weight (mg)") +
            scale_linetype_manual(values = c("High food" = "solid", "Low food" = "dashed"))  +
            theme(legend.position="none") +
            # facet_wrap(~factor(Fed_Unfed, level = c('Low food', 'High food'))) 
            facet_wrap(~pCO2)

RespSumTab_DW      <- Resp.Master_OM[!is.na(Resp.Master_OM$resp_µmol_mg_hr),] %>%  
          summarySE(measurevar="resp_µmol_mg_hr", groupvars=c("Age", "pCO2", "Fed_Unfed"))
RespSumTab_DW$pCO2 <- factor(RespSumTab_DW$pCO2, c("500 μatm","800 μatm"))
## Use geom_line and geom_point to plot over time
Resp_DryWgtStand   <- ggplot(data=RespSumTab_DW, aes(x=Age, y=resp_µmol_mg_hr, color=pCO2)) +
          geom_line(aes(linetype = factor(Fed_Unfed)), size = 0.5) +  
          geom_point()+ 
          scale_color_manual(values=c("forestgreen","darkorange2"))+
          geom_errorbar(aes(ymin=resp_µmol_mg_hr-se, ymax=resp_µmol_mg_hr+se), width=.2,
                        position=position_dodge(.1))+
          theme_bw() +  
          theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), plot.title = element_text(size=10))+ 
          scale_x_continuous(name ="Age (d)") +
          labs(title = "Resp corrected by whole animal dry weight", 
               y = expression(μmol~L^{-1}~O[2]%.%mg^{-1}~whole~DW%.% hr^{-1})) +
          scale_linetype_manual(values = c("High food" = "solid", "Low food" = "dashed"))  +
          theme(legend.position="none") +
          # facet_wrap(~factor(Fed_Unfed, level = c('Low food', 'High food'))) 
          facet_wrap(~pCO2)



# Print assembled plot from previous chunks....  ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# both shell length and whole dry weight used for standardizing respiration rate - view the diagnostic pots for this here (good visual!)
pdf(paste0(filename = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/All_Respiration_normalized_summary.pdf"), width = 10, height = 8)
# pdf(paste0(filename = "C:/Users/samuel.gurr/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/All_Respiration_normalized_summary.pdf"), width = 10, height = 8)
ggarrange(P_Length_resp_all ,Length_time, Resp_LengthStand,
          P_WholeDW_resp_all, WholeDW_time, Resp_DryWgtStand, ncol = 3, nrow = 2, heights=c(1,1))
dev.off()



```




### Skip to here to load the resp master file (if already completed above chunks!!)



```{r load master resp file, echo=FALSE}

# Resp.Master_OM    <- read.csv(file="C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/Calculated_Resp_Master.csv", header=T) # personnel computer 
Resp.Master_OM    <- read.csv(file="C:/Users/samuel.gurr/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/Calculated_Resp_Master.csv", header=T) # work computer

```



# Analysis 



### 9/14/2021 F1 juvenile scallops

**About**
- two pCO2 treatments 
- **before** we culled and started the food limitation trials


##### number of replicates for analysis...

```{r 9/14 replicates and mean resp, echo=FALSE}

# model effect of treatment on resp rate 20210507
Resp_0914 <- Resp.Master_OM %>% 
              dplyr::filter(Date %in% '9/14/2021')  %>% # call only 9/14
              dplyr::filter(!Chamber_tank  %in% 'blank')

Resp_0914 %>% dplyr::group_by(Chamber_tank) %>% dplyr::summarise(n()) # tank replication
# 7.5_A	3			
# 7.5_B	3			
# 7.5_C	3			
# 7.5_D	3			
# 8_A	2	   *2 rep			
# 8_B	3			
# 8_C	3			
# 8_D	1	   *1 rep

Resp_0914 %>% summarySE(measurevar="resp_µmol_L_mm_Length_hr", groupvars=c("pH")) %>% 
      dplyr::mutate(pCO2 = case_when(pH == 8  ~ "500 μatm", pH == 7.5 ~ "800 μatm"))


```

### 9/14/2021 linear model, diagnostics, and plots

#### Length standardized

```{r 9/14 Length standardized, echo=TRUE, message = FALSE, warning = FALSE}

# Shell length standardized (SL) ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
Resp_0914 %>% summarySE(measurevar="resp_µmol_L_mm_Length_hr", groupvars=("pH")) %>% 
      dplyr::mutate(pCO2 = case_when(pH == 8  ~ "500 μatm", pH == 7.5 ~ "800 μatm"))

# plot the replicates (visual diagnostics of random factor)
Resp914_Length_reps<- ggboxplot(Resp_0914, x = "pH", y = "resp_µmol_L_mm_Length_hr", color = "Replicate",
                              add = c("mean_se", "dotplot"),
                              palette = c("#00AFBB", "#E7B800", "brown", "grey"))
Resp914_Length_reps

# One-way ANOVA (without the random effect) 
Resp914_ANOVA <- aov(resp_µmol_L_mm_Length_hr ~ pCO2, data=Resp_0914) # run mod
summary(Resp914_ANOVA) # summary mod
kable(  data.frame(unclass(summary(Resp914_ANOVA)), check.names = FALSE, stringsAsFactors = FALSE)  ) %>%  # print a png of this table
  kable_styling() %>%
  save_kable(file = "C:/Users/samuel.gurr/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/20210914_figs_tables/20210914_resp_OneWayANOVA_Table.png", zoom = 1.5)
#              Df   Sum Sq   Mean Sq F value Pr(>F)
# pCO2         1 0.000004 0.0000036   0.007  0.932
# Residuals   19 0.009096 0.000478
shapiro.test(residuals(Resp914_ANOVA)) # normal - 0.3276
leveneTest(Resp914_ANOVA) # homogeneity of variance (equal variance - 0.4131


# Linear mixed effects model with random effect of Replicate 
LMEmod_0914_SL<-lme(resp_µmol_L_mm_Length_hr ~ pCO2, random=~1|Chamber_tank, data=Resp_0914) # with the random effect as an LME model
# |     &nbsp;      | numDF | denDF | F-value |  p-value  |
# |:---------------:|:-----:|:-----:|:-------:|:---------:|
# | **(Intercept)** |   1   |  13   |  32.12  | 7.699e-05 |
# |    **pCO2**     |   1   |   6   | 0.02054 |  0.8907   |
pander(anova(LMEmod_0914_SL), style='rmarkdown') # anova table of lmer
kable(as.data.frame(anova(LMEmod_0914_SL))) %>%  # print a png of this table
  kable_styling() %>%
  save_kable(file = "C:/Users/samuel.gurr/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/20210914_figs_tables/20210914_resp_LME_Table.png", zoom = 1.5)
pdf(paste0(filename = "C:/Users/samuel.gurr/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/20210914_figs_tables/20210914_resp_LME_Diagnostics.pdf"))
check_model(LMEmod_0914_SL) # print the model diagnostics 
dev.off()

# call the results of LMER to add to boxplot below 
DF   <- paste( (anova(LMEmod_0914_SL)[[1]])[2], (anova(LMEmod_0914_SL)[[2]])[2], sep = '/') # call DF
Fval <- (anova(LMEmod_0914_SL)[[3]])[2] # call f
pval <- (anova(LMEmod_0914_SL)[[4]])[2] # call p value

# plot
Resp914_Length <- ggplot(Resp_0914, aes(x = factor(pCO2, level = c('500 μatm', '800 μatm')), resp_µmol_L_mm_Length_hr , fill = pCO2)) +
                    theme(panel.grid=element_blank()) +
                    geom_boxplot(size=0.2, width=0.5, alpha=0.1, aes(fill=pCO2)) +
                    scale_fill_manual(values=c("white","grey50")) +
                    geom_point(shape = 21, size = 2, position = position_jitterdodge(jitter.width = 0.1)) +
                    theme_classic() +
                    scale_x_discrete(labels= c('~500 μatm', '~800 μatm')) +
                   # scale_y_continuous(expand = c(0, 0), limits = c(0, 2)) +
                    labs(title = "F1 Scallops: respiration rates on 20210914 (shell length stand.)", 
                         y = expression(Respiration~rate~"("~μmol~L^{-1}~O[2]%.%mm^{-1}~shell~length%.% hr^{-1}~")"),
                         x = expression(italic(p)*CO[2]~Treatment~"("~μ*atm~")")) + 
                    theme(axis.text=element_text(size=8),
                          axis.title=element_text(size=8,face="bold")) +
                     stat_summary(fun.y=mean, geom="point", shape=18, size=4, color="black", fill="white") # +
                     # annotate("text", x=2, y=0.000005, size = 4, label = "shapiro wilk = 0.3347") +
                     # annotate("text", x=2, y=0.0000075, size = 4, label = "levene's = ???") +
                     # annotate("text", x=2, y=0.0000115, size = 4, label= paste('DF =',DF,'F =', signif(Fval, digits=3), 'p value =', signif(pval, digits=3), sep=" ")) 
Resp914_Length # print this figure...


# Export the figures to pdf
ggarrange(Resp914_Length,Resp914_Length_reps,nrow = 2) %>%
  ggexport(filename = "C:/Users/samuel.gurr/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/20210914_figs_tables/20210914_respiration_length.pdf")

```


# 9/30/2021 F1 juvenile scallops

**About**

- two pCO2 treatments 

- *before* we culled and started the food limitation trials


#### number of replicates for analysis...

```{r 9/30 replicates, echo=FALSE}

Resp_0930 <- Resp.Master_OM %>% 
  dplyr::filter(Date %in% '9/30/2021')  %>% # call only 9/14
  dplyr::select(-Center) %>% 
  dplyr::mutate(pHxFood = paste(pH,Food, sep = "_")) %>% 
  dplyr::mutate(random_fact = as.factor(paste(Chamber_tank, Food, sep="_")))

kable(Resp_0930 %>% dplyr::group_by(Chamber_tank, Food) %>% dplyr::summarise(n())) # tank replication - lowest value was 2 for 7.5_D unfed

Resp_0930 %>% summarySE(measurevar="resp_µmol_L_mm_Length_hr", groupvars=(c("pH", "Food"))) %>% 
      dplyr::mutate(pCO2 = case_when(pH == 8  ~ "500 μatm", pH == 7.5 ~ "800 μatm"))
```


## 9/30/2021 linear model, diagnostics, and plots

#### Length standardized

```{r 9/30 Length standardized, echo=TRUE, message = FALSE, warning = FALSE}


# Shell length standardized (SL) ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

# Visualize the data with the random effet as treplicate 
Resp930_Length_reps <- ggboxplot(Resp_0930, x = "pHxFood", y = "resp_µmol_L_mm_Length_hr", color = "Replicate",
          add = c("mean_se", "dotplot"),
          palette = c("#00AFBB", "#E7B800", "brown", "grey"))
Resp930_Length_reps

# Two-way ANOVA (without the random effect) 
Resp930_ANOVA <- aov(resp_µmol_L_mm_Length_hr ~ pCO2*Food, data=Resp_0930) # run mod
summary(Resp930_ANOVA) # summary mod
kable(  data.frame(unclass(summary(Resp930_ANOVA)), check.names = FALSE, stringsAsFactors = FALSE)  ) %>%  # print a png of this table
  kable_styling() %>%
  save_kable(file = "C:/Users/samuel.gurr/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/20210930_figs_tables/20210930_resp_TwoWayANOVA_Table.png", zoom = 1.5)
#              Df  Sum Sq  Mean Sq F value  Pr(>F)   
# pCO2         1 0.00154 0.001539   2.094 0.15313   
# Food         1 0.00671 0.006713   9.135 0.00368 **
# pCO2:Food    1 0.00079 0.000786   1.070 0.30516   
# Residuals   60 0.04409 0.000735
shapiro.test(residuals(Resp930_ANOVA)) # NON normal - 0.009643
leveneTest(Resp930_ANOVA) # homogeneity of variance (equal) variance - 0.2709



# Linear mixed effects model with random effect of Replicate
LMEmod_0930<-lme(resp_µmol_L_mm_Length_hr ~ pCO2 * Food, random=~1|Chamber_tank, data=Resp_0930)
# |     &nbsp;      | numDF | denDF | F-value |  p-value  |
# |:---------------:|:-----:|:-----:|:-------:|:---------:|
# | **(Intercept)** |   1   |  54   |  110.5  | 1.144e-14 |
# |    **pCO2**     |   1   |   6   |  1.757  |  0.2333   |
# |    **Food**     |   1   |  54   |  9.367  | 0.003438  | *
# |  **pCO2:Food**  |   1   |  54   |  1.009  |  0.3196   |
pander(anova(LMEmod_0930), style='rmarkdown')
kable(as.data.frame(anova(LMEmod_0930))) %>% 
  kable_styling() %>%
  save_kable(file = "C:/Users/samuel.gurr/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/20210930_figs_tables/20210930_resp_LME_Table.png", zoom = 1.5)
pdf(paste0(filename = "C:/Users/samuel.gurr/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/20210930_figs_tables/20210930_resp_LME_Diagnostics.pdf"))
check_model(LMEmod_0930) 
dev.off()


# plot
Resp930_Length <- ggplot(Resp_0930, aes(x = factor(pCO2, level = c('500 μatm', '800 μatm')), resp_µmol_L_mm_Length_hr , fill = pCO2)) +
              theme(panel.grid=element_blank()) +
              geom_boxplot(size=0.2, width=0.5, alpha=0.1, aes(fill=pCO2)) +
              scale_fill_manual(values=c("white","grey50")) +
              geom_point(shape = 21, size = 2, position = position_jitterdodge(jitter.width = 0.1)) +
              theme_classic() +
              scale_x_discrete(labels= c('~500 μatm', '~800 μatm')) +
              #scale_y_continuous(expand = c(0, 0), limits = c(0, 120)) +
              theme(axis.text=element_text(size=8),
                          axis.title=element_text(size=8,face="bold")) +
              labs(title = "F1 Scallops: respiration rates on 20210930 (shell length stand.)", 
                   y = expression(Respiration~rate~"("~μmol~L^{-1}~O[2]%.%mm^{-1}~shell~length%.% hr^{-1}~")"),
                   x = expression(italic(p)*CO[2]~Treatment~"("~μ*atm~")"))  + 
               stat_summary(fun.y=mean, geom="point", shape=18, size=4, color="black", fill="white") +
               facet_wrap(~factor(Fed_Unfed, level = c('Low food', 'High food')))
Resp930_Length

# Export to pdf
ggarrange(Resp930_Length,Resp930_Length_reps,nrow = 2) %>%
  ggexport(filename = "C:/Users/samuel.gurr/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/20210930_figs_tables/20210930_resp_Figures.pdf")

```


# density plot - Day 64

```{r, Day 92 density respiration plot }
library(dplyr)
library(tidyr)
Resp_0930$pHxFood <- as.factor(Resp_0930$pHxFood)

df_mean <- Resp_0930 %>% 
  dplyr::group_by(pHxFood) %>% 
  dplyr::summarize(average = mean(resp_µmol_L_mm_Length_hr)) %>%
  dplyr::ungroup()
p.box <- ggplot(Resp_0930, aes(x = pHxFood, y = resp_µmol_L_mm_Length_hr)) + geom_boxplot() + geom_point(data= df_mean, mapping = aes(x = pHxFood, y = average),
             color="red") 
p.box.data <- layer_data(p.box) %>%
  select(x, ymin, lower, middle, upper, ymax, outliers, flipped_aes) %>%
  dplyr::rename(mean = flipped_aes) %>% 
  dplyr::mutate(mean  = df_mean$average) %>% 
  mutate(pHxFood = factor(x, labels = levels(Resp_0930$pHxFood), ordered = TRUE)) %>%
  select(-x)


p.box.data %>% unnest(outliers)


denisty_box_resp_64DPF <-ggplot(p.box.data) +
                            # manually plot flipped boxplot
                            geom_segment(aes(x = ymin, xend = ymax, y = -0.15, yend = -0.15)) +
                            geom_rect(aes(xmin = lower, xmax = upper, ymin = -0.3, ymax = 0,  fill = pHxFood),color = "black") +
                            # geom_point(data = . %>% unnest(outliers), aes(x = outliers, y = -0.15), color = "grey60", size = 1) +
                            # vertical lines at Q1 / Q2 / Q3
                            geom_vline(data = . %>% select(pHxFood, lower, mean, upper) %>% gather(key, value, -pHxFood), aes(xintercept = value)) +
                            # density plot
                            geom_density(data = Resp_0930, aes(x = resp_µmol_L_mm_Length_hr, group=pHxFood, fill=pHxFood, ..scaled..), alpha=.4, adjust=1.5) +
                            #  theme
                            theme_classic() +
                            xlim(0, 0.22) +
                            facet_grid(pHxFood ~ .) +
                            theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.position = "none", plot.title = element_text(size=10))+
                            labs(title = "F1 Scallops: respiration rates 64 DPF)", 
                                 x = expression(Respiration~rate~"("~μmol~L^{-1}~O[2]%.%mm^{-1}~shell~length%.% hr^{-1}~")"),
                                 y = "Scaled density") +
                            scale_fill_manual(values=c("grey40", "grey40", "grey85", "grey85"))
denisty_box_resp_64DPF

pdf(paste0(filename = "C:/Users/samuel.gurr/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/20210930_figs_tables/20210930_resp_density_plot.pdf"), width = 5, height = 5)
pdf(paste0(filename = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/20210930_figs_tables/20210930_resp_density_plot.pdf"), width = 5, height = 5)
denisty_box_resp_64DPF # print the model diagnostics 
dev.off()

```

# 10/26/2021 F1 juvenile scallops

**About**

- two pCO2 treatments 

- *before* we culled and started the food limitation trials


#### number of replicates for analysis...

```{r 10/26 replicates, echo=FALSE}

Resp_1026 <- Resp.Master_OM %>% 
  dplyr::filter(Date %in% '10/26/2021')  %>% # call only 10/14
  dplyr::select(-Center) %>% 
  dplyr::mutate(pHxFood = paste(pH,Food, sep = "_")) %>% 
  dplyr::mutate(random_fact = as.factor(paste(Chamber_tank, Food, sep="_")))

kable(Resp_1026 %>% dplyr::group_by(Chamber_tank, Food) %>% dplyr::summarise(n())) # tank replication

Resp_1026 %>% summarySE(measurevar="resp_µmol_L_mm_Length_hr", groupvars=(c("Food","pH"))) %>% 
      dplyr::mutate(pCO2 = case_when(pH == 8  ~ "500 μatm", pH == 7.5 ~ "800 μatm"))
```


### 10/26/2021 Linear mixed-effects models, diagnostics, and plots


#### Length standardized

```{r 10/26 Length standardized, echo=TRUE, message = FALSE, warning = FALSE}

# Shell length standardized (SL) ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

# Visualize the data with the random effet as treplicate 
Res1026_Length_reps <- ggboxplot(Resp_1026, x = "pHxFood", y = "resp_µmol_L_mm_Length_hr", color = "Replicate",
                          add = c("mean_se", "dotplot"),
                          palette = c("#00AFBB", "#E7B800", "brown", "grey"))
Res1026_Length_reps

# ANOVA (wihtout the random effect
summary(aov(resp_µmol_L_mm_Length_hr ~ pCO2 * Food, data=Resp_1026)) # 0.0392 * (pCO2) 0.0499 * (food) - without the random effect of tank)
#             Df Sum Sq Mean Sq F value Pr(>F)  
# pCO2         1 0.0089 0.00888   0.606 0.4428  
# Food         1 0.0815 0.08148   5.562 0.0256 *
# pCO2:Food    1 0.0056 0.00561   0.383 0.5410  
# Residuals   28 0.4102 0.01465  

require(nlme)
# Linear mixed effects model with random effect of Replicate 
LMEmod_1026_SL<-lme(resp_µmol_L_mm_Length_hr ~ pCO2 * Food, random=~1|random_fact, data=Resp_1026)
# |     &nbsp;      | numDF | denDF | F-value |  p-value  |
# |:---------------:|:-----:|:-----:|:-------:|:---------:|
# | **(Intercept)** |   1   |  16   |  77.89  | 1.516e-07 |
# |    **pCO2**     |   1   |  12   | 0.01125 |  0.9173   |
# |    **Food**     |   1   |  12   |  25.58  | 0.0002811 |
# |  **pCO2:Food**  |   1   |  12   |  0.227  |  0.6423   |
pander(anova(LMEmod_1026_SL), style='rmarkdown')
kable(as.data.frame(anova(LMEmod_1026_SL))) %>% 
  kable_styling() %>%
  save_kable(file = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/20211026_figs_tables/20211026_resp_LME_Table.png", zoom = 1.5)
pdf(paste0(filename = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/20211026_figs_tables/20211026_resp_LME_Diagnostics.pdf"))
check_model(LMEmod_1026_SL) 
dev.off()
# tukey posthoc for lmer model
# require('lsmeans')
# lsmeans(LMEmod_1026_SL, pairwise~pCO2 * Food, adjust="tukey") # Compute least-squares means
# $contrasts
#  contrast                         estimate       SE df t.ratio p.value
#  500 µatm fed - 800 µatm fed     -5.74e-05 8.93e-06 12  -6.430  0.0002
#  500 µatm fed - 500 µatm unfed    9.03e-05 9.41e-06 12   9.589  <.0001
#  500 µatm fed - 800 µatm unfed    9.08e-05 9.41e-06 12   9.640  <.0001
#  800 µatm fed - 500 µatm unfed    1.48e-04 8.93e-06 12  16.538  <.0001
#  800 µatm fed - 800 µatm unfed    1.48e-04 8.93e-06 12  16.592  <.0001
 # 500 µatm unfed - 800 µatm unfed  4.82e-07 9.41e-06 12   0.051  0.9999



# call the results of LMER to add to boxplot below 
DF   <- paste( (anova(LMEmod_01026_SL)[[1]])[3], (anova(LMEmod_01026_SL)[[2]])[3], sep = '/') # call DF
Fval <- (anova(LMEmod_01026_SL)[[3]])[3] # call f
pval <- (anova(LMEmod_01026_SL)[[4]])[3] # call p value

# plot
Resp1026_Length <- ggplot(Resp_1026, aes(x = factor(pCO2, level = c('500 μatm', '800 μatm')), resp_µmol_L_mm_Length_hr , fill = pCO2)) +
              theme(panel.grid=element_blank()) +
              geom_boxplot(size=0.2, width=0.5, alpha=0.1, aes(fill=pCO2)) +
              scale_fill_manual(values=c("white","grey50")) +
              geom_point(shape = 21, size = 2, position = position_jitterdodge(jitter.width = 0.1)) +
              theme_classic() +
              scale_x_discrete(labels= c('~500 μatm', '~800 μatm')) +
              # scale_y_continuous(expand = c(0, 0), limits = c(0, 250)) +
              theme(axis.text=element_text(size=8),
                    axis.title=element_text(size=8,face="bold")) +
              labs(title = "F1 Scallops: respiration rates on 20211026 (shell length stand.)", 
                   y = expression(Respiration~rate~"("~μmol~L^{-1}~O[2]%.%mm^{-1}~shell~length%.% hr^{-1}~")"),
                   x = expression(italic(p)*CO[2]~Treatment~"("~μ*atm~")"))  + 
              facet_wrap(~factor(Fed_Unfed, level = c('Low food', 'High food'))) # +
Resp1026_Length


# Export to pdf
ggarrange(Resp1026_Length, Res1026_Length_reps,nrow = 2) %>% 
  ggexport(filename = "C:/Users/samuel.gurr/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/20211026_figs_tables/20211026_resp_Figures.pdf")

```


# density plot - Day 92

```{r, Day 92 density respiration plot }
library(dplyr)
library(tidyr)
Resp_1026$pHxFood <- as.factor(Resp_1026$pHxFood)
Resp_1026$resp_µmol_L_mm_Length_hr.noSCI     <- format(as.numeric(Resp_1026$resp_µmol_L_mm_Length_hr), scientific = FALSE, digits = 3)
Resp_1026$resp_µmol_L_mm_Length_hr.NUM       <- as.numeric(sprintf("%s", Resp_1026$resp_µmol_L_mm_Length_hr.noSCI))

df_mean <- Resp_1026 %>% 
  dplyr::group_by(pHxFood) %>% 
  dplyr::summarize(average = mean(resp_µmol_L_mm_Length_hr.NUM)) %>%
  dplyr::ungroup()
p.box <- ggplot(Resp_1026, aes(x = pHxFood, y = resp_µmol_L_mm_Length_hr.NUM)) + geom_boxplot() + geom_point(data= df_mean, mapping = aes(x = pHxFood, y = average),
             color="red") 
p.box.data <- layer_data(p.box) %>%
  select(x, ymin, lower, middle, upper, ymax, outliers, flipped_aes) %>%
  dplyr::rename(mean = flipped_aes) %>% 
  dplyr::mutate(mean  = df_mean$average) %>% 
  mutate(pHxFood = factor(x, labels = levels(Resp_1026$pHxFood), ordered = TRUE)) %>%
  select(-x)


p.box.data %>% unnest(outliers)


denisty_box_resp_92DPF <-ggplot(p.box.data) +
                            # manually plot flipped boxplot
                            geom_segment(aes(x = ymin, xend = ymax, y = -0.15, yend = -0.15)) +
                            geom_rect(aes(xmin = lower, xmax = upper, ymin = -0.3, ymax = 0,  fill = pHxFood),color = "black") +
                            #geom_point(data = . %>% unnest(outliers), aes(x = outliers, y = -0.15), color = "grey60", size = 1) +
                            # vertical lines at Q1 / Q2 / Q3
                            geom_vline(data = . %>% select(pHxFood, lower, mean, upper) %>% gather(key, value, -pHxFood), aes(xintercept = value)) +
                            # density plot
                            geom_density(data = Resp_1026, aes(x = resp_µmol_L_mm_Length_hr.NUM, group=pHxFood, fill=pHxFood, ..scaled..), alpha=.4, adjust=1.5) +
                            #  theme
                            theme_classic() +
                            facet_grid(pHxFood ~ .) +
                            theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.position = "none", plot.title = element_text(size=10))+
                            labs(title = "F1 Scallops: respiration rates 92 DPF)", 
                                 x = expression(Respiration~rate~"("~μmol~L^{-1}~O[2]%.%mm^{-1}~shell~length%.% hr^{-1}~")"),
                                 y = "Scaled density") +
                            scale_fill_manual(values=c("grey40", "grey40", "grey85", "grey85"))
denisty_box_resp_92DPF

pdf(paste0(filename = "C:/Users/samuel.gurr/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Respiration/20211026_figs_tables/20211026_resp_density_plot.pdf"), width = 5, height = 5)
denisty_box_resp_92DPF # print the model diagnostics 
dev.off()

```
