---
title: "F1 Bay Scallops: High vs. Low food availability under OA conditions"
author: "Samuel Gurr"
date: "10/12/2021"
output:
  pdf_document:
    latex_engine: xelatex
---

<!-- Last updates: october 6, 2021 -->


## Load libraries

```{r startup, include=FALSE}

library(ggplot2)
library(dplyr)
library(tidyverse)
library(car)
library(nlme)
library(multcompView)
library(agricolae)
library(Rmisc)
library(lmerTest)
library(lme4)
library(pander)
library(performance)
library(Rmisc)
library(tidyr)
library(reshape2)
library(rcompanion)
library(kableExtra)
library(ggpubr)
library(tidyr)
library(nlme)
library(car)
library(rcompanion) # to run the Schrier -Ray-Hare non parametric 2 way 
setwd("C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis") # Work computer
# setwd("C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis") # Work computer

```

## Set Path
```{r, include=TRUE}
setwd("C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis") # Work computer

# setwd("C:/Users/samjg/Documents/Github_repositories/Airradians_OA/RAnalysis") # Work computer
# setwd("C:/Users/samuel.gurr/Documents/Github_repositories/Airradians_OA/RAnalysis") # Work computer
length                     <-read.csv(file="Data/Survival_Size/Lengths_master.csv", header = TRUE)
len.dryweight.CI_1026      <-read.csv(file="Data/Survival_Size/20211026_lengths_dryweights.csv", header = TRUE) 
# len.dryweight.CI_1202      <-read.csv(file="Data/Survival_Size/20211202_lengths_dryweights.csv", header = TRUE)


survival_juvenile          <-read.csv(file="C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Data/Survival_Size/Survival_master.csv", header = TRUE)

# Structure of the data - to check that variables are properly assigned to factor or variable
# str(length)

min(length$Length_um/1000) # 1.011402
max(length$Length_um/1000) # 20.36

nrow(length %>% dplyr::filter(Length_um/1000 < 3)) # 1417
```

# First lets plot and run stats on the single time-point data.. (CI and dry shell weight)

## Dry shell weight  (only one time point on Oct 26 2021)

* plot and statistics 

```{r dry shell weight data, analysis, plotting, include=FALSE}
#  ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# DRY SHELL WEIGHT  :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
#  ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::




# call the data (all)
DSW_1026 <- len.dryweight.CI_1026 %>%  
              dplyr::filter(shell_or_tissue %in% 'shell') %>% 
              dplyr::select('Date_sampled','pH','Tank_Replicate',
                            'Dry_Sample_Weight_mg', 'Shell_length_mm','shell_or_tissue') %>% 
              dplyr::mutate(DSW_corrected = (Dry_Sample_Weight_mg/Shell_length_mm) * 100) %>% 
              na.omit() %>%  
              dplyr::mutate(pCO2 = case_when(pH == 8  ~ "500 μatm", pH == 7.5 ~ "800 μatm")) 

DSW_1026$pCO2 <- as.factor(DSW_1026$pCO2)


# call the data (means)
DSW_1026_means <- len.dryweight.CI_1026 %>%  
                    dplyr::filter(shell_or_tissue %in% 'shell') %>% 
                    dplyr::select('Date_sampled','pH','Tank_Replicate',
                                  'Dry_Sample_Weight_mg', 'Shell_length_mm','shell_or_tissue') %>% 
                    dplyr::mutate(DSW_corrected = (Dry_Sample_Weight_mg/Shell_length_mm) * 100) %>% 
                    na.omit() %>% 
                    summarySE(measurevar="DSW_corrected", groupvars=c("Tank_Replicate","pH")) %>% 
                        dplyr::mutate(pCO2 = case_when(pH == 8  ~ "500 μatm", pH == 7.5 ~ "800 μatm")) %>%
                        dplyr::mutate(Age = 92)

DSW_1026_means$pCO2 <- as.factor(DSW_1026_means$pCO2)

# plot the means 
ggplot(data=DSW_1026_means, aes(x=pCO2, y=DSW_corrected, color=Tank_Replicate)) +
  geom_line( stat = "identity", size=1.0)+
  geom_point(position=position_dodge(.5))+ 
  # scale_color_manual(values=c("forestgreen","darkorange2"))+
  geom_errorbar(aes(ymin=DSW_corrected-se, ymax=DSW_corrected+se), width=.2,
                position=position_dodge(.5))+
  theme_classic() +  
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  scale_y_continuous(name ="Dry shell weight (g)")+
  theme(text = element_text(size=15))

# one-way ANOVA
AOV_DSW <- aov(DSW_corrected ~  pCO2,  
              data=DSW_1026_means) # run mod
# check model assumptions
shapiro.test(residuals(AOV_DSW)) # normal - 0.5211
leveneTest(AOV_DSW) # homogeneity of variance (equal variance) - 0.04778 *
# need to run the non-parametric Kruskal Wallis
KW_DSW <- kruskal.test(DSW_corrected ~ pCO2, data = DSW_1026_means) # run mod
# all is good, lets see the results
pander(print(KW_DSW), style='rmarkdown') # table for SRH test
# | Test statistic | df |  P value   |
# |:--------------:|:--:|:----------:|
# |     5.333      | 1  | 0.02092  * |
DSW_1026_means %>% summarySE(measurevar="DSW_corrected", groupvars= c("pCO2"))  # view summary means 
((0.6845062- 0.3850634) / 0.6845062) * 100 # 43.74581 % difference 


# DENSITY PLOT 



df_mean <- DSW_1026 %>% 
  dplyr::group_by(pCO2) %>% 
  dplyr::summarize(average = mean(DSW_corrected)) %>%
  dplyr::ungroup()

p.box <- ggplot(DSW_1026, aes(x = pCO2, y = (DSW_corrected))) + 
  geom_boxplot() + 
  geom_point(data= df_mean, 
             mapping = aes(x = pCO2, y = (average)),
             color="red") 

p.box.data <- layer_data(p.box) %>%
  select(x, ymin, lower, middle, upper, ymax, outliers, flipped_aes) %>%
  dplyr::rename(mean = flipped_aes) %>% 
  dplyr::mutate(mean  = (df_mean$average)) %>% 
  mutate(pCO2 = factor(x, labels = levels(DSW_1026$pCO2), ordered = TRUE)) %>%
  select(-x)

denisty_box_DSW <-ggplot(p.box.data) +
                            # manually plot flipped boxplot
                            geom_segment(aes(x = ymin, xend = ymax, y = -0.2, yend = -0.2)) +
                            geom_rect(aes(xmin = lower, xmax = upper, ymin = -0.25, 
                                          ymax = -0.15,  fill = pCO2),color = "black") +
                            geom_point(data = . %>% unnest(outliers), 
                                       aes(x = outliers, y = -0.2), color = "grey60", size = 1) +
                            # vertical lines at Q1 / Q2 / Q3
                            geom_vline(data = . %>% select(pCO2, lower, mean, upper) %>% 
                                         gather(key, value, -pCO2), aes(xintercept = value)) +
                            # density plot
                            geom_density(data = DSW_1026, aes(x = DSW_corrected, fill=pCO2, ..scaled..), alpha=.4) +
                            #  theme
                            theme_classic() +
                            xlim(0, 1.5) +
                            facet_grid(pCO2 ~ .) +
                            theme(panel.grid.major = element_blank(), 
                                  panel.grid.minor = element_blank(), 
                                  legend.position = "none", plot.title = element_text(size=10))+
                            labs(x = "Dry shell weight (g)", y = "frequency")  +
                            scale_fill_manual(values=c("grey85", "grey40"))
denisty_box_DSW
# export the plot
pdf(paste0(filename = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Survival_size/20211026_figs_table/20211026_DSW_density_plot.pdf"), width = 4, height = 4)
denisty_box_DSW # print the model diagnostics 
dev.off()

```


## Dry tissue weight  (only one time point on Oct 26 2021)

* plot and statistics 

```{r dry tissue weight data, analysis, plotting, include=FALSE}
#  ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# DRY TISSUE WEIGHT  :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
#  ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::




# call the data (all)
DTW_1026 <- len.dryweight.CI_1026 %>%  
              dplyr::filter(shell_or_tissue %in% 'tissue') %>% 
              dplyr::select('Date_sampled','pH','Tank_Replicate',
                            'Dry_Sample_Weight_mg', 'Shell_length_mm','shell_or_tissue') %>% 
              dplyr::mutate(DTW_corrected = (Dry_Sample_Weight_mg/Shell_length_mm) * 100) %>% 
              dplyr::mutate(pCO2 = case_when(pH == 8  ~ "500 μatm", pH == 7.5 ~ "800 μatm")) %>%
              na.omit()
DTW_1026$pCO2 <- as.factor(DTW_1026$pCO2)

# call the data (means)
DTW_1026_means <- DTW_1026 %>% 
                    dplyr::mutate(DTW_corrected = (Dry_Sample_Weight_mg/Shell_length_mm) * 100) %>% 
                    na.omit() %>% 
                    summarySE(measurevar="DTW_corrected", groupvars=c("Tank_Replicate","pH")) %>% 
                        dplyr::mutate(pCO2 = case_when(pH == 8  ~ "500 μatm", pH == 7.5 ~ "800 μatm")) %>%
                        dplyr::mutate(Age = 92)

DTW_1026_means$pCO2 <- as.factor(DTW_1026_means$pCO2)

# plot the means 
ggplot(data=DTW_1026_means, aes(x=pCO2, y=DTW_corrected, color=Tank_Replicate)) +
  geom_line( stat = "identity", size=1.0)+
  geom_point(position=position_dodge(.5))+ 
  # scale_color_manual(values=c("forestgreen","darkorange2"))+
  geom_errorbar(aes(ymin=DTW_corrected-se, ymax=DTW_corrected+se), width=.2,
                position=position_dodge(.5))+
  theme_classic() +  
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  scale_y_continuous(name ="Dry tissue weight (g)")+
  theme(text = element_text(size=15))

# one-way ANOVA
AOV_DTW <- aov(DTW_corrected ~  pCO2,  
              data=DTW_1026_means) # run mod
# check model assumptions
shapiro.test(residuals(AOV_DTW)) # normal - 0.1213
leveneTest(AOV_DTW) # homogeneity of variance (equal variance) - 0.1828
# all is good, lets see the results
pander(print(AOV_DTW), style='rmarkdown') # table for SRH test
# |    &nbsp;     | Df |  Sum Sq  | Mean Sq  | F value | Pr(>F)  |
# |:-------------:|:--:|:--------:|:--------:|:-------:|:-------:|
# |   **pCO2**    | 1  | 0.001446 | 0.001446 |  4.504  | 0.07805 |
# | **Residuals** | 6  | 0.001926 | 0.000321 |   NA    |   NA    |
DTW_1026_means %>% summarySE(measurevar="DTW_corrected", groupvars= c("pCO2"))  # view summary means 
# 500 μatm	4	0.06948337	0.025053597	0.012526799	
# 800 μatm	4	0.04259740	0.003785095	0.001892548	
((0.06948337- 0.04259740) / 0.06948337) * 100 # 38.69411 % difference 


# DENSITY PLOT 


df_mean <- DTW_1026 %>% 
  dplyr::group_by(pCO2) %>% 
  dplyr::summarize(average = mean(DTW_corrected)) %>%
  dplyr::ungroup()

p.box <- ggplot(DTW_1026, aes(x = pCO2, y = (DTW_corrected))) + 
  geom_boxplot() + 
  geom_point(data=df_mean, 
             mapping = aes(x = pCO2, y = (average)),
             color="red") 

p.box.data <- layer_data(p.box) %>%
  select(x, ymin, lower, middle, upper, ymax, outliers, flipped_aes) %>%
  dplyr::rename(mean = flipped_aes) %>% 
  dplyr::mutate(mean  = (df_mean$average)) %>% 
  mutate(pCO2 = factor(x, labels = levels(DTW_1026$pCO2), ordered = TRUE)) %>%
  select(-x)

denisty_box_DTW <-ggplot(p.box.data) +
                            # manually plot flipped boxplot
                            geom_segment(aes(x = ymin, xend = ymax, y = -0.2, yend = -0.2)) +
                            geom_rect(aes(xmin = lower, xmax = upper, 
                                          ymin = -0.25, ymax = -0.15,  
                                          fill = pCO2),color = "black") +
                            geom_point(data = . %>% unnest(outliers), aes(x = outliers, y = -0.2), 
                                       color = "grey60", size = 1) +
                            # vertical lines at Q1 / Q2 / Q3
                            geom_vline(data = . %>% select(pCO2, lower, mean, upper) %>% 
                                         gather(key, value, -pCO2), aes(xintercept = value)) +
                            # density plot
                            geom_density(data = DTW_1026, 
                                         aes(x = DTW_corrected, fill=pCO2, ..scaled..), alpha=.4) +
                            #  theme
                            theme_classic() +
                            xlim(0, 0.2) +
                            facet_grid(pCO2 ~ .) +
                            theme(panel.grid.major = element_blank(), 
                                  panel.grid.minor = element_blank(), 
                                  legend.position = "none", 
                                  plot.title = element_text(size=10))+
                            labs(x = "Dry shell weight (g)", y = "frequency")  +
                            scale_fill_manual(values=c("grey85", "grey40"))
denisty_box_DTW
# export the plot
pdf(paste0(filename = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Survival_size/20211026_figs_table/20211026_DTW_density_plot.pdf"), width = 4, height = 4)
denisty_box_DTW # print the model diagnostics 
dev.off()

```

## Condition Index (only one time point on Oct 26 2021)

* plot and statistics 

```{r Condition index data, statistics, plotting, include=FALSE}


#  ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# CONDITION INDEX :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
#  ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::


# call the data (all)
CI_1026 <- len.dryweight.CI_1026[!is.na(len.dryweight.CI_1026$AFDW),] %>% 
            dplyr::select(c('pH','Tank_Replicate', "Shell_length_mm", "AFDW")) %>% 
            dplyr::mutate(random_eff = (as.factor(paste(pH,Tank_Replicate, sep ='_')))) %>% 
            dplyr::mutate(pH_Age = (as.factor(paste(pH, sep = '_')))) %>% 
            dplyr::mutate(pCO2 = case_when(pH == 8  ~ "500 μatm", pH == 7.5 ~ "800 μatm")) %>% 
            dplyr::mutate(CI = (AFDW/Shell_length_mm)*100 ) %>% 
            dplyr::filter(CI > 0) # some negatieve AFDW values - error

CI_1026$pCO2 <- as.factor(CI_1026$pCO2)

# call the data (means)
CI_1026_means <- CI_1026 %>%summarySE(measurevar="CI", groupvars=c("Tank_Replicate","pCO2"))

CI_1026_means$pCO2 <- as.factor(CI_1026_means$pCO2)

# plot the means 
ggplot(data=CI_1026_means, 
       aes(x=pCO2, y=CI, color=Tank_Replicate)) +
        geom_line( stat = "identity", size=1.0)+
        geom_point(position=position_dodge(.5))+ 
        # scale_color_manual(values=c("forestgreen","darkorange2"))+
        geom_errorbar(aes(ymin=CI-se, ymax=CI+se), width=.2,
                      position=position_dodge(.5))+
        theme_classic() +  
        theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
        scale_y_continuous(name ="Condition index [(Dry tissue / dry shell) *100]")+
        theme(text = element_text(size=15))

# one-way ANOVA
AOVCI <- aov(CI ~ 
               pCO2, 
             data=CI_1026_means) # run mod
# check model assumptions
shapiro.test(residuals(AOVCI)) # non - normal - 0.395
leveneTest(AOVCI) # homogeneity of variance (equal variance) - 0.36 .
summary(AOVCI)
#             Df    Sum Sq   Mean Sq F value Pr(>F)
# pCO2         1 0.0006467 0.0006467    3.64  0.105
# Residuals    6 0.0010661 0.0001777 
CI_1026_means %>% summarySE(measurevar="CI", groupvars= c("pCO2"))  # view summary means 
((11.30190- 10.15005) / 11.30190) * 100 # 10.19165 % difference 



# DENSITY PLOT 


df_mean <- CI_1026 %>% 
              dplyr::group_by(pCO2) %>% 
              dplyr::summarize(average = mean(CI)) %>%
              dplyr::ungroup()

p.box <- ggplot(CI_1026, aes(x = pCO2, y = (CI))) + 
              geom_boxplot() + 
              geom_point(data= df_mean, 
                         mapping = aes(x = pCO2, y = (average)),
                         color="red") 

p.box.data <- layer_data(p.box) %>%
                  select(x, ymin, lower, middle, upper, ymax, outliers, flipped_aes) %>%
                  dplyr::rename(mean = flipped_aes) %>% 
                  dplyr::mutate(mean  = (df_mean$average)) %>% 
                  mutate(pCO2 = factor(x, labels = levels(CI_1026$pCO2), ordered = TRUE)) %>%
                  select(-x)

denisty_box_CI <-ggplot(p.box.data) +
                            # manually plot flipped boxplot
                            geom_segment(aes(x = ymin, xend = ymax, y = -0.2, yend = -0.2)) +
                            geom_rect(aes(xmin = lower, xmax = upper, ymin = -0.25, ymax = -0.15,  fill = pCO2),color = "black") +
                            geom_point(data = . %>% unnest(outliers), aes(x = outliers, y = -0.2), color = "grey60", size = 1) +
                            # vertical lines at Q1 / Q2 / Q3
                            geom_vline(data = . %>% select(pCO2, lower, mean, upper) %>% gather(key, value, -pCO2), aes(xintercept = value)) +
                            # density plot
                            geom_density(data = CI_1026, aes(x = CI, fill=pCO2, ..scaled..), alpha=.4) +
                            #  theme
                            theme_classic() +
                            #xlim(5, 25) +
                            facet_grid(pCO2 ~ .) +
                            theme(panel.grid.major = element_blank(), 
                                  panel.grid.minor = element_blank(), 
                                  legend.position = "none", plot.title = element_text(size=10))+
                            labs(x = "Condition Index", y = "frequency")  +
                            scale_fill_manual(values=c("grey85", "grey40"))
denisty_box_CI
# export the plot
pdf(paste0(filename = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Survival_size/20211026_figs_table/20211026_CI_density_plot.pdf"), width = 4, height = 4)
denisty_box_CI # print the model diagnostics 
dev.off()





```


# Food limitation x pCO2 experiment (50 - 92 dpf)

## Growth rate 

* animals at '51 DPF' were reared under low and high pCO2 BUT were not split to low and high food yet, 
this is our time 'zero' to correct the subseuent timepoints (wihtin pCO2) for a growth rate calculation 

* Example: 400 uatm at 51 DPF is the first growth value for all subseqnt DPF under 400 uatm - oth at high and low food

```{r, Shell growth rate}
# Length ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

Length_Means <- summarySE(length, measurevar="Length_um", groupvars=c("Age_DPF", "pH", "Fed_Unfed"))
Length_Means <- Length_Means %>% 
                dplyr::mutate(pCO2 = case_when(pH == 8 ~ "500 μatm",  pH == 7.5 ~ "800 μatm")) %>% 
                dplyr::mutate(Fed_Unfed = case_when(Fed_Unfed == "fed" ~ "High food",  
                                                    Fed_Unfed == "unfed" ~ "Low food"))

Length_Means_byTank  <- summarySE(length, measurevar="Length_um", 
                                  groupvars=c("Age_DPF", "pH", "Fed_Unfed", "Replicate")) %>% 
                          dplyr::mutate(pCO2 = case_when(pH == 8 ~ "500 μatm",  pH == 7.5 ~ "800 μatm")) %>% 
                          dplyr::mutate(Fed_Unfed = case_when(Fed_Unfed == "fed" ~ "High food",  
                                                              Fed_Unfed == "unfed" ~ "Low food"))

Length_Means_byTank %>% dplyr::filter(Age_DPF %in% 51) # these are the mean shell lengths we want to use to subtract from av lengths within pCO2

Av_7.5FedA <- (Length_Means_byTank %>% dplyr::filter(Age_DPF %in% 51))[1,6] # pH 7.5 Rep (tank) A
Av_7.5FedB <- (Length_Means_byTank %>% dplyr::filter(Age_DPF %in% 51))[2,6] # pH 7.5 Rep (tank) B
Av_7.5FedC <- (Length_Means_byTank %>% dplyr::filter(Age_DPF %in% 51))[3,6] # pH 7.5 Rep (tank) C
Av_7.5FedD <- (Length_Means_byTank %>% dplyr::filter(Age_DPF %in% 51))[4,6] # pH 7.5 Rep (tank) D

Av_8.0FedA <- (Length_Means_byTank %>% dplyr::filter(Age_DPF %in% 51))[5,6] # pH 8.0 Rep (tank) A
Av_8.0FedB <- (Length_Means_byTank %>% dplyr::filter(Age_DPF %in% 51))[6,6] # pH 8.0 Rep (tank) B
Av_8.0FedC <- (Length_Means_byTank %>% dplyr::filter(Age_DPF %in% 51))[7,6] # pH 8.0 Rep (tank) C
Av_8.0FedD <- (Length_Means_byTank %>% dplyr::filter(Age_DPF %in% 51))[8,6] # pH 8.0 Rep (tank) D

Growth_rate <- Length_Means_byTank %>% 
                  dplyr::mutate(Start_Length_um = 
                                  case_when( (pH == 7.5 & Replicate == 'A') ~ Av_7.5FedA, # pH = 7.5, insert this starting length value 
                                             (pH == 7.5 & Replicate == 'B') ~ Av_7.5FedB, # Note: two conditional case_when statements apply BOTH with & and inside ()
                                             (pH == 7.5 & Replicate == 'C') ~ Av_7.5FedC,
                                             (pH == 7.5 & Replicate == 'D') ~ Av_7.5FedD,
                                             
                                             (pH == 8.0 & Replicate == 'A') ~ Av_8.0FedA,
                                             (pH == 8.0 & Replicate == 'B') ~ Av_8.0FedB,
                                             (pH == 8.0 & Replicate == 'C') ~ Av_8.0FedC,
                                             (pH == 8.0 & Replicate == 'D') ~ Av_8.0FedD)) %>% # pH = 7.5, insert this starting length value 
                  dplyr::mutate(Growth_rate_umperday = 
                                  (Length_um - Start_Length_um) / (Age_DPF - 51)) %>% 
                  dplyr::filter(!(Age_DPF %in% 51)) %>%  # we no longer need this first time point of length - just == zero for growth!
                  dplyr::select(!c(N,sd,se,ci)) # cut down necessary columns - however remember the N was 4, a mean from each replicate tank mean


# STATISTICS

## 64 DPF
Growth_rate_64DPF <- Growth_rate %>% dplyr::filter(Age_DPF %in% 64) # the data 
GR_DPF64_MOD      <- lm(Growth_rate_umperday ~ pCO2*Fed_Unfed,data=Growth_rate_64DPF)
shapiro.test(resid(GR_DPF64_MOD)) # 0.3609 normal
leveneTest(GR_DPF64_MOD) # 0.02278 * -  homogeneity of variance FAILED
GR_DPF64_MOD_SRH  <- scheirerRayHare(Growth_rate_umperday ~ pCO2*Fed_Unfed,data=Growth_rate_64DPF)
GR_DPF64_MOD_SRH # food effect 
#                 Df Sum Sq       H p.value
# pCO2            1      1  0.0441 0.83363
# Fed_Unfed       1    256 11.2941 0.00078
# pCO2:Fed_Unfed  1      4  0.1765 0.67442
summarySE(Growth_rate_64DPF, measurevar="Growth_rate_umperday", groupvars=c("Fed_Unfed"))
# High food	98.800270	+- 5.802124 (SE) - um per day
# Low food	-3.658014 +- 3.113321 (SE) - um per day

## 92 DPF
Growth_rate_92DPF <- Growth_rate %>% dplyr::filter(Age_DPF %in% 92) # the data 
GR_DPF92_MOD      <- lm(Growth_rate_umperday ~ pCO2*Fed_Unfed,data=Growth_rate_92DPF)
shapiro.test(resid(GR_DPF92_MOD)) # 0.3329 normal
leveneTest(GR_DPF92_MOD) # 0.09306 -  homogeneity of variance PASS
summary(aov(GR_DPF92_MOD)) # food effect
#                 Df Sum Sq Mean Sq F value   Pr(>F)    
# pCO2            1     31      31   0.178    0.680    
# Fed_Unfed       1  76696   76696 439.801 8.01e-11 ***
# pCO2:Fed_Unfed  1     41      41   0.233    0.638    
# Residuals      12   2093     174 
summarySE(Growth_rate_92DPF, measurevar="Growth_rate_umperday", groupvars=c("Fed_Unfed"))
# High food	158.14751	+- 5.690852 (SE) - um per day
# Low food	19.67748 +- 2.502746 (SE) - um per day

# PLOTTING

Growth_rate_Means_byTreat <- summarySE(Growth_rate, measurevar="Growth_rate_umperday", 
                                       groupvars=c("Age_DPF", "pH", "pCO2", "Fed_Unfed"))
Growth_rate_Means_byTreat


GrowthRate_Means_plot <- ggplot(data=Growth_rate_Means_byTreat, 
                                aes(x=Age_DPF, y=(Growth_rate_umperday/1000), color=pCO2)) +
                            geom_line(aes(linetype = factor(Fed_Unfed)), size = 0.5) +  
                            geom_point()+ 
                            scale_color_manual(values=c("black","black")) +
                            geom_errorbar(aes(ymin=(Growth_rate_umperday/1000)-(se/1000), 
                                              ymax=(Growth_rate_umperday/1000)+(se/1000)), width=.2,
                                          position=position_dodge(.1))+
                            theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
                            scale_x_continuous(name ="Age (days)") +
                            scale_y_continuous(name ="Shell growth rate (mm per day)")  + 
                            scale_linetype_manual(values = c("High food" = "solid", "Low food" = "dashed"))  +
                            theme_classic() +
                            #theme(legend.position="none") +
                            # facet_wrap(~factor(Fed_Unfed, level = c('Low food', 'High food'))) 
                            facet_wrap(~pCO2)
GrowthRate_Means_plot


GrowthRate_Means_plot_D92 <- Growth_rate_Means_byTreat %>% 
                                dplyr::filter(Age_DPF %in% 92) %>% 
                                ggplot(aes(x=Age_DPF, y=(Growth_rate_umperday/1000), color=pCO2)) +
                                geom_line(aes(linetype = factor(Fed_Unfed)), size = 0.5) +  
                                geom_point()+ 
                                scale_color_manual(values=c("black","black")) +
                                geom_errorbar(aes(ymin=(Growth_rate_umperday/1000)-(se/1000), 
                                                  ymax=(Growth_rate_umperday/1000)+(se/1000)), width=.2,
                                              position=position_dodge(.1))+
                                theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
                                scale_x_continuous(name ="Age (days)") +
                                scale_y_continuous(name ="Shell growth rate (mm per day)")  + 
                                scale_linetype_manual(values = c("High food" = "solid", "Low food" = "dashed"))  +
                                theme_classic() +
                                #theme(legend.position="none") +
                                # facet_wrap(~factor(Fed_Unfed, level = c('Low food', 'High food'))) 
                                facet_wrap(~pCO2)
GrowthRate_Means_plot_D92


```



# PLOTTING  (survival + shell size)

## Survival plot (all)

* Note: this experiment only included the low and moderate pCO2 due to low survivorship in the high pCO2 condition 

```{r foodxpCO2 survival mean SE plots}

#First make calculations for means and standard erro
survival_juvenile$Fed_Unfed <-  as.factor(gsub("^(?:[^_]+_){2}([^_]+).*", "\\1", survival_juvenile$trt))
levels(survival_juvenile$Fed_Unfed) <- c("High food", "Low food")


survival_juvenile$pCO2 <-  as.factor(gsub("^(?:[^_]+_){1}([^_]+).*", "\\1", survival_juvenile$trt))
levels(survival_juvenile$pCO2) <- c("800 μatm", "500 μatm")

# Survival ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

Survival_Means <- summarySE(survival_juvenile, measurevar="Survival", groupvars=c("Age_DPF", "pCO2", "Fed_Unfed")) 
Survival_Means$pCO2 <- factor(Survival_Means$pCO2, c("500 μatm","800 μatm"))

dodge <- position_dodge(.50)
## Use geom_line and geom_point to plot over time
Survival_All_plot <- ggplot(data=Survival_Means, aes(x=Age_DPF, y=Survival, color=pCO2)) +
                        #geom_line(aes(linetype = factor(Fed_Unfed)), size = c(0.2, 0.2,0.2, 1,1, 1, 0.2, 0.2,0.2,1,1, 1)) +
                        geom_line(aes(linetype = factor(Fed_Unfed)), size = 0.5) +  
                        #geom_point(position = position_jitterdodge(jitter.width = 10)) +
                        geom_point(position = position_dodge(width=10)) +
                        #scale_color_manual(values=c("forestgreen","darkorange2")) +
                        #scale_color_manual(values=c("black","black")) +
                        scale_color_manual(values=c("forestgreen","darkorange2"))+
                        geom_errorbar(aes(ymin=Survival-se, ymax=Survival+se), width=.2,
                                      position=position_dodge(width=10))+
                        theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
                        scale_x_continuous(name ="Age (days)") +
                        scale_y_continuous(name ="Survival (%)")  + 
                        scale_linetype_manual(values = c("High food" = "solid", "Low food" = "dashed"))  +
                        theme_classic() +
                        theme(legend.position="none") +
                        # facet_wrap(~factor(Fed_Unfed, level = c('Low food', 'High food'))) 
                        facet_wrap(~pCO2)
Survival_All_plot
pdf(paste0("C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Survival_size/Juvenile_survival_FoodxOA.pdf"), width = 8, height = 6)
Survival_All_plot
dev.off()

```

##  Shell length plot (all)

```{r foodxpCO2 shell size  mean SE plots}
# Length ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::

# Use 'Length_Means' summary data in the growth rate chunk above

## Use geom_line and geom_point to plot over time
Length_All_plot <- ggplot(data=Length_Means, aes(x=Age_DPF, y=(Length_um/1000), color=pCO2)) +
  geom_line(aes(linetype = factor(Fed_Unfed)), size = 0.5) +  
  geom_point()+ 
  scale_color_manual(values=c("black","black")) +
  geom_errorbar(aes(ymin=(Length_um/1000)-(se/1000), ymax=(Length_um/1000)+(se/1000)), width=.2,
                position=position_dodge(.1))+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+ 
  scale_x_continuous(name ="Age (days)") +
  scale_y_continuous(name ="Shell length (mm)")  + 
  scale_linetype_manual(values = c("High food" = "solid", "Low food" = "dashed"))  +
  theme_classic() +
  theme(legend.position="none") +
  # facet_wrap(~factor(Fed_Unfed, level = c('Low food', 'High food'))) 
  facet_wrap(~pCO2)
Length_All_plot
pdf(paste0("C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Survival_size/Juvenile_length_FoodxOA.pdf"))
Length_All_plot
dev.off()

```


# STATISTICS (survival + shell size)


## 9/14/2021 F1 juvenile scallops (50 DPF; Day 0)

**About**

- two pCO2 treatments 

- **before** we culled and started the food limitation trials

```{r, Day 50 length - no survival data started the same!}
# call the data fro 50 DPF
data_51 <- length %>%
              filter(Age_DPF=="51") %>%
              dplyr::mutate(pCO2 = case_when(pH == 8 ~ "500 μatm",  pH == 7.5 ~ "800 μatm")) %>% 
              dplyr::mutate(Fed_Unfed = 
                              case_when(Fed_Unfed == "fed" ~ "High food",  
                                        Fed_Unfed == "unfed" ~ "Low food")) %>% 
              dplyr::mutate(random_fact = 
                              as.factor(paste(pCO2,Replicate, sep = "_")))

data_51_AVG <- data_51 %>% 
                    summarySE(measurevar="Length_um", 
                              groupvars= c("Replicate","Fed_Unfed","pCO2"))

# plot the replicates (visual diagnostics of random factor)
Length914_reps<- ggboxplot(data_51, x = "pCO2", y = "Length_um", color = "Replicate",
                              add = c("mean_se", "dotplot"),
                              palette = c("#00AFBB", "#E7B800", "brown", "grey"))
Length914_reps

# One-way ANOVA (without the random effect) 
AOV914.length <- aov(Length_um ~ 
                       pCO2, 
                     data=data_51_AVG) # run mod
# check model assumptions
shapiro.test(residuals(AOV914.length)) # normal - 0.3891
leveneTest(AOV914.length) # homogeneity of variance (equal variance) - 0.2817
summary(AOV914.length)
#             Df Sum Sq Mean Sq F value Pr(>F)
# pCO2         1   9318    9318   0.229  0.649
# Residuals    6 243918   40653

data_51_AVG %>% summarySE(measurevar="Length_um", 
                              groupvars= c("Fed_Unfed","pCO2"))

# High food	500 μatm	4	2390.269	262.0468	131.02342	
# High food	800 μatm	4	2322.011	112.4159	56.20797	

# plot
Length914 <- ggplot(data_51, aes(x = factor(pCO2, level = c('500 μatm', '800 μatm')), (Length_um/1000) , fill = pCO2)) +
                    theme(panel.grid=element_blank()) +
                    geom_boxplot(size=0.2, width=0.5, alpha=0.1, aes(fill=pCO2)) +
                    scale_fill_manual(values=c("white","grey50")) +
                    geom_point(shape = 21, size = 1, position = position_jitterdodge(jitter.width = 0.25)) +
                    theme_classic() +
                    scale_x_discrete(labels= c('~500 μatm', '~800 μatm')) +
                    ylim(0, 22) +
                    labs(title = "F1 Scallops: Shell length 50 DPF", 
                         y = expression(Shell~length~"("~mm~")"),
                         x = expression(italic(p)*CO[2]~Treatment~"("~μ*atm~")")) + 
                    theme(axis.text=element_text(size=8),
                          axis.title=element_text(size=8,face="bold")) +
                     stat_summary(fun.y=mean, geom="point", shape=18, size=4, color="black", fill="white")
Length914 # print this figure...

# Export the figures to pdf
ggarrange(Length914,Length914_reps,nrow = 2) %>%
  ggexport(filename = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Survival_size/20210914_figs_table/20210914_length.pdf")
```

```{r, Day 64 density length plot }


data_51$pCO2 <- as.factor(data_51$pCO2)
df_mean <- data_51 %>% 
  dplyr::group_by(pCO2) %>% 
  dplyr::summarize(average = mean(Length_um)) %>%
  dplyr::ungroup()
p.box <- ggplot(data_51, aes(x = pCO2, y = (Length_um/1000))) + geom_boxplot() + geom_point(data= df_mean, mapping = aes(x = pCO2, y = (average/1000)),
             color="red") 
p.box.data <- layer_data(p.box) %>%
  select(x, ymin, lower, middle, upper, ymax, outliers, flipped_aes) %>%
  dplyr::rename(mean = flipped_aes) %>% 
  dplyr::mutate(mean  = (df_mean$average/1000)) %>% 
  mutate(pCO2 = factor(x, labels = levels(data_51$pCO2), ordered = TRUE)) %>%
  select(-x)

denisty_box_length_50DPF <-ggplot(p.box.data) +
                            # manually plot flipped boxplot
                            geom_segment(aes(x = ymin, xend = ymax, y = -0.2, yend = -0.2)) +
                            geom_rect(aes(xmin = lower, xmax = upper, ymin = -0.25, ymax = -0.15,  fill = pCO2),color = "black") +
                            geom_point(data = . %>% unnest(outliers), 
                                       aes(x = outliers, y = -0.2), color = "grey60", size = 1) +
                            # vertical lines at Q1 / Q2 / Q3
                            geom_vline(data = . %>% select(pCO2, lower, mean, upper) %>% 
                                         gather(key, value, -pCO2), aes(xintercept = value)) +
                            # density plot
                            geom_density(data = data_51, aes(x = (Length_um/1000), fill=pCO2, ..scaled..), alpha=.4) +
                            #  theme
                            theme_classic() +
                            xlim(0, 5) +
                            facet_grid(pCO2 ~ .) +
                            theme(panel.grid.major = element_blank(), 
                                  panel.grid.minor = element_blank(), 
                                  legend.position = "none", 
                                  plot.title = element_text(size=10))+
                            labs(x = "Shell length", y = "frequency")  +
                            scale_fill_manual(values=c("grey85", "grey40"))
denisty_box_length_50DPF
# export the plot
pdf(paste0(filename = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Survival_size/20210914_figs_table/20210914_length_density_plot.pdf"), width = 5, height = 5)
denisty_box_length_50DPF # print the model diagnostics 
dev.off()
```








# 9/30/2021 F1 juvenile scallops (64 DPF; Day 14)

```{r, Day 64 data}


# Shell length ::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# length data 
data_64_length <- length %>%
                    filter(Age_DPF=="64") %>%
                    dplyr::mutate(pCO2 = case_when(pH == 8 ~ "500 μatm",  pH == 7.5 ~ "800 μatm")) %>% 
                    dplyr::mutate(Fed_Unfed = case_when(Fed_Unfed == "fed" ~ "High food",  Fed_Unfed == "unfed" ~ "Low food")) %>% 
                    dplyr::mutate(random_fact = as.factor(paste(pCO2,Replicate,Fed_Unfed, sep = "_")))

data_64_AVG.length <- data_64_length %>%  
                      summarySE(measurevar="Length_um", 
                                groupvars= c("Replicate","pCO2", "Fed_Unfed"))  # view summary means 

# run model
AOV930.length = aov(Length_um ~ 
                           pCO2 * Fed_Unfed, 
                         data=data_64_AVG.length)
leveneTest(AOV930.length) # 0.2602
shapiro.test(resid(AOV930.length)) # 0.1051
summary(AOV930.length)
#                Df  Sum Sq Mean Sq F value   Pr(>F)    
# pCO2            1    6094    6094   0.094    0.765    
# Fed_Unfed       1 7096445 7096445 108.939 2.25e-07 ***
# pCO2:Fed_Unfed  1    6106    6106   0.094    0.765    
# Residuals      12  781694   65141
(summary(AOV930.length))
# all is good, lets see the results
kable(unclass(print(summary(AOV930.length)))) %>%  # print a png of this table
  save_kable(file = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Survival_size/20210930_figs_table/20210930_length_AOV_Table.pdf")


# percent difference
# data_64_survival %>% dplyr::group_by(pCO2) %>% dplyr::summarise(mean = mean(Survival))
# data_64_survival %>% dplyr::group_by(trt) %>% dplyr::summarise(mean = mean(Survival))
data_64_AVG.length %>%  dplyr::mutate(Length_mm = Length_um/1000) %>% summarySE(measurevar="Length_mm", groupvars= c("Fed_Unfed"))  # view summary means 
((3.640543-2.308585) / 3.640543) * 100 # 36.58679 % greater shell length under high food availability


# Survival:::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::


data_64_survival <- survival_juvenile %>%
                    dplyr::filter(Age_DPF=="64") %>% 
                    dplyr::mutate(Fed_Unfed = as.factor(Food)) %>% 
                    dplyr::mutate(pCO2 = as.factor(gsub("^(?:[^_]+_){1}([^_]+).*", "\\1", trt))) %>% 
                    dplyr::rename(Length_um = Length) %>% 
                    dplyr::mutate(random_fact = as.factor(paste(pCO2,Rep,Food, sep = "_")))
levels(data_64_survival$Fed_Unfed) <- c("High food", "Low food")
levels(data_64_survival$pCO2) <- c("800 μatm", "500 μatm")

data_64_AVG.survival <- data_64_survival %>%  
                        summarySE(measurevar="Survival", 
                                  groupvars= c("pCO2", "Fed_Unfed")) # summary of means

# run the model
AOV930.survival = aov(Survival ~ 
                         pCO2 * Fed_Unfed, 
                       data=data_64_survival) # no replicates within the tanks a,b,c,d - linear model used here
shapiro.test(residuals(AOV930.survival)) # non normal 0.2602
leveneTest(AOV930.survival) # 0.4668
# so lets do thenonparametric equivalent Schierer-Ray_Hare Test
SRH930.survival <- scheirerRayHare(Survival ~ 
                       pCO2 * Fed_Unfed,
                     data = data_64_survival) # run mod
# all is good, lets see the results
pander(print(SRH930.survival), style='rmarkdown') # table for KW test
# |       &nbsp;       | Df | Sum Sq |   H    | p.value |
# |:------------------:|:--:|:------:|:------:|:-------:|
# |      **pCO2**      | 1  |   4    | 0.1843 | 0.6677  |
# |   **Fed_Unfed**    | 1  | 95.06  | 4.381  | 0.03635 |
# | **pCO2:Fed_Unfed** | 1  | 3.062  | 0.1411 | 0.7072    |
# |   **Residuals**    | 12 | 223.4  |   NA   |   NA    |
kable(unclass(print(SRH930.survival))) %>%  # print a png of this table
  kable_styling() %>%
  save_kable(file = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Survival_size/20210930_figs_table/20210930_survival_SRH_Table.png", zoom = 1.5)


# percent difference
# data_64_survival %>% dplyr::group_by(pCO2) %>% dplyr::summarise(mean = mean(Survival))
# data_64_survival %>% dplyr::group_by(trt) %>% dplyr::summarise(mean = mean(Survival))
data_64_survival %>% dplyr::mutate(PercSurv = Survival*100) %>%  summarySE(measurevar="PercSurv", groupvars= c("Fed_Unfed"))  # view summary means 
((0.98625-0.88750) / 0.98625) * 100 # 10.01267 % greater shell length under high food availability




# plots

Length_64dpf <- ggplot(data_64_length, aes(x =pCO2, (Length_um/1000),  fill = pCO2)) +
                    theme(panel.grid=element_blank()) +
                    geom_boxplot(size=0.2, alpha=0.1, aes(fill=pCO2)) +
                    scale_fill_manual(values=c("grey50","white")) +
                    geom_point(shape = 21, size = 1, position = position_jitterdodge(jitter.width = 0.4)) +
                    theme_classic() +
                    ylim(0, 22) +
                    scale_x_discrete(labels=c('~500 μatm', '~800 μatm')) +
                    theme(axis.text=element_text(size=12),
                          axis.title=element_text(size=14,face="bold")) +
                    stat_summary(fun.y=mean, geom="point", shape=18, size=4) +
                    labs(title = "F1 Scallops: Shell length 64 DPF", 
                         y = expression(Shell~length~"("~mm~")"), 
                         x = expression(italic(p)*CO[2]~Treatment~"("~μ*atm~")")) + 
                    facet_wrap(~factor(Fed_Unfed, level = c('Low food', 'High food'))) 

Survival_64DPF <- ggplot(data_64_survival, aes(x =pCO2, (Survival*100) , fill = pCO2)) +
                    theme(panel.grid=element_blank()) +
                    geom_boxplot(size=0.2, alpha=0.1, aes(fill=pCO2)) +
                    scale_fill_manual(values=c("white","grey50")) +
                    geom_point(shape = 21, size = 2, position = position_jitterdodge(jitter.width = 0.1)) +
                    theme_classic() +
                    ylim(0, 100) +
                    scale_x_discrete(labels=c('~500 μatm', '~800 μatm')) +
                    theme(axis.text=element_text(size=12),
                          axis.title=element_text(size=14,face="bold")) +
                    stat_summary(fun.y=mean, geom="point", shape=18, size=4) +
                    labs(title = "F1 Scallops: Perent survival 64 DPF", 
                         y = expression(Survival~"(%)"), 
                         x = expression(italic(p)*CO[2]~Treatment~"("~μ*atm~")")) + 
                    facet_wrap(~factor(Fed_Unfed, level = c('Low food', 'High food'))) 

# Export the figures to pdf
ggarrange(Length_64dpf,Survival_64DPF,nrow = 2) %>%
  ggexport(filename = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Survival_size/20210930_figs_table/20210930_length_survival.pdf")

```

### density plot - Day 64

```{r, Day 64 density length plot }


data_64_length$pHxfood <- as.factor(paste(data_64_length$pH, data_64_length$Fed_Unfed, sep = "_"))
df_mean <- data_64_length %>% 
  dplyr::group_by(pHxfood) %>% 
  dplyr::summarize(average = mean(Length_um)) %>%
  dplyr::ungroup()
p.box <- ggplot(data_64_length, aes(x = pHxfood, y = (Length_um/1000))) + geom_boxplot() + geom_point(data= df_mean, mapping = aes(x = pHxfood, y = (average/1000)),
             color="red") 
p.box.data <- layer_data(p.box) %>%
  select(x, ymin, lower, middle, upper, ymax, outliers, flipped_aes) %>%
  dplyr::rename(mean = flipped_aes) %>% 
  dplyr::mutate(mean  = (df_mean$average/1000)) %>% 
  mutate(pHxfood = factor(x, labels = levels(data_64_length$pHxfood), ordered = TRUE)) %>%
  select(-x)

denisty_box_length_64DPF <-ggplot(p.box.data) +
                            # manually plot flipped boxplot
                            geom_segment(aes(x = ymin, xend = ymax, y = -0.2, yend = -0.2)) +
                            geom_rect(aes(xmin = lower, xmax = upper, ymin = -0.25, ymax = -0.15,  fill = pHxfood),color = "black") +
                            geom_point(data = . %>% unnest(outliers), 
                                       aes(x = outliers, y = -0.2), color = "grey60", size = 1) +
                            # vertical lines at Q1 / Q2 / Q3
                            geom_vline(data = . %>% select(pHxfood, lower, mean, upper) %>% 
                                         gather(key, value, -pHxfood), aes(xintercept = value)) +
                            # density plot
                            geom_density(data = data_64_length, aes(x = (Length_um/1000), fill=pHxfood, ..scaled..), alpha=.4) +
                            #  theme
                            theme_classic() +
                            xlim(0, 20) +
                            facet_grid(pHxfood ~ .) +
                            theme(panel.grid.major = element_blank(), 
                                  panel.grid.minor = element_blank(), 
                                  legend.position = "none", 
                                  plot.title = element_text(size=10))+
                            labs(x = "Shell length", y = "frequency")  +
                            scale_fill_manual(values=c("grey40", "grey40", "grey85", "grey85"))
denisty_box_length_64DPF
# export the plot
pdf(paste0(filename = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Survival_size/20210930_figs_table/20210930_length_density_plot.pdf"), width = 4, height = 8)
denisty_box_length_64DPF # print the model diagnostics 
dev.off()
```










# 10/26/2021 F1 juvenile scallops  (92 DPF; Day 42)

**About**

- two pCO2 treatments 

- *before* we culled and started the food limitation trials


```{r, Day 92 data}





# Shell length :::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
# length data 
data_92_length <- length %>%
                  filter(Age_DPF=="92") %>%
                  dplyr::mutate(pCO2 = case_when(pH == 8 ~ "500 μatm",  pH == 7.5 ~ "800 μatm")) %>% 
                  dplyr::mutate(Fed_Unfed = case_when(Fed_Unfed == "fed" ~ "High food",  Fed_Unfed == "unfed" ~ "Low food")) %>% 
                  dplyr::mutate(random_fact = as.factor(paste(pCO2,Replicate,Fed_Unfed, sep = "_")))

data_92_AVG.length <- data_92_length %>% 
                      summarySE(measurevar="Length_um",  # view summary means 
                                groupvars= c("Replicate","pCO2", "Fed_Unfed"))  # view summary means 
# run model
AOV930.length = aov(Length_um ~ 
                           pCO2 * Fed_Unfed, 
                           data=data_92_AVG.length)
leveneTest(AOV930.length) # 0.5298
shapiro.test(resid(AOV930.length)) #0.9197
summary(AOV930.length)
#                Df    Sum Sq   Mean Sq F value   Pr(>F)    
# pCO2            1      8482      8482   0.024    0.880    
# Fed_Unfed       1 128925640 128925640 358.668 2.63e-10 ***
# pCO2:Fed_Unfed  1     68302     68302   0.190    0.671    
# Residuals      12   4313477    359456

# all is good, lets see the results
kable(unclass(print(summary(AOV930.length)))) %>%  # print a png of this table
  save_kable(file = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Survival_size/20211026_figs_table/20211026_length_AOV_Table.pdf")


# percent difference
# data_92_survival %>% dplyr::group_by(pCO2) %>% dplyr::summarise(mean = mean(Survival))
# data_92_survival %>% dplyr::group_by(trt) %>% dplyr::summarise(mean = mean(Survival))
data_92_AVG.length %>%  dplyr::mutate(Length_mm = Length_um/1000) %>% summarySE(measurevar="Length_mm", groupvars= c("Fed_Unfed"))  # view summary means 
((8.840188-3.167427) / 8.840188) * 100 # 64.17014 % greater shell length under high food availability




# Survival:::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::::
data_92_survival <- survival_juvenile %>%
                    dplyr::filter(Age_DPF=="92") %>% 
                    dplyr::mutate(Fed_Unfed = as.factor(Food)) %>% 
                    dplyr::mutate(pCO2 = as.factor(gsub("^(?:[^_]+_){1}([^_]+).*", "\\1", trt))) %>% 
                    dplyr::rename(Length_um = Length) %>% 
                    dplyr::mutate(random_fact = as.factor(paste(pCO2,Rep,Food, sep = "_")))
levels(data_92_survival$Fed_Unfed) <- c("High food", "Low food")
levels(data_92_survival$pCO2) <- c("800 μatm", "500 μatm")

data_92_AVG.survival <- data_92_survival %>%  summarySE(measurevar="Survival", groupvars= c("pCO2", "Fed_Unfed")) # summary of means

# run the model
AOV1026.survival = aov(Survival ~ 
                         pCO2 * Fed_Unfed, 
                       data=data_92_survival) # no replicates within the tanks a,b,c,d - linear model used here
shapiro.test(residuals(AOV1026.survival)) #  normal 0.1005
leveneTest(AOV1026.survival) # 0.3336
# all is good, lets see the results
pander(aov(AOV1026.survival), style='rmarkdown') # table for KW test
# |       &nbsp;       | Df |  Sum Sq  | Mean Sq  | F value |  Pr(>F)   |
# |:------------------:|:--:|:--------:|:--------:|:-------:|:---------:|
# |      **pCO2**      | 1  | 0.000225 | 0.000225 | 0.03404 |  0.8567   |
# |   **Fed_Unfed**    | 1  |  1.525   |  1.525   |  230.8  | 3.362e-09 |
# | **pCO2:Fed_Unfed** | 1  | 0.001156 | 0.001156 | 0.1749  |  0.6832   |
# |   **Residuals**    | 12 | 0.07931  | 0.006609 |   NA    |    NA     |
kable(unclass(print(SRH930.survival))) %>%  # print a png of this table
  kable_styling() %>%
  save_kable(file = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Survival_size/20210930_figs_table/20210930_survival_SRH_Table.png", zoom = 1.5)


# percent difference
# data_92_survival %>% dplyr::group_by(pCO2) %>% dplyr::summarise(mean = mean(Survival))
# data_92_survival %>% dplyr::group_by(trt) %>% dplyr::summarise(mean = mean(Survival))
data_92_survival %>% dplyr::mutate(PercSurv = Survival*100) %>%  summarySE(measurevar="PercSurv", groupvars= c("Fed_Unfed"))  # view summary means 
((0.93825-0.32075) / 0.93825) * 100 # 65.81402 % greater survival under high food




# plots

Length_92dpf <- ggplot(data_92_length, aes(x =pCO2, (Length_um/1000),  fill = pCO2)) +
                    theme(panel.grid=element_blank()) +
                    geom_boxplot(size=0.2, alpha=0.1, aes(fill=pCO2)) +
                    scale_fill_manual(values=c("grey50","white")) +
                    geom_point(shape = 21, size = 1, position = position_jitterdodge(jitter.width = 0.4)) +
                    theme_classic() +
                    ylim(0, 22) +
                    scale_x_discrete(labels=c('~500 μatm', '~800 μatm')) +
                    theme(axis.text=element_text(size=12),
                          axis.title=element_text(size=14,face="bold")) +
                    stat_summary(fun.y=mean, geom="point", shape=18, size=4) +
                    labs(title = "F1 Scallops: Shell length 92 DPF", 
                         y = expression(Shell~length~"("~mm~")"), 
                         x = expression(italic(p)*CO[2]~Treatment~"("~μ*atm~")")) + 
                    facet_wrap(~factor(Fed_Unfed, level = c('Low food', 'High food'))) 

Survival_92DPF <- ggplot(data_92_survival, aes(x =pCO2, (Survival*100) , fill = pCO2)) +
                    theme(panel.grid=element_blank()) +
                    geom_boxplot(size=0.2, alpha=0.1, aes(fill=pCO2)) +
                    scale_fill_manual(values=c("white","grey50")) +
                    geom_point(shape = 21, size = 2, position = position_jitterdodge(jitter.width = 0.1)) +
                    theme_classic() +
                    ylim(0, 100) +
                    scale_x_discrete(labels=c('~500 μatm', '~800 μatm')) +
                    theme(axis.text=element_text(size=12),
                          axis.title=element_text(size=14,face="bold")) +
                    stat_summary(fun.y=mean, geom="point", shape=18, size=4) +
                    labs(title = "F1 Scallops: Perent survival 92 DPF", 
                         y = expression(Survival~"(%)"), 
                         x = expression(italic(p)*CO[2]~Treatment~"("~μ*atm~")")) + 
                    facet_wrap(~factor(Fed_Unfed, level = c('Low food', 'High food'))) 


# Export the figures to pdf
ggarrange(Length_92dpf,Survival_92DPF,nrow = 2) %>%
  ggexport(filename = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Survival_size/20211026_figs_table/20211026_length_survival.pdf")

```

### density plot - Day 92

```{r, Day 92 density length plot }
library(dplyr)
library(tidyr)

data_92_length$pHxfood <- as.factor(paste(data_92_length$pH, data_92_length$Fed_Unfed, sep = "_"))
df_mean <- data_92_length %>% 
  dplyr::group_by(pHxfood) %>% 
  dplyr::summarize(average = mean(Length_um)) %>%
  dplyr::ungroup()
p.box <- ggplot(data_92_length, aes(x = pHxfood, y = (Length_um/1000))) + geom_boxplot() + geom_point(data= df_mean, mapping = aes(x = pHxfood, y = (average/1000)),
             color="red") 
p.box.data <- layer_data(p.box) %>%
  select(x, ymin, lower, middle, upper, ymax, outliers, flipped_aes) %>%
  dplyr::rename(mean = flipped_aes) %>% 
  dplyr::mutate(mean  = (df_mean$average/1000)) %>% 
  mutate(pHxfood = factor(x, labels = levels(data_92_length$pHxfood), ordered = TRUE)) %>%
  select(-x)

denisty_box_length_92DPF <-ggplot(p.box.data) +
                            # manually plot flipped boxplot
                            geom_segment(aes(x = ymin, xend = ymax, y = -0.2, yend = -0.2)) +
                            geom_rect(aes(xmin = lower, xmax = upper, ymin = -0.25, ymax = -0.15,  fill = pHxfood),color = "black") +
                            geom_point(data = . %>% unnest(outliers), aes(x = outliers, y = -0.2), color = "grey60", size = 1) +
                            # vertical lines at Q1 / Q2 / Q3
                            geom_vline(data = . %>% select(pHxfood, lower, mean, upper) %>% 
                                         gather(key, value, -pHxfood), aes(xintercept = value)) +
                            # density plot
                            geom_density(data = data_92_length, aes(x = (Length_um/1000), fill=pHxfood, ..scaled..), alpha=.4) +
                            #  theme
                            theme_classic() +
                            xlim(0, 20) +
                            facet_grid(pHxfood ~ .) +
                            theme(panel.grid.major = element_blank(), 
                                  panel.grid.minor = element_blank(), 
                                  legend.position = "none", 
                                  plot.title = element_text(size=10))+
                            labs(x = "Shell length", y = "frequency")  +
                            scale_fill_manual(values=c("grey40", "grey40", "grey85", "grey85"))
denisty_box_length_92DPF
# export the plot
pdf(paste0(filename = "C:/Users/samjg/Documents/Github_repositories/Airradians_OA-foodsupply/RAnalysis/Output/Survival_size/20211026_figs_table/20211026_length_density_plot.pdf"), width = 4, height = 8)
denisty_box_length_92DPF # print the model diagnostics 
dev.off()
```
